### 2018-04-24 frontiers.tex
First commit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
% * <acercyc@gmail.com> 2018-04-10T06:46:45.496Z:
%
% > nor frontiers.tex  %
% > % This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.
%
% ^.
% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.   
%                                              %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.3 Generated 2018/01/26 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
%\documentclass[utf8]{frontiersHLTH} % for Health articles
%\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}

\linenumbers

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Acer Y.C. Chang\,$^{1,*}$, Co-Author\,$^{2}$ and Ryota Kanai\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{ARAYA, Inc., Tokyo, Japan}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author

\def\corrAuthor{Corresponding Author}

\def\corrEmail{acercyc@araya.org}

\begin{document}
\onecolumn
\firstpage{1}

\title[A neural coarse graining theory of consciousness]{A neural coarse graining theory of consciousness}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\maketitle

\begin{abstract}
Neural systems process information through different levels of organisation in a hierarchical manner. Information at lower levels is finer-grained and can be coarse-grained for higher level computation. However, one is aware of information processed only at specific levels.
Theorists have addressed this issue. For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness. It is true that we do not experience information processed by individual neurons which is always highly noisy. Besides, we have no conscious experience from interpersonal activities albeit massive interactions among individuals. Instead, neurophysiological evidence has been showing that conscious experience tends to covary with information encoded in coarse-grained neural states such as neural population codes. 
We hypothesise that, through coarse-graining, neural systems construct a non-trivial information closure representation which represents deterministic dynamics of external environments. Information closure characterises that future states of a system can be deterministically predicted by its past states without information outside the system. Therefore, coarse-grained information encoded within the representation is sufficient to deterministically determine its future states without accessing fine-grained information processed at lower levels. There are significant advantages to construct the information closure representation in neural systems including increasing robustness against noise within fine-grained information processing, providing reliable information for future prediction, and alleviating computational cost for computing sensory data. 
We argue that the neural states within the scope of the information closure determine the contents of consciousness and brain processes outside apart from the representations of that level  remain unconscious. This argument suggests a distinction between conscious and unconscious processing and provides a generic computational framework. Finally, using the deep learning network, we can measure information closure in deep hidden layers. Our preliminary results show that information closure representation emerged after learning. We further decoded the information from the representation and compared it with human conscious perception.

\section{}

\tiny
 \keyFont{ \section{Keywords:} theory of Consciousness, information closure, neural coarse-graining, level of analysis, keyword, keyword, keyword, keyword} %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

% ============================================================================ %
%                                     Start                                    %
% ============================================================================ %
\section{Introduction}

\section{Information Closure}

\section{Mathematical definition}

\section{neural coarse-graining}

\section{Relations to conscious perception phenomena}

\section{Comparison with other theories}

\section{Conclusion}

% ============================================================================ %
%                                      End                                     %
% ============================================================================ %

\subsection{Equations}
Equations should be inserted in editable format from the equation editor.

\begin{equation}
\sum x+ y =Z\label{eq:01}
\end{equation}

\subsection{Figures}
Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript. Figures will then be automatically embedded at the bottom of the submitted manuscript. Kindly ensure that each table and figure is mentioned in the text and in numerical order. Figures must be of sufficient resolution for publication \href{http://home.frontiersin.org/about/author-guidelines#ResolutionRequirements}{see here for examples and minimum requirements}. Figures which are not according to the guidelines will cause substantial delay during the production process. Please see \href{http://home.frontiersin.org/about/author-guidelines#GeneralStyleGuidelinesforFigures}{here} for full figure guidelines. Cite figures with subfigures as figure \ref{fig:2}B.

\subsubsection{Permission to reuse and Copyright}
Permission must be obtained for use of copyrighted material from other sources (including the web). Please note that it is compulsory to follow figure instructions.

\subsection{Tables}
Tables should be inserted at the end of the manuscript. Please build your table directly in LaTeX.Tables provided as jpeg/tiff files will not be accepted. Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space. These tables will be published as \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} on the online article page at the time of acceptance. The author will be notified during the typesetting of the final article if this is the case.

\section{Nomenclature}

\subsection{Resource Identification Initiative}
To take part in the Resource Identification Initiative, please use the corresponding catalog number and RRID in your current manuscript. For more information about the project and for steps on how to search for an RRID, please click \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}{here}.

\subsection{Life Science Identifiers}
Life Science Identifiers (LSIDs) for ZOOBANK registered names or nomenclatural acts should be listed in the manuscript before the keywords. For more information on LSIDs please see \href{http://www.frontiersin.org/about/AuthorGuidelines#InclusionofZoologicalNomenclature}{Inclusion of Zoological Nomenclature} section of the guidelines.

\section{Additional Requirements}

For additional requirements for specific article types and further information please refer to \href{http://www.frontiersin.org/about/AuthorGuidelines#AdditionalRequirements}{Author Guidelines}.

\section*{Conflict of Interest Statement}
%All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to confirm the following statement:

The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Author Contributions}

The Author Contributions section is mandatory for all articles, including articles by sole authors. If an appropriate statement is not provided on submission, a standard one will be inserted during the production process. The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work. Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.

\section*{Funding}
Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.

\section*{Acknowledgements}
This is a short text to acknowledge the contributions of specific colleagues, institutions, or agencies that aided the efforts of the authors.

\section*{Supplemental Data}
 \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.

\section*{Data Availability Statement}
The datasets [GENERATED/ANALYZED] for this study can be found in the [NAME OF REPOSITORY] [LINK].
% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData

\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
\bibliography{ref}

%%% Make sure to upload the bib file along with the tex file and PDF
%%% Please see the test.bib file for some examples of references

\section*{Figure captions}

%%% Please be aware that for original research articles we only permit a combined number of 15 figures and tables, one figure with multiple subfigures will count as only one figure.
%%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
%%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.eps and logos.eps) are in the Frontiers LaTeX folder
%%% If using *.tif files convert them to .jpg or .png
%%%  NB logo1.eps is required in the path in order to correctly compile front page header %%%

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{logo1}% This is a *.eps file
\end{center}
\caption{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures}\label{fig:1}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=15cm]{logos}
\end{center}
\caption{This is a figure with sub figures, \textbf{(A)} is one logo, \textbf{(B)} is a different logo.}\label{fig:2}
\end{figure}

%%% If you are submitting a figure with subfigures please combine these into one image file with part labels integrated.
%%% If you don't add the figures in the LaTeX files, please upload them when submitting the article.
%%% Frontiers will add the figures at the end of the provisional pdf automatically
%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.

\end{document}

### 2018-05-10 frontiers.tex
noting cool

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
-% * <acercyc@gmail.com> 2018-04-10T06:46:45.496Z:
-%
-% > nor frontiers.tex  %
-% > % This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.
-%
-% ^.
-% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.   
-%                                              %
-%                                                                                                                                                         %
-% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %%% Version 3.3 Generated 2018/01/26 %%%
@@
 
-\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
+\documentclass[utf8]{frontiersSCNS} 
+% for Science, Engineering and Humanities and Social Sciences articles
 %\documentclass[utf8]{frontiersHLTH} % for Health articles
 %\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles
+%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
 
-%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
+% ============================================================================ %
+%                                     Macro                                    %
+% ============================================================================ %
+\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}}
+\newcommand{\temp}[1]{\textcolor{Plum}{[[ #1 ]]\newline}}
+
+% ============================================================================ %
+%                                   Packages                                   %
+% ============================================================================ %
 \usepackage{url,hyperref,lineno,microtype,subcaption}
+
 \usepackage[onehalfspacing]{setspace}
+
+\usepackage{todonotes}
+
+\usepackage{xcolor}
+
+\usepackage[margin=2in]{geometry}
+
+% ============================================================================ %
+
+% ============================================================================ %
+%                             Math request package                             %
+% ============================================================================ %
+
+% ============================================================================ %
 
@@
 % Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
-% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
 \def\Address{ARAYA, Inc., Tokyo, Japan}
@@
 Instead, neurophysiological evidence has been showing that conscious experience tends to covary with information encoded in coarse-grained neural states such as neural population codes.
-We hypothesise that, through coarse-graining, neural systems construct a non-trivial information closure representation which represents deterministic dynamics of external environments.
-Information closure characterises that future states of a system can be deterministically predicted by its past states without information outside the system.
-Therefore, coarse-grained information encoded within the representation is sufficient to deterministically determine its future states without accessing fine-grained information processed at lower levels.
-There are significant advantages to construct the information closure representation in neural systems including increasing robustness against noise within fine-grained information processing, providing reliable information for future prediction, and alleviating computational cost for computing sensory data.
 We argue that the neural states within the scope of the information closure determine the contents of consciousness and brain processes outside apart from the representations of that level  remain unconscious.
@@
 We further decoded the information from the representation and compared it with human conscious perception.
-
-\section{}
 
@@
 % ============================================================================ %
+
 \section{Introduction}
 
-\section{Information Closure}
+\section{neural coarse-graining}
+%TODO Single neurons are noisy
 
-\section{Mathematical definition}
+%TODO Population coding
+* \rewrite{Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli. These f
 
-\section{neural coarse-graining}
+eatures consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
 
-\section{Relations to conscious perception phenomena}
+		> The diverse response selectivity of sensory neurons
+		> \rewrite{How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
+
+		% ============================================================================ %
+		% review ref
+		% ============================================================================ %
+		% \cite{Stanley2013}		
+		% \cite{QuianQuiroga2009}
+
+	%TODO sensory hierarchy
+		* Sensors can only receive partial information
+		* Through coarse-graining, higher level cortical areas can integrate those partial information to infer hidden causes.
+
+	\subsection{The advantage of NCG}
+		\subsubsection{Resist to noise}
+		\subsubsection{Operate on deterministic and abstract level}
+		\subsubsection{Predictive power}
+		\subsubsection{Reduce energy cost}
+
+\section{Non-trivial Information Closure}
+
+	% ============================== what is closure ============================= %
+	\rewrite{Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world.
+This requires a system that can be described as a whole without reference to its environment.
+In systems theory, this property is usually referred to as closure.}\citep{BERTSCHINGER.2006}
+
+	\rewrite{These concepts of closure play an important role in the architecture of systems theory, because they are used to
+		1. define the system (in distinction to its environment) and to 
+		2. explain the autonomy of the system.
+	}
+
+	\begin{quotation}
+		Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level.
+Knowledge of the microstate will not improve predictions of the macrostate \citep[p.
+4]{PFANTE.2014}.
+	\end{quotation}
+
+	% ======================= trivial informational closure ====================== %
+	\rewrite{A system that is independent from its environment trivially achieves informational closure.}
+	\citep{BERTSCHINGER.2006}
+
+	\subsection{Mathematical definition of information closure}
+		\rewrite{The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.
+		}
+
+		\cite{BERTSCHINGER.2006} suggests that information closure can be defined as the degree of information flow between environment and the system.
+
+		\begin{equation}
+			\left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \end{array} \right.
+		\end{equation}
+
+		% =============================== Decompose IC =============================== %				
+%		\begin{align}
+%			M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) = M I ( S _ { n + 1} ; E _ { n } ) - ( M I ( S _ { n + 1} ; S _ { n } ) - M I ( S _ { n + 1} ; S _ { n } | E _ { n } ) )
+%		\end{align}
+
+	\subsection{Non-trivial information closure}
+	Information closure could be trivial.
+That is, when a system is fully independent from the environment, no information can flow into the system from the environment and also leak to the environment from the system.
+
+	Equa.
+xxxx shows the mathematical description of trivial information closure.
+When mutual information between the environment and system future state close to 0, and the system transition is independent from the environment, the system can reach informational closure.
+However, such systems do not have any functional meaning and evolutional advantages.
+\\
+	Therefore, it's important to ensure the informational closure that the system reach is non-trivial.\\
+
+	\temp{cite 2006 and nic's paper}
+	To achieve non-trivial information closure, \\
+	\citep{BERTSCHINGER.2006}\\
+	\citep{guttenberg2016neural}
+
+		% ============================================================================ %
+		%                           I don't know what happen                           %
+		% ============================================================================ %		
+%		\begin{equation}	
+%			\begin{align}
+%				{ M I ( S _ { n + 1} ; E _ { n } ) } &= 0&\textmd{and}\\ 
+%				M I ( S _ { n + 1} ; S _ { n } ) - M I ( S _ { n + 1} ; S _ { n } | E _ { n } ) &= 0
+%			\end{align}
+%		\end{equation}
+		% ???????????????????????????????????????????????????????????????????????????? %
+
+	\subsection{how to achieve information closure}
+	\rewrite{This demonstrates that a system exhibiting certain internal regularities as measured by $A^* = MI(Sn+1; Sn)$ can achieve informational closure either by gaining information about the environment or by increased autonomy, i.e.
+by becoming unpredictable or uncontrollable from the
+		(13) environment. Therefore, information about the environment, i.e. modeling, and autonomy can be considered as complementary strategies for achieving informational closure.}
+
+	\subsection{information closure and Level Identification}
+
+\section{My claim of consciousness}
+	* We claim that the coarse-grained state in the information closure determines contents of consciousness. 
+	* It's important that not the neural states but the coarse-grained state determine contents of consciousness.
+
+	% ============================================================================ %
+	%                         Information and system theory                        %
+	%                                                                              %
+	% ============================================================================ %
+	\subsection{Information and system theory}
+		\temp{Closure can define a system, consciousness is information}
+		\temp{Could be linked to system theory, but may need help}
+
+		\rewrite{This self-referential distinction from its environment therefore gives rise to the specific autonomy of such a system.
+Consequently, in systems theory, closure properties and autonomy are considered to be closely related concepts which are both at the heart of defining the system itself.
+		}
+
+\section{Biological Evidence of information closure in neural system}
+
+	% Internal self-predictive mechanism	
+	\cite{sederberg2018learning}
+
+\section{Relation to empirical findings}
+	\subsection{Explain normal and abnormal conscious/non-conscious experience}
+
+%		Binocular rivalry
+%		Hallucinations
+%		subliminal perception
+%		blindsight    
+%		reflex is nonconscious
+%		Procedure memory is state dependent
+%		from conscious to unconscious processes
+%		What happen to lesion
+%		Sleep
+
+%		Perceptual overflow
+%		Discrete vs continuous
+%		Trace conditioning and delay conditioning
+%		agnosia
+
+%		Attention
+%		Top-down attention
+
+	\subsection{Deterministic vs probabilistic}
+	\cite{dehaene2017consciousness}
+	\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}
 
 \section{Comparison with other theories}
+	\subsection{Intermediate Level Theory}
+	\subsection{Global Workspace}
+
+	\subsubsection{Ignition in GWT}
+ 	\temp{Explain ignite}
+
+	\subsection{Sensorimotor contingency}
+	\subsection{IIT}
+	\subsection{Internal simulation and self-modeling}
+
+\section{counterintuitive prediction}
+	% To make a closure, we may discard some information! But what info?
+	% Critical prediction that can test the the theory and IIT: CUT! Split brain
+
+\section{Evolution of conscious mind}
+	\cite{dennett2008kinds}
 
 \section{Conclusion}
+	NCC: To find NCC, it's not about where and when, it's about scale and level of discription
 
@@
 % ============================================================================ %
-
-\subsection{Equations}
-Equations should be inserted in editable format from the equation editor.
-
-\begin{equation}
-\sum x+ y =Z\label{eq:01}
-\end{equation}
-
-\subsection{Figures}
-Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript.
-Figures will then be automatically embedded at the bottom of the submitted manuscript.
-Kindly ensure that each table and figure is mentioned in the text and in numerical order.
-Figures must be of sufficient resolution for publication \href{http://home.frontiersin.org/about/author-guidelines#ResolutionRequirements}{see here for examples and minimum requirements}.
-Figures which are not according to the guidelines will cause substantial delay during the production process.
-Please see \href{http://home.frontiersin.org/about/author-guidelines#GeneralStyleGuidelinesforFigures}{here} for full figure guidelines.
-Cite figures with subfigures as figure \ref{fig:2}B.
-
-\subsubsection{Permission to reuse and Copyright}
-Permission must be obtained for use of copyrighted material from other sources (including the web). Please note that it is compulsory to follow figure instructions.
-
-\subsection{Tables}
-Tables should be inserted at the end of the manuscript.
-Please build your table directly in LaTeX.Tables provided as jpeg/tiff files will not be accepted.
-Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space.
-These tables will be published as \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} on the online article page at the time of acceptance.
-The author will be notified during the typesetting of the final article if this is the case.
-
-\section{Nomenclature}
-
-\subsection{Resource Identification Initiative}
-To take part in the Resource Identification Initiative, please use the corresponding catalog number and RRID in your current manuscript.
-For more information about the project and for steps on how to search for an RRID, please click \href{http://www.frontiersin.org/files/pdf/letter_to_author.pdf}{here}.
-
-\subsection{Life Science Identifiers}
-Life Science Identifiers (LSIDs) for ZOOBANK registered names or nomenclatural acts should be listed in the manuscript before the keywords.
-For more information on LSIDs please see \href{http://www.frontiersin.org/about/AuthorGuidelines#InclusionofZoologicalNomenclature}{Inclusion of Zoological Nomenclature} section of the guidelines.
-
-\section{Additional Requirements}
-
-For additional requirements for specific article types and further information please refer to \href{http://www.frontiersin.org/about/AuthorGuidelines#AdditionalRequirements}{Author Guidelines}.
-
-\section*{Conflict of Interest Statement}
-%All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed.
-If no such relationship exists, authors will be asked to confirm the following statement:
-
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-
-\section*{Author Contributions}
-
-The Author Contributions section is mandatory for all articles, including articles by sole authors.
-If an appropriate statement is not provided on submission, a standard one will be inserted during the production process.
-The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work.
-Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.
 
@@
 LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.
-
-\section*{Data Availability Statement}
-The datasets [GENERATED/ANALYZED] for this study can be found in the [NAME OF REPOSITORY] [LINK].
-% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData
 
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=15cm]{logos}
-\end{center}
-\caption{This is a figure with sub figures, \textbf{(A)} is one logo, \textbf{(B)} is a different logo.}\label{fig:2}
-\end{figure}
-
-%%% If you are submitting a figure with subfigures please combine these into one image file with part labels integrated.
-%%% If you don't add the figures in the LaTeX files, please upload them when submitting the article.
-%%% Frontiers will add the figures at the end of the provisional pdf automatically
-%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.
-
 \end{document}

### 2018-05-10 tex/infoClosure.tex
noting cool

\documentclass[12pt]{article}
\newcommand\longdiv[1]{\overline{\smash{)}#1}}
\usepackage{hyperref}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{tikz}
\begin{document}
\begin{align}
\left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { \text{ we restrict ourselves to discrete observables, i.e. } } \end{array} \right.
\end{align}
\end{document}

### 2018-05-14 Paper_neural_coarse_graining_of_consciousness.tex
Totally use a new Template

\documentclass[utf8]{article}

%% Language and font encodings
\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}

%% glossaries
\usepackage{glossaries}

%% Macro
\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}}
\newcommand{\temp}[1]{\textcolor{Plum}{[[ #1 ]]\newline}}

% ============================================================================ %
%                                     Title                                    %
% ============================================================================ %
\title{A neural coarse graining theory of consciousness}

% ============================================================================ %
%                                    Authors                                   %
% ============================================================================ %
\author[1]{Acer Y.C. Chang\thanks{acercyc@araya.org}}
\author[1]{Martin Biehl\thanks{martin@araya.org}}
\author[1]{Ryota Kanai\thanks{Ryota Kanai}}
\affil[1]{ARAYA, Inc., Tokyo, Japan}

\begin{document}
	\maketitle

	\begin{abstract}
		Neural systems process information through different levels of organisation in a hierarchical manner. Information at lower levels is finer-grained and can be coarse-grained for higher level computation. However, one is aware of information processed only at specific levels. Theorists have addressed this issue. For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness. It is true that we do not experience information processed by individual neurons which is always highly noisy. Besides, we have no conscious experience from interpersonal activities albeit massive interactions among individuals. Instead, neurophysiological evidence has been showing that conscious experience tends to covary with information encoded in coarse-grained neural states such as neural population codes. We argue that the neural states within the scope of the information closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious. This argument suggests a distinction between conscious and unconscious processing and provides a generic computational framework. Finally, using the deep learning network, we can measure information closure in deep hidden layers. Our preliminary results show that information closure representation emerged after learning. We further decoded the information from the representation and compared it with human conscious perception. 
	\end{abstract}

	\section*{keywords:}
	Keywords: theory of Consciousness, information closure, neural coarse-graining, level of analysis

	% ============================================================================ %
	%                                     Start                                    %
	% ============================================================================ %

	\section{Introduction}

	\section{neural coarse-graining}
		\subsection{coarse-graining in neural system}
		\subsection{Single neurons are noisy}
			* \rewrite{neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.}

			* This fact leads to two important points. 
				1. coarse-graining is necessary to resist noise
				2. The information processing related to consciousness should not be situated at 
				this level. Otherwise our conscious percept should be very noisy and unstable.

		\subsection{firing rate coding}
			* temporal coarse-graining

		\subsection{Population coding}
			* Population coding is the idea that nervous systems signal and compute parameters using
			large populations of imprecise neurons, rather than one or a few precise neurons.

			* \rewrite{As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}

			* \rewrite{Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli. These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}

			* The diverse response selectivity of sensory neurons

			* \rewrite{How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}

			* \rewrite{Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.} \cite{binder2009encyclopedia}

			% ============================================================================ %
			% review ref
			% ============================================================================ %
			% \cite{Stanley2013}		
			% \cite{QuianQuiroga2009}

		\subsection{sensory hierarchy}
			* Sensors can only receive partial information
			* Through coarse-graining, higher level cortical areas can integrate those partial information to infer hidden causes.

		\subsection{The advantage of NCG}
			\subsubsection{Resist to noise}
				* \rewrite{ The population will therefore be relatively insensitive to the loss of
					cells or noise in a small number of cells} \cite{eurich2000multidimensional}

			\subsubsection{Operate on deterministic and abstract level}
			\subsubsection{Predictive power}
			\subsubsection{Reduce energy cost}

		\subsection{neural coarse-graining in deep learning}

	\section{Non-trivial Information Closure}

		% ============================== what is closure ============================= %
		\rewrite{
			Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world. This requires a system that can be described as a whole without reference to its environment. In systems theory, this property is usually referred to as closure.
		}\citep{BERTSCHINGER.2006}

		\rewrite{
			These concepts of closure play an important role in the architecture of systems
			theory, because they are used to
			1. define the system (in distinction to its environment) and to 
			2. explain the autonomy of the system.
		}

		\begin{quotation}
			Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level. Knowledge of the microstate will not improve predictions of the macrostate \citep[p. 4]{PFANTE.2014}.
		\end{quotation}

		% ======================= trivial informational closure ====================== %
		\rewrite{A system that is independent from its environment trivially achieves informational 
			closure.}
		\citep{BERTSCHINGER.2006}

		\subsection{Mathematical definition of information closure}
			\rewrite{
				The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.
			}\cite{BERTSCHINGER.2006}

			suggests that information closure can be defined as the degree of information flow between environment and the system.

		\begin{equation}
			 \left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \end{array} \right.
		\end{equation}

		% =============================== Decompose IC =============================== %				
		%		\begin{align}
		%			M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) = M I ( S _ { n + 1} ; E _ { n } ) - ( M I 
		%( S _ { n + 1} ; S _ { n } ) - M I ( S _ { n + 1} ; S _ { n } | E _ { n } ) )
		%		\end{align}

		\subsection{Non-trivial information closure}
			Information closure could be trivial. That is, when a system is fully independent from the environment, no information can flow into the system from the environment and also leak to the environment from the system. Equa. xxxx shows the mathematical description of trivial information closure. When mutual information between the environment and system future state close to 0, and the system transition is independent from the environment, the system can reach informational closure. However, such systems do not have any functional meaning and evolutional advantages.

			Therefore, it's important to ensure the informational closure that the system reach is non-trivial.

			\temp{cite 2006 and nic's paper}
			To achieve non-trivial information closure
			\citep{BERTSCHINGER.2006}\\
			\citep{guttenberg2016neural}

			% ============================================================================ %
			%                           I don't know what happen                           %
			% ============================================================================ %		
			%		\begin{equation}	
			%			\begin{align}
			%				{ M I ( S _ { n + 1} ; E _ { n } ) } &= 0&\textmd{and}\\ 
			%				M I ( S _ { n + 1} ; S _ { n } ) - M I ( S _ { n + 1} ; S _ { n } | E _ { n } ) &= 0
			%			\end{align}
			%		\end{equation}
			% ???????????????????????????????????????????????????????????????????????????? %

		\subsection{how to achieve non-trivial information closure}
			* Through coarse-graining
			* Accurately model deterministic environment 
				\rewrite{
					This demonstrates that a system exhibiting certain internal regularities as measured by $A^* = MI(Sn+1; Sn)$ can achieve informational closure either by gaining information about the environment or by increased autonomy, i.e. by becoming unpredictable or uncontrollable from the (13) environment. Therefore, information about the environment, i.e. modeling, and autonomy can be considered as complementary strategies for achieving informational closure.}
			* by Action

		\subsection{information closure and Level Identification}

	\section{Our claim of consciousness}
		* We claim that the coarse-grained state in the information closure determines contents of 
		consciousness. 
		* It's important that not the neural states but the coarse-grained state determine contents
		of consciousness.

		\subsection{Measure of conscious level}

		% ============================================================================ %
		%                         Information and system theory                        %
		%                                                                              %
		% ============================================================================ %
		\subsection{Information and system theory}
			\temp{Closure can define a system, consciousness is information}
			\temp{Could be linked to system theory, but may need help}

			\rewrite{
				This self-referential distinction from its environment therefore gives rise to the specific autonomy of such a system. Consequently, in systems theory, closure properties and autonomy are considered to be closely related concepts which are both at the heart of defining the system itself.}
	\section{Emperical approaches of measuring neural information closure}

	\section{Biological Evidence of information closure in neural system}

		% ============================================================================ %
		%                             sederberg2018learning                            %
		% ============================================================================ %

		% Internal self-predictive mechanism	
		* Recent biological evidence suggests that low-level neurons encodes predictive information about external  and

		\todo{need to say this is exactly the non-trivial information closure, and refer to equation XXX}
		\cite{sederberg2018learning}
		\rewrite{in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }

		\rewrite{We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}

		\rewrite{ We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }

		\rewrite{
			Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal. This suggests that bottom-up prediction may play an important role in sensory processing}

		\rewrite{Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}

		\rewrite{ Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}

		* They also showed generalization of internal predictability across stimulus. This suggests .... what?

		\rewrite{ The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}

		\cite{Palmer2015}
		\rewrite{ Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}

		\todo{\url{http://tinyurl.com/y9zmhlln}	}

		\rewrite{It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig. 3, but the brain has no direct access to visual stimuli except that provided by the retina. Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs? More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future? The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ }

		\rewrite{ larger groups of cells carry predictive information for hundreds of milliseconds, }

	\section{Relation to empirical findings in neuroscience and consciousness studies}
		\subsection{reflexive behavioural is unconscious}

		\subsection{Explain normal and abnormal conscious/non-conscious experience}

		%		Binocular rivalry
		%		Hallucinations
		%		subliminal perception
		%		blindsight    
		%		reflex is nonconscious
		%		Procedure memory is state dependent
		%		from conscious to unconscious processes
		%		What happen to lesion
		%		Sleep

		%		Perceptual overflow
		%		Discrete vs continuous
		%		Trace conditioning and delay conditioning
		%		agnosia

		%		Attention
		%		Top-down attention

		\subsection{Deterministic vs probabilistic}
		\cite{dehaene2017consciousness}
		\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}

	\section{Comparison with other theories}
		\subsection{Intermediate Level Theory}

			\cite{jackendoff1987consciousness}
			\cite{prinz2007intermediate}

			\rewrite{
				In 1987, Ray Jackendoff published Consciousness and the Computational Mind. In it, he posed an important Where question: Where, in the fl ow of information, does consciousness arise? Most cognitive scientists agree that the mind is, in some sense, a computer. It is a device that processes information by transforming representations in accordance with rules. Computational devices decompose into various interconnected subsystems, each of which performs some aspect of a complex task. Given such a decompositional analysis, we can ask: in which subsystems does consciousness arise? If we depict the mind as a vast fl ow chart, and highlight the boxes whose rules and representations are conscious, which boxes should we mark? Jackendoff ’s answer is simple and elegant. He noticed that many of our mental capacities, including our senses and our language systems, are organized hierarchically. In each of these hierarchies, it makes sense to talk about low- , intermediate- , and high- level processing systems. We break down tasks into stages. Appealing to prevailing models of these stages, Jackendoff observed that the intermediate level seems to be privileged with respect to consciousness. Consciousness seems to arise in intermediate- level processing systems and not elsewhere.} - \cite{prinz2007intermediate}

			* 2.5D

			\todo{about why it is this level}
			\rewrite{
				Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive? Th is is a tractable question, and it may lead to insights into the function of consciousness. Representations at the intermediate level are ideally suited for real- time deliberative behavioral responses. Low- level representations fail to bind features into coherent wholes. If we are going to interact with our environment, the low level is not a good guide. Th e high level is a good deal better for action, but also suboptimal. Th e high level tells us the category of the stimuli we perceive, but from an allocentric point of view. It abstracts away from stimulus features that are crucial for action. If we encounter a predator, the high- level visual representation does not tell us if it is facing toward us or away from us. Without that knowledge, we cannot decide what course of action to take. So, I propose that the intermediate level plays a distinctive role in information processing. It delivers representations that are coherent but viewpoint specifi c. Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
			\rewrite{
				I conclude that the intermediate level plays a distinctive and important computational role. Some researchers fi nd this puzzling. In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels. Could they not have two? Or a hundred? Do the 50 or so areas that contribute to visual processing really divide neatly into three levels? I think these puzzles depend on a particular understanding of what the word “intermediate” amounts to. One might get caught up in the fact that the intermediate level is the second stage in a sequence. Call this the “serial understanding of the intermediate level.” Alternatively, one might think of the intermediate level semantically. On this reading, the intermediate level is one that is not abstract and categorical, but not piecemeal or disunifi ed. Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}

			\subsubsection{The difference between ILT and our theory}
				Prinz suggested that \rewrite{as. Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously. } \cite{prinz2007intermediate}

				* Our prediction is, if information that is carried by v1 neurons are necessary to complete information closure, the states of V1 neurons should also co-vary with conscious contents.

		\subsection{Global Workspace}
			\subsubsection{Ignition in GWT}
				\temp{Explain ignite}
		\subsection{Sensorimotor contingency}
		\subsection{Predictive Brain}
			\todo{I need math here!!}
			* To achieve non-trivial information closure naturally maximal predictive power via coarse-graining.

		\subsection{IIT}
			\temp{Hoel's theory}
		\subsection{Internal simulation and self-modeling}

	\section{Counter-intuitive prediction}
		% To make a closure, we may discard some information! But what info? Critical prediction that can test the the theory and IIT: CUT! Split brain

	\section{Evolution of conscious mind}
		\cite{dennett2008kinds}

	\section{Conclusion}
		* NCC: To find NCC, it's not about where and when, it's about scale and level of description

	% ============================================================================ %
	%                                      End                                     %
	% ============================================================================ %

	\section*{Funding}

	\section*{Acknowledgements}

	\section*{Supplemental Data}

	\bibliographystyle{authordate1}
	\bibliography{ref}

\end{document}

### 2018-05-22 Paper_neural_coarse_graining_of_consciousness.tex
Add lots of macros

@@
 %% Sets page size and margins
-\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
+%\usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
+\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
 
@@
 \usepackage{graphicx}
-\usepackage[colorinlistoftodos]{todonotes}
 \usepackage[colorlinks=true, allcolors=blue]{hyperref}
@@
 
-%% glossaries
-\usepackage{glossaries}
+%% acronym
+\usepackage{acronym}
+\newacro{ntic}{non-trivial information closure}
+\newacro{ic}{information closure}
+\newacro{cg}{coarse-grain}
+\newacro{cging}{coarse-graining}
+\newacro{cged}{coarse-grained}
+\newacro{ncg}{neural coarse-graining}
 
-%% Macro
-\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}}
-\newcommand{\temp}[1]{\textcolor{Plum}{[[ #1 ]]\newline}}
+% =================================== Macro ================================== %
+\usepackage[colorinlistoftodos]{todonotes}
+\usepackage[at]{easylist}
+\usepackage{tcolorbox}
+
+% Real content
+	% Finished part
+	% Outline items that can be integrated into main text
+		\newenvironment{ants}
+			{
+			 \begin{easylist}[itemize]
+			}
+			{
+			\end{easylist}
+			}
+% Funcitonal content
+	% Quotes
+		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}
+	% todo
+	% Need reference 
+		\newcommand{\needref}[1]{%
+			\ifthenelse{\equal{#1}{}}{%
+				\todo[color=White, linecolor=BlueViolet]{\textcolor{BlueViolet}{Ref}}}{%
+				\todo[color=White, linecolor=BlueViolet]{\textcolor{BlueViolet}{Ref: #1}}%
+				}%
+		}
+
+	% idea
+		% text idea
+			\newcommand{\idea}[1]{\noindent
+				\textcolor{Plum}{[[ #1 ]]\newline}}
+
+		% box idea
+			\newcommand{\ideaBox}[1]{
+				\begin{tcolorbox}[hyphenationfix, width=12cm, colback=Thistle!50!white, flush right]
+					#1
+				\end{tcolorbox}
+			}
+
+		% callout idea
+			\newcommand{\ideaCallout}[1]{\todo[color=Thistle, size=\small]{#1}}
+
+	% guildline and direction
+		\newcommand{\toWrite}[1]{\noindent
+			\textcolor{Cyan}{\textbf{[[ #1 ]]}\newline}}
+	% call for help
+		\newcommand{\martin}[1]{\todo[color=SpringGreen]{@Martin:\\#1}}
 
@@
 \author[1]{Martin Biehl\thanks{martin@araya.org}}
-\author[1]{Ryota Kanai\thanks{Ryota Kanai}}
+\author[1]{Ryota Kanai\thanks{kanair@araya.org }}
 \affil[1]{ARAYA, Inc., Tokyo, Japan}
@@
 	\maketitle
+	\tableofcontents
 
@@
 We further decoded the information from the representation and compared it with human conscious perception.
+\needref{}
 	\end{abstract}
@@
 
+		\begin{ants}
+			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.
+
+			@ Intuitive physics \needref{Intuitive physics}
+
+			@ We propose that consciousness is not related to particular neural architectures or location of the neural system.
+
+			@ We argue that consciousness corresponds to information processing at a certain coarse-graining level which form information closure. 
+		\end{ants}
+
 	\section{neural coarse-graining}
+
+		\begin{ants}
+			@ \rewrite{Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
+
+		\end{ants}
+
 		\subsection{coarse-graining in neural system}
 		\subsection{Single neurons are noisy}
-			* \rewrite{neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.}
 
-			* This fact leads to two important points. 
-				1. coarse-graining is necessary to resist noise
-				2. The information processing related to consciousness should not be situated at 
-				this level. Otherwise our conscious percept should be very noisy and unstable.
+			\begin{ants}
+				@ \rewrite{
+					neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.}
+
+				@ This fact leads to two important points
+					@@ coarse-graining is necessary to resist noise
+					@@ The information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
+
+			\end{ants}
 
 		\subsection{firing rate coding}
-			* temporal coarse-graining
+
+			\begin{ants}
+
+				@ temporal coarse-graining
+
+			\end{ants}
 
 		\subsection{Population coding}
-			* Population coding is the idea that nervous systems signal and compute parameters using
-			large populations of imprecise neurons, rather than one or a few precise neurons.
+			\begin{ants}
+				@ Population coding is the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
 
-			* \rewrite{As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}
+				@ \rewrite{
+					As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}
 
-			* \rewrite{Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
+				@ \rewrite{
+					Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
 These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
 
-			* The diverse response selectivity of sensory neurons
+				@ The diverse response selectivity of sensory neurons
 
-			* \rewrite{How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
+				@ \rewrite{
+					How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
 
-			* \rewrite{Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.} \cite{binder2009encyclopedia}
+				@ \rewrite{
+					Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
+					} \cite{binder2009encyclopedia}
+
+			\end{ants}
 
@@
 		\subsection{sensory hierarchy}
-			* Sensors can only receive partial information
-			* Through coarse-graining, higher level cortical areas can integrate those partial information to infer hidden causes.
+
+			\begin{ants}
+				@ Sensors can only receive partial information
+
+				@ Through coarse-graining, higher level cortical areas can integrate those partial information to infer hidden causes.
+
+			\end{ants}
 
@@
 		\subsection{neural coarse-graining in deep learning}
+			\martin{todo}
 
 	\section{Non-trivial Information Closure} 
+		\martin{todo}
 
@@
 
-			\temp{cite 2006 and nic's paper}
+			\todo{cite 2006 and nic's paper}
 			To achieve non-trivial information closure
@@
 
-	\section{Our claim of consciousness}
+		\subsection{Biological Creature may try to achieve closure even the environment is not }
+
+	\section{A neural coarse graining theory of consciousness}
 		* We claim that the coarse-grained state in the information closure determines contents of 
@@
 		\subsection{Measure of conscious level}
+		\subsection{Conscious contents}
+		\subsection{Sensory hierarchy and neural coarse-graining}
+
+			\begin{ants}
+				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining
+			\end{ants}
 
@@
 		\subsection{Information and system theory}
-			\temp{Closure can define a system, consciousness is information}
-			\temp{Could be linked to system theory, but may need help}
+			\idea{A closure can define a system, consciousness is information}
+
+			\idea{Could be linked to system theory, but may need help}
 
@@
 Consequently, in systems theory, closure properties and autonomy are considered to be closely related concepts which are both at the heart of defining the system itself.}
-	\section{Emperical approaches of measuring neural information closure}
+		\subsection{Emperical approaches of measuring neural information closure}
 
@@
 		\subsection{reflexive behavioural is unconscious}
+			\begin{ants}
+				@ x -> s -> a
+					@@ the system state is determined by environmental state, then it is not conscious. 
+				@ Policy is not conscious
+				@ Patient B.F.
+			\end{ants}
 
@@
 
-			\cite{jackendoff1987consciousness}
-			\cite{prinz2007intermediate}
+			\begin{ants}
+				@ \rewrite{
+					The intermediate level theory originally proposed by Ray Jackendoff and further defended and specified by Jesse Prinz proposes that within the hierarchy of representations that are used to describe the cognitive system, conscious experience occurs only for specific levels of representation.
+The theory is rooted in Jackendoff ’s analysis of different cognitive systems such as vision, language, and music and the subsequent observation that consciousness does not arise anywhere within these systems.
+According to Jackendoff, consciousness is not associated with low-level, nor with high-level representations, but rather with those implying intermediate levels of processing.
+For instance, in the domain of object recognition, it is assumed that the visual system comprises a low level with local computations of visual features, an intermediate level reflecting binding and object recognition, and a higher level computing viewpoint invariance and representing abstract categories.
+According to Jackendoff and Prinz, conscious experience is not comprised of a disunified picture of visual features, nor is it represented by viewinvariant categories.
+Rather it is composed of bound and specific instances of objects that are assumed to be computed at the intermediate level of representation.
+In an analogous manner, speech perception can be decomposed into three levels: an acoustic representation of speech sounds at the lower level, a high level involving abstract lexical and syntactic categories, and in between a word recognition level relying on phonological representations.
+This theory explains why the conscious experience associated with speech perception mostly involves phonological representations, rather than other levels of representations.
+In Jackendoff and Prinz’ theory,the privileged role of the intermediate level of processing is based on the need for real-time computational efficiency.
+Indeed, this level of representation is assumed to be the most relevant one regarding ecological and functional needs.
+Another important aspect of this theory concerns the central role of attention during conscious experience.
+Here, attention is defined as a selection process that acts as a gate to working memory mechanisms.
+It performs the function of selecting the relevant information that is amplified afterward and then becomes conscious.
+Indeed, Prinz acknowledges that activation of an intermediatelevel representation on its own cannot be a sufficient condition for consciousness, given that those representations can be activated during subliminal perception.
+However, this theory makes the crucial postulate that the amplification of intermediatelevel representations by attention is a necessary and sufficient condition for consciousness.
+In sum, for each domain of processing, the content of consciousness at a particular moment is supported by a representational structure of intermediate level for that domain, which is selected to enter short-term memory, and enriched by attentional processing.} \cite{banks2009encyclopedia}
 
-			\rewrite{
+				@ \rewrite{
 					In 1987, Ray Jackendoff published Consciousness and the Computational Mind.
@@
 Appealing to prevailing models of these stages, Jackendoff observed that the intermediate level seems to be privileged with respect to consciousness.
-Consciousness seems to arise in intermediate- level processing systems and not elsewhere.} - \cite{prinz2007intermediate}
+Consciousness seems to arise in intermediate- level processing systems and not elsewhere.} \cite{prinz2007intermediate}
 
-			* 2.5D
+				@ \cite{jackendoff1987consciousness}
+				@ \cite{prinz2007intermediate}
+				@ 2.5D
 
-			\todo{about why it is this level}
-			\rewrite{
+				@ about why it is this level
+				@@ \rewrite{
 					Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive?
@@
 Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
-			\rewrite{
+				@@ \rewrite{
 					I conclude that the intermediate level plays a distinctive and important computational role.
@@
 Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}
+			\end{ants}
 
@@
 
-		\subsection{Global Workspace}
-			\subsubsection{Ignition in GWT}
-				\temp{Explain ignite}
+		\subsection{first-order theories}
+			\begin{ants}
+				@\cite{lau2011empirical}
+					@@ \rewrite{
+						The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
+Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.\\
+						Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26].\\
+						Most ﬁrst-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g.
+subcortical) sensory pathways.
+Thus this view suggests that conscious and unconscious processing will have different functional consequences.
+Whereas some ﬁrst-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most ﬁrst-order theorists take a difference in perceptual task performance (e.g.
+‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33].
+In other words, they typically associate task performance with awareness.
+					}
+
+			\end{ants}
+
+		\subsection{Global Workspace Theory (GWT)}
+			\subsubsection{Global availability and Broadcasting}
+
+			\subsubsection{Code translation}
+				\begin{ants}
+					@ neural coarse-graining can natually solve this problem. 
+					@ coarse-graining between levels can be thought as code translation\todo{is this true?}
+				\end{ants}
+
+			\subsubsection{Stability}
+				\begin{ants}
+					@ the presence of contexts as stable coalitions shaping access to the workspace.
+
+				\end{ants}
+
+			\subsubsection{broadcasting}
+
+			\subsubsection{Ignition}
+				\toWrite{Explain ignite}
+
+			\begin{ants}
+				@ GWT is one of the current popular consciousness theories.
+
+				@ \rewrite{AI system and corresponds to our first functional definition of consciousness: global availability} \cite{Dehaene2017}
+
+				@ C1: Global availability of relevant information The need for integration and coordination \cite{Dehaene2017}
+
+				@ Evidence for integration and broadcasting
+
+				@ Stability as a feature of consciousness \rewrite{“ meta-stability ” seems to be necessary for the nervous system to integrate information from a variety of modules and then broadcast it back to them, achieving flexible cross-module routing.}
+
+				@ \rewrite{integration of computational resources in a large-scale coordination and for the exchange of information among processors}
+
+				@ \rewrite{Grounded on the distinction between conscious and unconscious processes, Bernard Baars’ global workspace theory is one of the most influential cognitive theories of consciousness.
+This theory relies on the metaphor of a theater.
+In this theater, unconscious specialized processors (equivalent to modules) are assumed to be the actors and the audience.
+While the audience represents the set of passive processors, actors represents active processors playing on the stage of the theater (i.e., the workspace).
+These actors are engaged in a competition for being seen by the audience: by broadcasting their information they actually compete for more broadcasting.
+Active processors with the highest coherent activity can form local coalitions that strengthen them in this competition process.
+The strongest coalition in this competition dominates the workspace, in a winner-take-all fashion, and corresponds to the content of consciousness.
+The workspace is equated by Baars to working-memory, in which only the most active content becomes conscious.
+Additionally, the dominant coalition benefits from global broadcasting, which allows it to recruit new processors from the audience in order to form a global coalition.
+Here, consciousness allows for the integration of computational resources in a large-scale coordination and for the exchange of information among processors that would otherwise remain separated.
+In this theory, each processor can operate in the conscious mode if it benefits from global broadcasting through the workspace, or it can operate in the unconscious mode when disconnected from the workspace.
+An important feature of the global workspace theory is the presence of contexts as stable coalitions shaping access to the workspace.
+Contexts are constituted of unconscious processors reflecting, in a hierarchical manner, our expectations, our beliefs, our goals, and ultimately our self.
+In particular, attention is implemented as a goal context in this theory.
+It is described as a mechanism that controls access to the workspace, acting as a filter and biasing the competition process toward a particular set of actors.
+At any given moment, the dominant coalition is under the spotlight of attention, and its informational content becomes the content of conscious experience.
+A crucial aspect of Baars’ theory is that it avoids the problem of the homunculus by reducing it to an audience of multiple unconscious processors.
+Here, there is no need for a hypothetical single conscious observer in the system, and thus there is no issue of infinite regression with a homunculus inside another homunculus.
+Instead, consciousness is considered to reflect the global broadcasting of information to an audience of unconscious processors.
+As the audience is unconscious, unsupervised, and receptive rather than attending to the information, it does not constitute an internal homunculus.}
+
+			\end{ants}
+
+		\subsection{Higher Order Thought theory of consciousness}	
+			\idea{People think a high order representation receives information from the first order representation.
+This may be a misunderstanding.
+This may be the result of neural coarse-graining.
+Because contents in information closure look like watching fine-grained information, people may have an wrong impression about it}
+
+			============================================================================			
+			\begin{ants}
+				@ Information closure directly is critical for other systems to construct forward models.
+
+				@ Therefore, most of the high level cognitions can utilise the state of information closure.
+
+				@ For example, mental planning needs a precise forward model to infer the environmental dynamics.
+
+				@ \idea{This is way HOT always involve consciousness }
+
+				@ \cite{rosenthal2005consciousness}
+			\end{ants}
+
+			\rewrite{
+				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}
+
+			\rewrite{
+				According to this view, humans not only have first-order non-conceptual and/or analog perceptions of states of their environments and bodies, they also have second-order non-conceptual and/or analog perceptions of their first-order states of perception.
+And the most popular version of higher-order perception theory holds, in addition, that humans (and perhaps other animals) not only have sense-organs that scan the environment/body to produce fine-grained representations that can then serve to ground thoughts and action-planning, but they also have inner senses, charged with scanning the outputs of the first-order senses (i.e.
+perceptual experiences) to produce equally fine-grained, but higher-order, representations of those outputs (i.e.
+to produce higher-order experiences).
+A version of this view was first proposed by the British Empiricist philosopher John Locke (1690).
+In our own time it has been defended especially by Armstrong (1968, 1984) and by Lycan (1996).} \url{https://plato.stanford.edu/entries/consciousness-higher/#SelRepHigOrdThe}
+
+			\rewrite{
+				neutral about whether conscious awareness adds signiﬁcant utility or immediate impact on behavior and task performance [1,27].
+This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on ﬁrst-order rather than higher-order representations.
+Because conscious awareness can differ even if all ﬁrst-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
+				\ideaCallout{
+					My theory would have similar prediction.
+Because conscious contents are coarse-grained results from low-level information.
+It is possible that more than two low-level neural states all coarse-grained to a high-level state.
+}
+
+			\subsubsection{Metacognition}
+				\rewrite{
+					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world.
+In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efﬁcacy of a perceptual process.
+The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}
+
 		\subsection{Sensorimotor contingency}
 		\subsection{Predictive Brain}
-			\todo{I need math here!!}
-			* To achieve non-trivial information closure naturally maximal predictive power via coarse-graining.
+
+			* Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}
+
+			* Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.
+
+			* More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.
+
+			* Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.
+
+			* Note that, a system showing some predictive power is not sufficient to be conscious.
+
+			* For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future.
+Derivative action predicts system behaviour and thus improves settling time and stability of the system.
+
+			* However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.
+
+			.
+It can compute position, velocity, and acceleration of objects, and output control signals (action).
+However, the state of the PID controller is not information-closed.
+The state still fully determined by the input signals.
+Therefore, it fails to reach \ac{ic}.
+Hence, according to our theory, the PID system is not conscious.
+
+			* Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.
 
 		\subsection{IIT}
-			\temp{Hoel's theory}
+			\subsubsection{Hoel's theory}
+				\martin{Do you want to write this session?}
+
 		\subsection{Internal simulation and self-modeling}
@@
 	\section{Counter-intuitive prediction}	
-		% To make a closure, we may discard some information! But what info? Critical prediction that can test the the theory and IIT: CUT! Split brain
+		\subsection{Prediction on split-brain (vs IIT)}
+			* IIT suggests that cutting, two subparts may both still have MIP, therefore, have two conscious mind.
 
-	\section{Evolution of conscious mind}
+			* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.
+
+	\section{Future work}
+		\begin{ants}
+
+			@ Lack of direct evidence because no one focus on information closure
+
+		\end{ants}
+
+		\subsection{Brain area}
+
+	\section{Evolution of conscious mind (not sure but if I have time)}
 		\cite{dennett2008kinds}

### 2018-05-25 Paper_neural_coarse_graining_of_consciousness.tex
An update

@@
 
+% Meaning of colours --------------------------------------------------------- %
+%	Red: Important and Critical
+%	Orange: Todo
+%	Blue: Topic and Guideline
+%	Purple: Murmur, talking to myself
+%	Green: Question, Call for help, Open for opinions and comments
+%	Brown: Need Wording 
+% ---------------------------------------------------------------------------- %
+
 % Real content
@@
 		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}
+
 	% todo
+
+	% Highlight
+		\newcommand{\highlight}[2][Yellow]{\colorbox{#2}}
+
+		% Highlight and comment
+		\newcommand{\highlightAndComment}[3][Yellow]{\todo[color=#1]{#3}\colorbox{#1}{#2}}
+
+	% rewording
+		\newcommand{\rewording}[1]{\textcolor{RawSienna}{[[ REWORDING | #1 ]]}}
+
 	% Need reference 
@@
 		\newcommand{\toWrite}[1]{\noindent
-			\textcolor{Cyan}{\textbf{[[ #1 ]]}\newline}}
+			\textcolor{Cyan}{\textbf{[[ #1 ]]}}}
+
 	% call for help
+		\newcommand{\callforhelp}[1]{\todo[color=SpringGreen]{#1}}
 		\newcommand{\martin}[1]{\todo[color=SpringGreen]{@Martin:\\#1}}
@@
 We further decoded the information from the representation and compared it with human conscious perception.
-\needref{}
 	\end{abstract}
@@
 		\begin{ants}
+
+			%% Story about a cell
+				@ Imagining you are a neuron in (a human) Bill's brain.
+Your "responsibility" is to collect neurotransmitters from dendrites, accumulate membrane potential, and finally send a signal to your colleagues through an action potential.
+
+				@ You have no idea about whether you are involved in an information processing chain for Bill to see or catch  a ball.
+
+				@ All you have to do is receiving, computing, and outputting information.
+
+				@ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour.
+If your work contributes some part of Bill's conscious perception or intention to act.
+
+			%% scale
+				@ \rewording{
+					It seems that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.}
+
+				@ Information processing of individual neurons are highly noisy. Neurons fires all the time. However, those massive action potentials do not appear in our conscious contents.
+
+				@ Don't even mention ion channel dynamic.
+
+				@ We also lake of experience of whole brain operation. Some parts of our brains process in an unconscious way.
+
+				@ We don't have experience of inter-individual super-consciousness
+
+			%% our argument
+				@ In this article, we argue that consciousness \highlightAndComment[YellowGreen]{correlates}{Is this proper?} information processing at a certain coarse-graining level which form information closure.
+More specifically, the conscious level is determined by the level of information closure and conscious contents is determined by the states of information closure.
+
+				@ We first introduce non-trivial information closure and its importance for human scale agents.
+
+				@ We then presume that through neural coarse-graining the human brain achieves a non-trivial information closure \highlightAndComment[YellowOrange]{realm}{Need to unify this term} at a specific macroscopic level.
+
+				@ We then argue that consciousness levels and contents are determines the state of consciousness for both levels and contents.
+
+				@ We then discuss how this theory can concisely explain empirical results from previous studies and integrate several current major theories of consciousness.
+
+				@ We finally provide theory predictions testable approaches.
+
+			%% Advantage 
+				@ This framework provides a concise and quantifiable explanation for all current major theories of consciousness.
+
+				@ This framework provides a more fundamental understanding about why some neural process are conscious but others are not.
+
+		\end{ants}
+
+		==================================================
+		\begin{ants}
+
+			@ consciousness is information
+
+			@ conscious contents
+				@@ \toWrite{lower level}
+				@@ Information processing of individual neurons are noisy.
+				@@ We don't have conscious content changes when individual neurons fire action potentials. 				
+				@@ Don't even mention ion channel dynamic.
+
+				@@ \toWrite{Higher-level dynamic}
+
 			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.
+
+			@ \toWrite{Human tendency for active prediction }
+				@@ \cite{Stahl2015} \rewrite{
+					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore?
+We found that 11-month-old infants (N = 110) used violations of prior expectations as special opportunities for learning.
+The infants were shown events that violated expectations about object behavior or events that were nearly identical but did not violate expectations.
+The sight of an object that violated expectations enhanced learning and promoted information-seeking behaviors; specifically, infants learned more effectively about objects that committed violations, explored those objects more, and engaged in hypothesis-testing behaviors that reflected the particular kind of violation seen.
+Thus, early in life, expectancy violations offer a wedge into the problem of what to learn.}
 
@@
 
+			@ However, sensory signal are always noisy.
+
 			@ We propose that consciousness is not related to particular neural architectures or location of the neural system.
-
-			@ We argue that consciousness corresponds to information processing at a certain coarse-graining level which form information closure. 
-		\end{ants}
-
-	\section{neural coarse-graining}
-
-		\begin{ants}
-			@ \rewrite{Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
 
@@
 
-		\subsection{coarse-graining in neural system}
-		\subsection{Single neurons are noisy}
-
+	\section{\martin{todo}Non-trivial Information Closure}
 		\begin{ants}
-				@ \rewrite{
-					neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.}
-
-				@ This fact leads to two important points
-					@@ coarse-graining is necessary to resist noise
-					@@ The information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
 
 		\end{ants}
-
-		\subsection{firing rate coding}
-
-			\begin{ants}
-
-				@ temporal coarse-graining
-
-			\end{ants}
-
-		\subsection{Population coding}
-			\begin{ants}
-				@ Population coding is the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
-
-				@ \rewrite{
-					As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}
-
-				@ \rewrite{
-					Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
-These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
-
-				@ The diverse response selectivity of sensory neurons
-
-				@ \rewrite{
-					How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
-
-				@ \rewrite{
-					Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
-					} \cite{binder2009encyclopedia}
-
-			\end{ants}
-
-			% ============================================================================ %
-			% review ref
-			% ============================================================================ %
-			% \cite{Stanley2013}		
-			% \cite{QuianQuiroga2009}
-
-		\subsection{sensory hierarchy}
-
-			\begin{ants}
-				@ Sensors can only receive partial information
-
-				@ Through coarse-graining, higher level cortical areas can integrate those partial information to infer hidden causes.
-
-			\end{ants}
-
-		\subsection{The advantage of NCG}
-			\subsubsection{Resist to noise}
-				* \rewrite{ The population will therefore be relatively insensitive to the loss of
-					cells or noise in a small number of cells} \cite{eurich2000multidimensional}
-
-			\subsubsection{Operate on deterministic and abstract level}
-			\subsubsection{Predictive power}
-			\subsubsection{Reduce energy cost}
-
-		\subsection{neural coarse-graining in deep learning}
-			\martin{todo}
-
-	\section{Non-trivial Information Closure} 
-		\martin{todo}
 
@@
 
+	\section{neural coarse-graining}
+
+		\begin{ants}
+			@ Definition of coarse-graining
+				@ \rewrite{Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
+
+				@ \rewrite{a number of different microstates,First, typically a number of different microstates, will realize the same value of the macro-variables of upper level causal theories. 
+				}
+
+			@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
+
+		\end{ants}
+
+		\subsection{coarse-graining in neural system}
+		\subsection{Single neurons are noisy}
+
+			\begin{ants}
+				@ \rewrite{
+					neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.}
+
+				@ This fact leads to two important points
+					@@ coarse-graining is necessary to resist noise
+					@@ The information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
+
+			\end{ants}
+
+		\subsection{firing rate coding}
+
+			\begin{ants}
+
+				@ temporal coarse-graining
+
+			\end{ants}
+
+		\subsection{Population coding}
+			\begin{ants}
+				@ Population coding is the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
+
+				@ \rewrite{
+					As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}
+
+				@ \rewrite{
+					Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
+These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
+
+				@ The diverse response selectivity of sensory neurons
+
+				@ \rewrite{
+					How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
+
+				@ \rewrite{
+					Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
+					} \cite{binder2009encyclopedia}
+
+			\end{ants}
+
+			% ============================================================================ %
+			% review ref
+			% ============================================================================ %
+			% \cite{Stanley2013}		
+			% \cite{QuianQuiroga2009}
+
+		\subsection{sensory hierarchy}
+
+			\begin{ants}
+				@ Sensors can only receive partial information
+
+				@ Through coarse-graining, higher level cortical areas can integrate those partial information to infer hidden causes.
+
+			\end{ants}
+
+		\subsection{The advantage of NCG}
+			\subsubsection{Resist to noise}
+				* \rewrite{ The population will therefore be relatively insensitive to the loss of
+					cells or noise in a small number of cells} \cite{eurich2000multidimensional}
+
+			\subsubsection{Operate on deterministic and abstract level}
+			\subsubsection{Predictive power}
+			\subsubsection{Reduce energy cost}
+
+		\subsection{neural coarse-graining in deep learning}
+			\martin{todo}
+
 	\section{A neural coarse graining theory of consciousness}
-		* We claim that the coarse-grained state in the information closure determines contents of 
-		consciousness. 
-		* It's important that not the neural states but the coarse-grained state determine contents
-		of consciousness.
+		\toWrite{Need to describe my intuition more concretely }
+
+		\begin{ants}
+			@ We claim that the coarse-grained state in the information closure determines contents of consciousness.
+
+			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
+
+			@ Consciousness is information 
+				@@ Information is level-dependent.
+
+				@@ Information is different at microscopic and macroscopic levels
+
+				@@ Consciousness must be level-dependent
+
+			@ \rewrite{
+				This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
+
+				@@ conscious perception are very stable and time invariant.
+				@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
+
+		\end{ants}
 
@@
 		\subsection{Conscious contents}
-		\subsection{Sensory hierarchy and neural coarse-graining}
+		\subsection{Sensory hierarchy and neural coarse-graining
+			\todo[color=Red]{This is super important. I need to deal with this very carefully.}}
 
@@
 				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining
+
+				@ It is possible that the neural system represents higher-level information processing by low level physical subtract.
+For example, studies have found representation for summery statistics of signal and neural.
+population.\needref{neural representation for summery statistics}\\
+				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
+
 			\end{ants}
@@
 
+		\begin{ants}		
 			% ============================================================================ %
@@
 			% Internal self-predictive mechanism	
-		* Recent biological evidence suggests that low-level neurons encodes predictive information about external  and
+			@ Recent biological evidence suggests that low-level neurons encodes predictive information about external  and
 
-		\todo{need to say this is exactly the non-trivial information closure, and refer to equation XXX}
-		\cite{sederberg2018learning}
-		\rewrite{in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
+			@ \toWrite{
+				need to say this is exactly the non-trivial information closure, and refer to equation XXX}
 
-		\rewrite{We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
+			@ \cite{sederberg2018learning}
+			@ \rewrite{
+				in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
 
-		\rewrite{ We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
+			@ \rewrite{
+				We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
 
-		\rewrite{
+			@ \rewrite{
+				We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
+
+			@ \rewrite{
 				Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
@@
 
-		\rewrite{Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
+			@ \rewrite{
+				Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
 
-		\rewrite{ Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
+			@ \rewrite{
+				Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
 
-		* They also showed generalization of internal predictability across stimulus. This suggests .... what?
+			@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
 
-		\rewrite{ The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
+			@ \rewrite{
+				The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
 
-		\cite{Palmer2015}
-		\rewrite{ Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
+			@ \cite{Palmer2015}
+			@ \rewrite{
+				Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
 
-		\todo{\url{http://tinyurl.com/y9zmhlln}	}
-
-		\rewrite{It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
+			@ \rewrite{
+				It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
 3, but the brain has no direct access to visual stimuli except that provided by the retina.
@@
 More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future?
-The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ }
+The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
 
-		\rewrite{ larger groups of cells carry predictive information for hundreds of milliseconds, }
+			@ \rewrite{
+				larger groups of cells carry predictive information for hundreds of milliseconds, }
+
+		\end{ants}
 
@@
 					@@ \rewrite{
-						The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
+						ddThe ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
 Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.\\
@@
 ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33].
-In other words, they typically associate task performance with awareness.
-					}
+In other words, they typically associate task performance with awareness.}
 
@@
 		\subsection{Higher Order Thought theory of consciousness}	
-			\idea{People think a high order representation receives information from the first order representation.
+			\idea{
+				People think a high order representation receives information from the first order representation.
 This may be a misunderstanding.
@@
 
+			\subsubsection{statistical learning/prediction is not conscious}
+				\begin{ants}
+					@ considers the brain as a predictive machine
+					@ According to predictive processing account, conscious contents are the inference results (posterior from Bayesian inference framework) of predictive mechanism.
+
+					@ However, we can see that not all predictive mechanisms in the neural system can be consciously aware of.
+
+					@ So what's the critical difference between them in terms of consciousness?
+
+					@ We argue that when predictive mechanisms utilise the information in the information closure, the predictive result is conscious.
+
+					@ Because the forward model build on the information closure representation can be seen as part of the closure. \todo[color=red]{IS THIS TRUE? NEED DISCUSSION}
+
+					@ we can consider two scenarios
+
+						@@ Predictive information is encoded in neuron populations but there is high entropy of conditional probability which means it's not closure.
+Therefore, the conscious level could be very low even though the it still has some degree of predictability.
+
+						@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not information closured and therefore is not conscious.
+
+						@@ Based on this point of view, predictive power for a system does not guarantee consciousness.
+
+						@@ For example, in active inference \needref{active inference}, action is guided by prediction error so the state of the system is non-closured.
+
+				\end{ants}
+
 		\subsection{IIT}
+			\callforhelp{Help from Jun?}
+
+			\subsubsection{Information Integration}
+				\begin{ants}
+					@ \toWrite{Information integration without awareness}\cite{Mudrik_Faivre_Koch}
+					@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} I would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an information closure representation.
+
+					@ Similarly, it is not \rewrite{consciousness is necessary for multisensory integration}.
+It should be multisensory integration is more likely to create an information closure representation.
+Because in most situations, multisensory signals are generated from hidden causes which may have deterministic dynamic and relation with each other.
+Therefore, to infer the hidden causes and represent the deterministic relations can form information closure representation which is conscious.
+
+				\end{ants}
+
+			\subsubsection{IIT}
+
 			\subsubsection{Hoel's theory}
-				\martin{Do you want to write this session?}
+				\callforhelp{Help from Marting?}
 
@@
 	\section{Counter-intuitive prediction}
+
+		\subsection{information closure}
+			\begin{ants}
+				@ We predict that through coarse-graining, conscious agents create 
+			\end{ants}
+
 		\subsection{Prediction on split-brain (vs IIT)}
@@
 			* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.
+
+	\section{title}
 
@@
 		\subsection{Brain area}
+		\subsection{How to coarse-grain in the neural system}
+			\begin{ants}
+				@ \rewrite{
+					not all causal relationships (or relationships of nomological dependency) among micro-events aggregate up to causal relationships among coarse-grained macro-events that are constituted by those micro-events.
+Instead, whether one gets causation at the macroscopic level will depend (among other things) on the particular coarse-graining that is chosen.} \cite{price2007causation}
+
+				@ \rewrite{
+					It may seem surprising, even counterintuitive, that causal and statistical dependence relationships involving fine grained microscopic variables do not automatically show up in causal and dependence relationships among the macroscopic variables that are realized by the fine grained variables.} \cite{price2007causation}
+
+				@ \cite{jonas2017could} well demonstrated that it is difficult to understand higher-level information processing by the current neuroscience methods.
+
+			\end{ants}
 
@@
 	\section{Conclusion}
-		* NCC: To find NCC, it's not about where and when, it's about scale and level of description
+		\begin{ants}
+			@ Why is this theory better than other theories of consciousness
+			@ NCC: To find NCC, it's not about where and when, it's about scale and level of description			 
+		\end{ants}
 

### 2018-05-31 Paper_neural_coarse_graining_of_consciousness.tex
After discussion for Hierarchy

@@
 				@ Imagining you are a neuron in (a human) Bill's brain.
-Your "responsibility" is to collect neurotransmitters from dendrites, accumulate membrane potential, and finally send a signal to your colleagues through an action potential.
+Your "responsibility" is to collect neurotransmitters through dendrites from your other neurons, accumulate membrane potential, and send a signal to other neurons through an action potential.
 
-				@ You have no idea about whether you are involved in an information processing chain for Bill to see or catch  a ball.
+				@ You have no idea that you are at a neural circuit in Bill's supplementary motor area and is now involved in a motor control processing while Bill reaches his hand to grab a cup.
 
-				@ All you have to do is receiving, computing, and outputting information.
+				@  You are totally ignorant of the intension, the goal, and the motor plan that Bill is having now even thought you are part of the physiological substrate of those "high-level" information.
 
-				@ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour.
+				@ The same story also happens to Bill. In his conscious mind, he is not aware of what you do and even your existence if Bill never studies neuroscience.
+
+				@ It seems that information you are processing and information shows in Bill's conscious percept are divorced from each other.
+
+%				@ All you have to do is receiving, computing, and outputting information. 
+%			
+%				@ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour.
 If your work contributes some part of Bill's conscious perception or intention to act.
@@
 			%% scale
-				@ \rewording{
-					It seems that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.}
+
+				@ It seems true that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.
 
@@
 
+			%% Meaning of IC
+			@ \rewrite{
+				The notion of closure plays a prominent role in systems theory where it is used to identify or deﬁne the system in distinction from its environment} \cite{BERTSCHINGER.2006}
+
+			%% Definition of IC
+			@ Formally, then, a system is informationally closed if (almost) no information flows into it from the environment.
+
+			@ \rewrite{
+				The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.} \cite{BERTSCHINGER.2006}
+
+			@ Mathematically, information closure can be define and measured by as the degree of information flowing from the environment to a system.
+				\begin{equation}
+					\left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \end{array} \right.
+				\end{equation}
+
 		\end{ants}
+
+		% **************************************************************************** %
 
@@
 		\subsection{Mathematical definition of information closure}
-		\rewrite{
-			The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.
-		}\cite{BERTSCHINGER.2006}
 
 		suggests that information closure can be defined as the degree of information flow between environment and the system.
-
-		\begin{equation}
-		\left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \end{array} \right.
-		\end{equation}
 
@@
 
+		\begin{figure}[h]
+			\includegraphics[width=\textwidth]{CGandIC.png}
+			\caption{information closure through neural coarse-graining}
+			\label{fig:CGandIC}
+		\end{figure}
+
 		\begin{ants}
@@
 
+			\begin{figure}[h]
+				\includegraphics[width=\textwidth]{hierarchy.pdf}
+				{Coarse-grain and sensory anatomical hierarchies}
+				\label{fig:hierarchy}
+			\end{figure}
+
+			\begin{figure}[h]
+				\includegraphics[width=\textwidth]{WritingMaterials/HierachyDiscussion (1).jpg}
+%				{Coarse-grain and sensory anatomical hierarchies}
+			\end{figure}
+
 			\begin{ants}
+				@ It's important to note that the dimension coarse-graining direction is not necessary to be align with anatomical sensory hierarchy in the neural system.
+
+				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.
+
 				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining
@@
 
-	\section{title}
-
 	\section{Future work}

### 2018-05-31 Paper_neural_coarse_graining_of_consciousness.tex
Overleaf Test

@@
 
-				@ It seems true that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.
+				@ It seems true that we cannot consciously access information processed at all scale in the neural system.
+Only information at a certain level of coarse-graining is able to become parts of conscious contents.
 
-				@ Information processing of individual neurons are highly noisy. Neurons fires all the time. However, those massive action potentials do not appear in our conscious contents.
+				@ When we focus on microscopic level of the neural system, information processing in individual neurons is highly noisy and state transitions of neurons are stochastic \citep{Goldwyn2011, White2000}.
+However, instead of seeing action potentials and random noise at microscopic levels, conscious contents shows astonishing stability and robustness against to noise in the neural system \citep{mathis1995computational}.
 
-				@ Don't even mention ion channel dynamic.
+				 Neurons fires all the time. However, those massive action potentials do not appear in our conscious contents.
 

### 2018-06-08 Paper_neural_coarse_graining_of_consciousness.tex
Before to Martin

--- 2018-05-31 Paper_neural_coarse_graining_of_consciousness.tex
@@
 
+%% Title style
+\usepackage{stringstrings}
+\usepackage[explicit]{titlesec}
+\usepackage{sectsty}
+%\usepackage{titlesec}
+
+%\sectionfont{\capitalize}
+
+%\newcommand\SentenceCase[1]{%
+%	\caselower[e]{#1}%
+%	\capitalize[q]{\thestring}%
+%}
+%\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{\SentenceCase{#1}\thestring}
+
 %% Useful packages
@@
 \usepackage{authblk}
+\usepackage{float}
+\usepackage{tikz}
 
@@
 \usepackage{acronym}
-\newacro{ntic}{non-trivial information closure}
-\newacro{ic}{information closure}
+\newacro{ntic}{non-trivial informational closure}
+\newacro{ic}{informational closure}
 \newacro{cg}{coarse-grain}
@@
 	% todo
+		% figure
+
+		\newcommand{\includegraphicsTodo}[2][]{%
+			\tcbox[%
+				adjusted title=\LARGE To Be Modified,
+				halign title=right,
+				colbacktitle=Orange!75!White,
+				coltitle=Black,
+				colframe=Red!60!White,
+				boxrule=1mm,
+				colback=white%
+				]{\includegraphics[#1]{#2}}}
 
@@
 			\newcommand{\idea}[1]{\noindent
-				\textcolor{Plum}{[[ #1 ]]\newline}}
+				\textcolor{Plum}{[[ #1 ]]}}
 
@@
 Instead, neurophysiological evidence has been showing that conscious experience tends to covary with information encoded in coarse-grained neural states such as neural population codes.
-We argue that the neural states within the scope of the information closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious.
+We argue that the neural states within the scope of the informational closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious.
 This argument suggests a distinction between conscious and unconscious processing and provides a generic computational framework.
-Finally, using the deep learning network, we can measure information closure in deep hidden layers.
-Our preliminary results show that information closure representation emerged after learning.
+Finally, using the deep learning network, we can measure informational closure in deep hidden layers.
+Our preliminary results show that informational closure representation emerged after learning.
 We further decoded the information from the representation and compared it with human conscious perception.
@@
 
-	\section*{keywords:} 
-	Keywords: theory of Consciousness, information closure, neural coarse-graining, level of analysis
+	\section*{Keywords:} 
+	Keywords: theory of Consciousness, informational closure, neural coarse-graining, level of analysis
 
@@
 			%% Story about a cell
-				@ Imagining you are a neuron in (a human) Bill's brain.
-Your "responsibility" is to collect neurotransmitters through dendrites from your other neurons, accumulate membrane potential, and send a signal to other neurons through an action potential.
+				@ Imagining you are a neuron in Bill's brain.
+Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials.
 
-				@ You have no idea that you are at a neural circuit in Bill's supplementary motor area and is now involved in a motor control processing while Bill reaches his hand to grab a cup.
+				@ You have no idea that you are one of neurons in Bill's supplementary motor area and is now involved in motor control processing while Bill is reaching his hand to grab a cup.
 
-				@  You are totally ignorant of the intension, the goal, and the motor plan that Bill is having now even thought you are part of the physiological substrate of those "high-level" information.
+				@ You are totally ignorant of the intension, the goal, and the motor plan that Bill is having now even thought you are part of the physiological substrate responsible for this action.
 
-				@ The same story also happens to Bill. In his conscious mind, he is not aware of what you do and even your existence if Bill never studies neuroscience.
+				@ The same story also happens to Bill's conscious mind. In his conscious experience, he is unaware of everything you do and even not able to know your existence if Bill never studies neuroscience.
 
@@
 
-%				@ All you have to do is receiving, computing, and outputting information. 
-%			
+				@ \idea{Need a ending sentence here}
+
+				@ ====================================
+
 				% @ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour.
@@
 
-				@ It seems true that we cannot consciously access information at all scale. We can only be aware of information processed at a certain level of coarse-graining in the neural system.
+				@ It seems to be true that we are unable to consciously access information processed at every scale in the neural system.
+Only information at certain levels of coarse-graining is able to be parts of conscious contents.
 
-				@ Information processing of individual neurons are highly noisy. Neurons fires all the time. However, those massive action potentials do not appear in our conscious contents.
+				@ When we focus on microscopic level of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are highly stochastic \citep{Goldwyn2011, White2000}.
+However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious contents shows astonishing stability and high robustness against to ubiquitous noise in the neural system \citep{mathis1995computational}.
 
-				@ Don't even mention ion channel dynamic.
+				% Neurons fires all the time. However, those massive action potentials do not appear in our  conscious contents.
 
-				@ We also lake of experience of whole brain operation. Some parts of our brains process in an unconscious way.
+				@ Likewise, at the macroscopic level, conscious experience does not associate with joint states of the full neural system because we have known that some parts of the neural system process information unconsciously (cerebellum for example \citep{lemon2010life}).
 
-				@ We don't have experience of inter-individual super-consciousness
+				@ Meanwhile, we don't experience "super-consciousness" when we have massive inter-individual interactions with other human-beings.
+Even though evidence has shown several types of collective information processing at human social groups levels \needref{collective intelligent in human, collective memory, collective behavioural, etc.}, those processes seem to depart from our individual conscious contents.
+
+				@ \idea{Need a ending sentence here}
+
+				@ ====================================
 
 			%% our argument
-				@ In this article, we argue that consciousness \highlightAndComment[YellowGreen]{correlates}{Is this proper?} information processing at a certain coarse-graining level which form information closure.
-More specifically, the conscious level is determined by the level of information closure and conscious contents is determined by the states of information closure.
+				@ In this article, we propose that consciousness \highlightAndComment[YellowGreen]{correlates}{Is this proper?} information processing at a certain coarse-grained level where the neural system creates a high degree of non-trivial informational closure.
+We further predict that \textit{levels} of consciousness are determined by the levels of informational closure and \textit{contents} of consciousness are determined by the concurrent states of the informational closure \citep{laureys2005neural, overgaard2010neural}.\todo{There must be a better way to reword this part}
 
-				@ We first introduce non-trivial information closure and its importance for human scale agents.
+			%% About this paper
+				@ In the following sections, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
 
-				@ We then presume that through neural coarse-graining the human brain achieves a non-trivial information closure \highlightAndComment[YellowOrange]{realm}{Need to unify this term} at a specific macroscopic level.
+				@ We argue that through coarse-graining the human neural system can achieves non-trivial informational closure at a specific coarse-grained level.
 
-				@ We then argue that consciousness levels and contents are determines the state of consciousness for both levels and contents.
+				@ We then propose that the state of the informational closure correlates the state of consciousness for both levels and contents which can be explained and computationally quantified and predicted in this theory.
 
-				@ We then discuss how this theory can concisely explain empirical results from previous studies and integrate several current major theories of consciousness.
+				@ We discuss how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness.
 
-				@ We finally provide theory predictions testable approaches.
-
-			%% Advantage 
-				@ This framework provides a concise and quantifiable explanation for all current major theories of consciousness.
-
-				@ This framework provides a more fundamental understanding about why some neural process are conscious but others are not.
+				@ We finally provide predictions and testable approaches for this theory.
 
@@
 
-		==================================================
-		\begin{ants}
-
-			@ consciousness is information
-
-			@ conscious contents
-				@@ \toWrite{lower level}
-				@@ Information processing of individual neurons are noisy.
-				@@ We don't have conscious content changes when individual neurons fire action potentials. 				
-				@@ Don't even mention ion channel dynamic.
-
-				@@ \toWrite{Higher-level dynamic}
-
-			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.
-
-			@ \toWrite{Human tendency for active prediction }
-				@@ \cite{Stahl2015} \rewrite{
-					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore?
+%		==================================================
+%		\begin{ants}
+%			
+%			@ consciousness is information
+%			
+%			@ conscious contents
+%				@@ \toWrite{lower level}
+%				@@ Information processing of individual neurons are noisy.
+%				@@ We don't have conscious content changes when individual neurons fire action potentials. 				
+%				@@ Don't even mention ion channel dynamic. 
+%				
+%				
+%				@@ \toWrite{Higher-level dynamic}
+%
+%				
+%				
+%				
+%				
+%			
+%			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic. 
+%			
+%			
+%			@ \toWrite{Human tendency for active prediction }
+%				@@ \cite{Stahl2015} \rewrite{
+%					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore?
 We found that 11-month-old infants (N = 110) used violations of prior expectations as special opportunities for learning.
@@
 Thus, early in life, expectancy violations offer a wedge into the problem of what to learn.}
+%			
+%			@ Intuitive physics \needref{Intuitive physics}
+%			
+%			@ However, sensory signal are always noisy. 			
+%			
+%			
+%			@ We propose that consciousness is not related to particular neural architectures or location of the neural system.
+%			
+%
+%		\end{ants}
 
-			@ Intuitive physics \needref{Intuitive physics}
+	\section{Non-trivial informational closure\martin{todo}}
 
-			@ However, sensory signal are always noisy.
+		\subsection*{Meaning of informational closure}
+			\begin{ants}
+				@ \rewrite{
+					The notion of closure plays a prominent role in systems theory where it is used to identify or define the system in distinction from its environment} \cite{BERTSCHINGER.2006}
 
-			@ We propose that consciousness is not related to particular neural architectures or location of the neural system.
+				@ \rewrite{
+					Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world.
+This requires a system that can be described as a whole without reference to its environment.
+In systems theory, this property is usually referred to as closure.}\citep{BERTSCHINGER.2006}
+
+				@ \rewrite{
+					These concepts of closure play an important role in the architecture of systems
+					theory, because they are used to
+					1. define the system (in distinction to its environment) and to 
+					2. explain the autonomy of the system.}\citep{BERTSCHINGER.2006}
+
+				@ \rewrite{
+					Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level.
+Knowledge of the microstate will not improve predictions of the macrostate.} \citep[p.
+4]{PFANTE.2014}
 
@@
 
-	\section{\martin{todo}Non-trivial Information Closure}
+		\subsection*{Definition of informational closure}
+
+			\begin{figure}
+				\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-07_17-45-59.png} 
+				\cite{BERTSCHINGER.2006} I need something like this 
+				\caption{xxxx}
+				\label{fig:AgentAndEnv}			
+			\end{figure}
+
 			\begin{ants}				
-
-			%% Meaning of IC
-			@ \rewrite{
-				The notion of closure plays a prominent role in systems theory where it is used to identify or deﬁne the system in distinction from its environment} \cite{BERTSCHINGER.2006}
-
-			%% Definition of IC
 				@ Formally, then, a system is informationally closed if (almost) no information flows into it from the environment.
@@
 
-			@ Mathematically, information closure can be define and measured by as the degree of information flowing from the environment to a system.
+				@ Mathematically, informational closure can be define and measured by as the degree of information flowing from the environment to a system.
+				\begin{equation}\label{eq:InformationFlow}
+				\left.\begin{array}
+				{rl}{J_{n}(E \rightarrow S )} & { = MI(S_{n+1};E_{n}|S_{n})} \\
+				{ } & { = H(S_{n+1}|S_{n})-H(S_{n+1}|S_{n},E_{n})} \\
+				{ } & { = H(E_{n}|S_{n})-H(E_{n}|S_{n},S_{n+1})} \\
+				{ } & { = H(E_{n}|S_{n})-H(E_{n}|S_{n},S_{n+1})}
+				\end{array}\right.
+				\end{equation}
+
+				@ \ref{eq:InformationFlow} can be rewritten as 
 				\begin{equation}
-					\left.\begin{array} { r l } { J _ { n } ( E \rightarrow S ) } & { = M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) } \\ { } & { = H ( S _ { n + 1} | S _ { n } ) - H ( S _ { n + 1} | S _ { n } ,E _ { n } ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \\ { } & { = H ( E _ { n } | S _ { n } ) - H ( E _ { n } | S _ { n } ,S _ { n + 1} ) } \end{array} \right.
+				MI(S_{n+1};E_{n}|S_{n}) = 
+				MI(S_{n+1};E_{n}) - (MI(S_{n+1};S_{n})-MI(S_{n+1};S_{n}|E_{n}))
 				\end{equation}
@@
 
-		% **************************************************************************** %
+		\subsection*{trivial case}
+			\begin{ants}
+				@ However, informational closure could be trivial.
 
-		% ============================== what is closure ============================= %
-		\rewrite{
-			Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world.
-This requires a system that can be described as a whole without reference to its environment.
-In systems theory, this property is usually referred to as closure.
-		}\citep{BERTSCHINGER.2006}
-
-		\rewrite{
-			These concepts of closure play an important role in the architecture of systems
-			theory, because they are used to
-			1. define the system (in distinction to its environment) and to 
-			2. explain the autonomy of the system.
-		}
-
-		\begin{quotation}
-			Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level.
-Knowledge of the microstate will not improve predictions of the macrostate \citep[p.
-4]{PFANTE.2014}.
-		\end{quotation}
-
-		% ======================= trivial informational closure ====================== %
-		\rewrite{A system that is independent from its environment trivially achieves informational 
-			closure.}
-		\citep{BERTSCHINGER.2006}
-
-		\subsection{Mathematical definition of information closure}
-
-		suggests that information closure can be defined as the degree of information flow between environment and the system.
-
-		% =============================== Decompose IC =============================== %				
-		%		\begin{align}
-		%			M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) = M I ( S _ { n + 1} ; E _ { n } ) - ( M I 
-		%( S _ { n + 1} ; S _ { n } ) - M I ( S _ { n + 1} ; S _ { n } | E _ { n } ) )
-		%		\end{align}
-
-		\subsection{Non-trivial information closure}
-		Information closure could be trivial.
+				@ Information closure could be trivial.
 That is, when a system is fully independent from the environment, no information can flow into the system from the environment and also leak to the environment from the system.
 Equa.
-xxxx shows the mathematical description of trivial information closure.
+xxxx shows the mathematical description of trivial informational closure.
 When mutual information between the environment and system future state close to 0, and the system transition is independent from the environment, the system can reach informational closure.
@@
 
-		Therefore, it's important to ensure the informational closure that the system reach is non-trivial.
+				@ \rewrite{
+					A system that is independent from its environment trivially achieves informational closure.}  \cite{BERTSCHINGER.2006}
+					\begin{equation}
+						\left.\begin{array}
+						{l}{MI(S_{n+1};E_{n})=0}\\
+						{MI(S_{n+1};S_{n})-MI(S_{n+1};S_{n}|E_{n})=0}
+						\end{array}\right.
+					\end{equation}
+			\end{ants}
 
-		\todo{cite 2006 and nic's paper}
-		To achieve non-trivial information closure
-		\citep{BERTSCHINGER.2006}\\
+		\subsection*{Non-trivial informational closure}
+			\begin{ants}
+
+				@ \citep{BERTSCHINGER.2006}
+				@ \citep{guttenberg2016neural}
+
+				@ \rewrite{The “informational closure” becomes non-trivial if the state contains information about the environment, i.e. $MI(S_{n+1};E_{n})\neq0$}
+
+				@ We can define non-trivial informational closure (NTIC)
+
+				@ Definition:\callforhelp{Which def is better? }
+
+					@@
+					\begin{equation}
+					N T I C = H ( Y _ { t + 1} ) - H ( Y _ { t + 1} | Y _ { t } )
+					\end{equation}
 					\citep{guttenberg2016neural}
 
-		% ============================================================================ %
-		%                           I don't know what happen                           %
-		% ============================================================================ %		
-		%		\begin{equation}	
-		%			\begin{align}
-		%				{ M I ( S _ { n + 1} ; E _ { n } ) } &= 0&\textmd{and}\\ 
-		%				M I ( S _ { n + 1} ; S _ { n } ) - M I ( S _ { n + 1} ; S _ { n } | E _ { n } ) &= 0
-		%			\end{align}
-		%		\end{equation}
-		% ???????????????????????????????????????????????????????????????????????????? %
+					@@
+					\begin{equation}
+					\left.\begin{array}{l}{ N T I C  : = M I ( S _ { n + 1} ; E _ { n } ,\dots ,E _ { n - m } ) - M I ( S _ { n + 1} ; E _ { n } ,\dots ,E _ { n - m } | S _ { n } ) }\\{  = M I ( S _ { n + 1} ; E _ { n } ,\dots ,E _ { n - m } ) - M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) }\end{array} \right.
+					\end{equation}
+					\cite{BERTSCHINGER.2006}
 
-		\subsection{how to achieve non-trivial information closure}
-		* Through coarse-graining
-		* Accurately model deterministic environment 
-		\rewrite{
+				@ \rewrite{Modeling: The system reaches synchronization and internalizes the correlations observed in the environment by building up own structures.}
+
+			\end{ants}
+
+		\subsection*{Achieve non-trivial informational closure}
+			\begin{ants}
+
+				@ Accurately model deterministic environment 
+				@ \rewrite{
 					This demonstrates that a system exhibiting certain internal regularities as measured by $A^* = MI(Sn+1; Sn)$ can achieve informational closure either by gaining information about the environment or by increased autonomy, i.e.
@@
 modeling, and autonomy can be considered as complementary strategies for achieving informational closure.}
-		* by Action
 
-		\subsection{information closure and Level Identification}
+				@ By Action
 
-		\subsection{Biological Creature may try to achieve closure even the environment is not }
-
-	\section{neural coarse-graining}
-
-		\begin{ants}
-			@ Definition of coarse-graining
-				@ \rewrite{Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
-
-				@ \rewrite{a number of different microstates,First, typically a number of different microstates, will realize the same value of the macro-variables of upper level causal theories. 
-				}
-
-			@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
+				@ In the next section, we claim that the neural system achieve NTIC through coarse-graining.
 
@@
 
-		\subsection{coarse-graining in neural system}
-		\subsection{Single neurons are noisy}
+		\subsection*{informational closure and level identification \ideaCallout{maybe not necessary}}
+
+		\subsection*{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}
+
+	\section{Neural coarse-graining}
 
 		\begin{ants}
+
+			%% About coarse-graining
+%			@ \rewrite{
+%				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
+%			
+%			
+%			@ \rewrite{
+%				a number of different microstates,First, typically a number of different microstates, will realize the same value of the macro-variables of upper level causal theories.}
+%			
+%			
+%			@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
+
+			%% Our argument
+			@ We argues that the human neural system to achieve NTIC at a certain level of coarse-graining.
+
+			%% Macroscale Deterministic
+			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions \highlightAndComment{at a show time scale}{is this necessary?} are nearly deterministic.\callforhelp{Is there any good ref I can cite?}
+
+			@ \idea{Need something here}
+
+			%% Noise
+			@ However, information processing at the microscopic levels in the neural system is noisy.
+
 			@ \rewrite{
@@
 
-				@ This fact leads to two important points
-					@@ coarse-graining is necessary to resist noise
-					@@ The information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
+			%% Partial observable 
+			@ And every individual sensor only receives a little amount of information about the environment.
+
+			@ Therefore, the dynamic of microscopic level is highly stochastic
+
+			%% coarse-graining is necessary
+			@ Hence, to coarse-grain states of microscopic levels is necessary to represent and model the human-scale environment state and dynamics.
+
+			@ Coarse-graining is necessary to resist noise
+
+			@ \rewrite{ The population will therefore be relatively insensitive to the loss of
+				cells or noise in a small number of cells} \cite{eurich2000multidimensional}
+
+			%% About consicousness
+			@ More importantly, the information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
 
@@
 
-		\subsection{firing rate coding}
-
+		\subsection{Coarse-graining in neural system}
 			\begin{ants}
 
+				@ We have known that the neural system uses various coding strategies to encode information at coarse-grained levels.
+
+				@ \toWrite{For examples}
+
+				%% temporal 
 				@ temporal coarse-graining
+
+					@@ firing rate coding
+
+				@ Population coding
+
+					@@ review ref
+
+						@@@ \cite{Stanley2013}
+
+						@@@ \cite{QuianQuiroga2009}
+
+					@@ Population coding is the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
+
+					@@ \rewrite{
+						As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}
+
+					@@ \rewrite{
+						Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
+These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
+
+					@@ The diverse response selectivity of sensory neurons
+
+					@@ \rewrite{
+						How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
+
+					@@ \rewrite{
+						Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
+					} \cite{binder2009encyclopedia}
+
+				@ sensory hierarchy		
+					@@ sensory hierarchy also shows characteristic of coarse-graining
+
+					@@ Due to partial information that sensors can receive
+
+					@@ To form complex representation like shape, objects, coarse-graining is necessary.
+
+					@@ Through coarse-graining, \highlightAndComment{higher level}{might be confusing, need to think about the terminology here} cortical areas can integrate those partial information to infer hidden causes.
 
@@
 
-		\subsection{Population coding}
+		\subsection{\martin{todo}Neural coarse-graining}
+			\begin{figure}
+				\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
+				\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
+				\label{fig:NCG}				
+			\end{figure}
+
 			\begin{ants}
-				@ Population coding is the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
+				@ \citep{guttenberg2016neural} proposed an architecture, called neural coarse-graining (NCG), which aims to captures the emergent large-scale dynamics in the environment.
+
+				@ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.
+
+				@ During training, the objective of the architecture is to XXXXX\martin{todo}
 
 				@ \rewrite{
-					As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}
+					The transform can learn to discard uninformative and unpredictable components of the signal in favor of the features which are both highly predictive and highly predictable.}\citep{guttenberg2016neural}
 
 				@ \rewrite{
-					Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
-These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
-
-				@ The diverse response selectivity of sensory neurons
-
-				@ \rewrite{
-					How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
-
-				@ \rewrite{
-					Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
-					} \cite{binder2009encyclopedia}
-
-			\end{ants}
-
-			% ============================================================================ %
-			% review ref
-			% ============================================================================ %
-			% \cite{Stanley2013}		
-			% \cite{QuianQuiroga2009}
-
-		\subsection{sensory hierarchy}
-
-			\begin{ants}
-				@ Sensors can only receive partial information
-
-				@ Through coarse-graining, higher level cortical areas can integrate those partial information to infer hidden causes.
+					The result is a semi-supervised algorithm which is capable of extracting latent parameters, segmenting sections of time-series with diﬀering statistics, and building a higher-level representation of the underlying dynamics from unlabeled data}\citep{guttenberg2016neural}
 
@@
 		\subsection{The advantage of NCG}
-			\subsubsection{Resist to noise}
-				* \rewrite{ The population will therefore be relatively insensitive to the loss of
-					cells or noise in a small number of cells} \cite{eurich2000multidimensional}
-
-			\subsubsection{Operate on deterministic and abstract level}
+			\subsubsection{Resistant to noise}
 			\subsubsection{Predictive power}
-			\subsubsection{Reduce energy cost}
-
-		\subsection{neural coarse-graining in deep learning}
-			\martin{todo}
+			\subsubsection{Agent can process information and act at abstract levels}
 
@@
 
-		\begin{figure}[h]
-			\includegraphics[width=\textwidth]{CGandIC.png}
-			\caption{information closure through neural coarse-graining}
+		\begin{ants}
+
+			%% reasoning
+				@ Information processing in the neural system exists at different level of abstraction.
+
+				@ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
+
+				@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
+
+				@ This drives the neural system to create a non-trivial informational closure.
+
+				@ \idea{okay, I need to be very careful about the causal relation here.}
+
+				@ Therefore, coarse-graining becomes necessary because every individual sensor and neuron at the microscopic scale can only access and process a small part of information.
+
+				@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:CGandIC})
+
+			%% our claim 
+				@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
+
+				@ We further postulate that level of consciousness corresponds to informational closureness of processes.
+
+				@ The contents of consciousness correspond to the states of the non-trivial informational closure.
+
+			%% Following
+				@ In the following part, we....\todo{todo}
+
+		\end{ants}
+
+		\begin{figure}[H]
+			\includegraphicsTodo[width=\textwidth]{CGandIC.png}
+			\caption{informational closure through neural coarse-graining}
 			\label{fig:CGandIC}
@@
 
+		% ==================================== %
+		% Backup
+		% ==================================== %		
 		\begin{ants}
-			@ We claim that the coarse-grained state in the information closure determines contents of consciousness.
-
 			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
@@
 				@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level. 
+		\end{ants}
+		% ==================================== %
+
+		\subsection{Measure of conscious level}
+			\begin{ants}
+				@ The level of consciousness can be computed from how much degree of the non-trivial informational closure in a coarse-grained scale.
+
+				@ Based on Equation xxx\todo{equation}, the measure of non-trivial informational closure can be decomposed to XXX and XXX.
+
+				@ use \includegraphics{WritingMaterials/PDFXCview_2018-06-01_17-44-30.png}
+
+				@ or use \includegraphics{WritingMaterials/PDFXCview_2018-06-04_19-18-12.png}
+
+				@ To have high level non-trivial informational closure, the states of the coarse-grained scale need to
+
+				@ First, maximise the mutual information between environment and the representation.
+				This term implies that the agent need to maximise predictive power of environmental state.
+This also suggest that the environmental complexity is a crucial factor to the level of consciousness.
+The more rich and complex environment the agent try to predict the higher level of consciousness the agent has.
+
+				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation.
+This term suggests that the representation is self-predicable and it mimics the environmental transition.
+
+				@ Therefore, this theory predicts that level of consciousness determined by the environment that the agent adapts to.
+To form a high non-trivial informational closure, the agent will need to live in a complex environment and model the environmental transition precisely.
+
+				@ \rewording{Note that, our claim is that informational closure is a more fundamental property that correlates consciousness.
+A species acquiring advantage to model a complex environment through evolution and , therefore, achieving a high-level non-trivial informational closure has a high level of consciousness, is the consequence of the evolutional process.
+}
 
@@
 
-		\subsection{Measure of conscious level}
 		\subsection{Conscious contents}
+			\begin{ants}
+				@ We claim that conscious contents correspond to the state of the informational closure.
+
+				@ \idea{= not sure I want to say this here =}
+
+				@ Consciousness is informative.
+A conscious percept including volition and intention is a unique state that narrowing down all possible states into one.
+Therefore, a conscious percept reduces a huge amount of uncertainty.
+
+				@ This is the same claim as the third axiom called "information" in IIT. \needref{information axiom and need to say more about this.}
+
+				@ ====================================
+
+				@ Note that because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale. 
+			\end{ants}
+
 		\subsection{Sensory hierarchy and neural coarse-graining
-			\todo[color=Red]{This is super important. I need to deal with this very carefully.}}
+			\todo[color=Red]{This is super important. I need to deal with this very carefully. Need to completely rewording}}
 
-			\begin{figure}[h]
-				\includegraphics[width=\textwidth]{hierarchy.pdf}
-				{Coarse-grain and sensory anatomical hierarchies}
+			\begin{figure}[H]
+				\includegraphicsTodo[width=0.8\textwidth]{hierarchy.pdf}
+				\caption{Coarse-grain and sensory anatomical hierarchies}
 				\label{fig:hierarchy}
@@
 
-			\begin{figure}[h]
+			\begin{figure}[H]
 				\includegraphics[width=\textwidth]{WritingMaterials/HierachyDiscussion (1).jpg}
@@
 			\begin{ants}
-				@ It's important to note that the dimension coarse-graining direction is not necessary to be align with anatomical sensory hierarchy in the neural system.
+				@ It's important to note that the coarse-graining direction is not necessary to be align with anatomical sensory hierarchy in the neural system.
+
+				@ the coarse-grained information is needed and computed only when the information is required for microscopic scale processing.
+
+				@ \toWrite{I need a strong example here}
+
+				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining
 
 				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.
-
-				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining
 
@@
 Consequently, in systems theory, closure properties and autonomy are considered to be closely related concepts which are both at the heart of defining the system itself.}
-		\subsection{Emperical approaches of measuring neural information closure}
 
-	\section{Biological Evidence of information closure in neural system}
+		\subsection{Empirical approaches of measuring neural informational closure}
+
+	\section{Biological evidence of informational closure in neural system}
 
@@
 
+			@ So far, not so much research on non-trivial informational closure in biological neural systems.
+
+			@ However, \rewording{XXX}
+
 			% Internal self-predictive mechanism	
@@
 			@ \toWrite{
-				need to say this is exactly the non-trivial information closure, and refer to equation XXX}
+				need to say this is exactly the non-trivial informational closure, and refer to equation XXX}
 
@@
 	\section{Relation to empirical findings in neuroscience and consciousness studies}
-		\subsection{reflexive behavioural is unconscious}
+
+		\subsection{Unconscious Processing}
 			\begin{ants}
+				@ According the theory, there are two factor that renders neural processes unconscious.
+
+				@ First, processes are reflexive. This causes non-closured
+
+				@ Second, the abstraction level of the information is below the non-trivial informational closure scale. 
+			\end{ants}
+
+		\subsection{reflexive behavioural is unconscious / or environment-state dependent}	
+			\subsubsection{Reflection}
+				\begin{ants}
+					@ Reflexive systems is not informational closured. 
+					@ Based on our theory, 
 					@ x -> s -> a
 						@@ the system state is determined by environmental state, then it is not conscious. 
-				@ Policy is not conscious
-				@ Patient B.F.
+					@ Therefore, in general, a simple policy network is not conscious. 
 				\end{ants}
 
-		\subsection{Explain normal and abnormal conscious/non-conscious experience}
+			\subsubsection{Blindsight}
+				\begin{ants}
+					@ This also blindsight. 
+					@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
+					@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
+					@ Patient B.F. reactions are stimulus driven. 
+				\end{ants}
 
-		%		Binocular rivalry
-		%		Hallucinations
-		%		subliminal perception
-		%		blindsight    
-		%		reflex is nonconscious
-		%		Procedure memory is state dependent
-		%		from conscious to unconscious processes
-		%		What happen to lesion
-		%		Sleep
+			\subsubsection{procedure memory}
 
-		%		Perceptual overflow
-		%		Discrete vs continuous
-		%		Trace conditioning and delay conditioning
-		%		agnosia
+			\subsubsection{cerebellum}
+				\begin{ants}
+					@ cerebellum feed-forward connections, maybe just a policy network.\needref{cerebellum} 
+				\end{ants}
 
-		%		Attention
-		%		Top-down attention
+		\subsection{Due to level of abstraction}
+			\subsubsection{statistical inference}
+				\begin{ants}
+					@ The computation of Bayesian brain is unconscious.			 
+				\end{ants}
+
+			\subsubsection{subliminal perception}
+
+			\subsubsection{Libet Experiments}
 
@@
 			\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}
+
+	\section{Phenomenology (conscious processing)}
+
+		Binocular rivalry
+		Hallucinations
+		Dream / non-dream sleep
+		planning 
+		imagination
+
+		\subsection{Perceptual overflow}
 
@@
 
-				* Our prediction is, if information that is carried by v1 neurons are necessary to complete information closure, the states of V1 neurons should also co-vary with conscious contents.
+				* Our prediction is, if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.
 
@@
 This may be the result of neural coarse-graining.
-Because contents in information closure look like watching fine-grained information, people may have an wrong impression about it}
+Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it}
 
@@
 
-				@ Therefore, most of the high level cognitions can utilise the state of information closure.
+				@ Therefore, most of the high level cognitions can utilise the state of informational closure.
 
@@
 
-					@ We argue that when predictive mechanisms utilise the information in the information closure, the predictive result is conscious.
+					@ We argue that when predictive mechanisms utilise the information in the informational closure, the predictive result is conscious.
 
-					@ Because the forward model build on the information closure representation can be seen as part of the closure. \todo[color=red]{IS THIS TRUE? NEED DISCUSSION}
+					@ Because the forward model build on the informational closure representation can be seen as part of the closure. \todo[color=red]{IS THIS TRUE? NEED DISCUSSION}
 
@@
 
-						@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not information closured and therefore is not conscious.
+						@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not informational closured and therefore is not conscious.
 
@@
 
-		\subsection{IIT}
-			\callforhelp{Help from Jun?}
-
-			\subsubsection{Information Integration}
+		\subsection{Integrated information theory\callforhelp{Help from Jun?}}
 			\begin{ants}
 				@ \toWrite{Information integration without awareness}\cite{Mudrik_Faivre_Koch}
-					@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} I would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an information closure representation.
+				@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} I would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an informational closure representation.
 
 				@ Similarly, it is not \rewrite{consciousness is necessary for multisensory integration}.
-It should be multisensory integration is more likely to create an information closure representation.
+It should be multisensory integration is more likely to create an informational closure representation.
 Because in most situations, multisensory signals are generated from hidden causes which may have deterministic dynamic and relation with each other.
-Therefore, to infer the hidden causes and represent the deterministic relations can form information closure representation which is conscious.
+Therefore, to infer the hidden causes and represent the deterministic relations can form informational closure representation which is conscious.
 
@@
 
-			\subsubsection{IIT}
+			\subsubsection{Hoel's theory\callforhelp{Help from Marting?}}
+				\ideaBox{This is very important. Need to be careful here.}
 
-			\subsubsection{Hoel's theory}
-				\callforhelp{Help from Marting?}
+				\begin{ants}
+					@ \cite{hoel2016can}
+					@ causal emergence
+					@ \cite{hoel2013quantifying} examined causal power at different coarse-grained scale and show that causal power can be stronger at macro rather than micro levels.
 
-		\subsection{Internal simulation and self-modeling}
+					@ To answer the question about what is the best scale to compute Phi, \cite{hoel2016can} examined causal power at different coarse-grained scale.
+
+					@ Further instigation is needed to elucidate the relationship between our theory and causal emergence
+
+				\end{ants}
+
+		\subsection{Internal simulation and self-modelling}
 
@@
 
-		\subsection{information closure}
+		\subsection{informational closure}
 			\begin{ants}
@@
 
-	\section{Future work}
+	\section{Future works}
 		\begin{ants}
 
-			@ Lack of direct evidence because no one focus on information closure
+			@ Lack of direct evidence because no one focus on informational closure
+
+			@
 
@@
 		\subsection{Brain area}
+		\subsection{attention}
 		\subsection{How to coarse-grain in the neural system}
 			\begin{ants}
+				@ It's not clear what the coarse-graining function is.\todo[color=red]{this should be explained by environmental deterministic}
+
 				@ \rewrite{

### 2018-06-08 Paper_neural_coarse_graining_of_consciousness.tex
to Martin2

@@
 			%% Macroscale Deterministic
-			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions \highlightAndComment{at a show time scale}{is this necessary?} are nearly deterministic.\callforhelp{Is there any good ref I can cite?}
+			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\callforhelp{Is there any good ref I can cite?}
 
@@
 
-			\subsubsection{Hoel's theory\callforhelp{Help from Marting?}}
+			\subsubsection{Hoel's theory\callforhelp{Help from Martin?}}
 				\ideaBox{This is very important. Need to be careful here.}

### 2018-06-13 Paper_neural_coarse_graining_of_consciousness.tex
to Martin4
After ARC

@@
 \usepackage{sectsty}
-%\usepackage{titlesec}
-
-%\sectionfont{\capitalize}
-
-%\newcommand\SentenceCase[1]{%
-%	\caselower[e]{#1}%
-%	\capitalize[q]{\thestring}%
-%}
-%\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{\SentenceCase{#1}\thestring}
-
-%% Useful packages
+
+%% ============================== Useful packages ============================= %
 \usepackage[dvipsnames,table,xcdraw]{xcolor}
@@
 
-%% acronym
+%% ================================== acronym ================================= %
 \usepackage{acronym}
@@
 \usepackage{tcolorbox}
+\usepackage{comment}
 
@@
 			}
+
+	% Writing Materials
+		\newenvironment{writingMaterials}
+			{	
+				\begin{tcolorbox}[size=small, colframe=black!20!white, toprule=1mm]
+					Writing Materials
+				\end{tcolorbox}
+
+				\begin{easylist}[itemize]		
+			}
+			{
+				\end{easylist}
+				\begin{tcolorbox}[size=small, bottomrule=1mm, halign=flush right, colframe=black!20!white]
+					Writing Materials
+				\end{tcolorbox}			
+			}
+
 % Funcitonal content
@@
 		% figure
-
 		\newcommand{\includegraphicsTodo}[2][]{%
@@
 	% Highlight
-		\newcommand{\highlight}[2][Yellow]{\colorbox{#2}}
+		\newcommand{\highlight}[2][Yellow]{\colorbox{#1}{#2}}
 
@@
 		% text idea
-			\newcommand{\idea}[1]{\noindent
-				\textcolor{Plum}{[[ #1 ]]}}
+			\newcommand{\idea}[2][Plum]{\noindent
+				\textcolor{#1}{[[ #2 ]]}}
 
@@
 
+% ============================================================================ %
+%                                     Body                                     %
+% ============================================================================ %
 \begin{document}
@@
 
+				@ \todo{Do I need a figure?}
+					\begin{figure}
+						\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
+						\cite{pennartz2017consciousness}
+						\caption{xxxx}
+	   			   	\end{figure}
+
 		\end{ants}
@@
 
-		\subsection*{Meaning of informational closure}
+		\subsection{Meaning of informational closure}
 			\begin{ants}
@@
 
-		\subsection*{Definition of informational closure}
+		\subsection{Definition of informational closure}
 
@@
 
-		\subsection*{trivial case}
+		\subsection{Trivial case}
 			\begin{ants}
@@
 
-		\subsection*{Non-trivial informational closure}
+		\subsection{Non-trivial informational closure}
 			\begin{ants}
@@
 
-		\subsection*{Achieve non-trivial informational closure}
+		\subsection{Achieve non-trivial informational closure}
 			\begin{ants}
@@
 
-		\subsection*{informational closure and level identification \ideaCallout{maybe not necessary}}
-
-		\subsection*{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}
+		\subsection{Informational closure and level identification \ideaCallout{maybe not necessary}}
+
+		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}
 
@@
 		\subsection{The advantage of NCG}
-			\subsubsection{Resistant to noise}
-			\subsubsection{Predictive power}
-			\subsubsection{Agent can process information and act at abstract levels}
+			\begin{comment}
+				@ Resistant to noise
+				@ Predictive power
+				@ Agents can process information and act at abstract levels
+			\end{comment}
 
@@
 				@ The contents of consciousness correspond to the states of the non-trivial informational closure.
+
+				@ \idea[red]{I need to somehow acknowledge \cite{pennartz2017consciousness}}
+					@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}
+
+					@@ pennartz levels are defined by functional elements call "functional ensembles".
+\cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}
 
@@
 		\begin{ants}
+
+			@ \rewrite{ 
+				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}
+
+				@@ Oppenheim , P.
+, \& Putnam , H.
+( 1958 ).
+Unity of science as a working hypothesis .
+In H.
+Feigl , G.
+Maxwell , \& M.
+Scriven (Eds.), Concepts, theories, and the mind – body problem (pp.
+3 – 36 ).
+Minneapolis : University of Minnesota Press .
+				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
+				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
+				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
+				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
+				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press .
+
 			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
@@
 		\subsection{Sensory hierarchy and neural coarse-graining
-			\todo[color=Red]{This is super important. I need to deal with this very carefully. Need to completely rewording}}
+			\todo[color=Red]{This is super important. I need to deal with this very carefully. Need to completely rewording}}\label{sec:SensoryHierarchy}
 
@@
 
-	\section{Relation to empirical findings in neuroscience and consciousness studies}
+	\section{Relation to empirical findings in neuroscience and studies of consciousness}
 
@@
 
-		\subsection{reflexive behavioural is unconscious / or environment-state dependent}	
+		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
 			\subsubsection{Reflection}
@@
 
-		\subsection{Due to level of abstraction}
+		\subsection{Under the level of informational closure}
 			\subsubsection{statistical inference}
@@
 			\subsubsection{subliminal perception}
-
+				\begin{ants}
+					@ Above chance performance can be performed through non-closure pathway (reflexive behaviours)
+
+					@ Due to coarse-graining, mapping between changes of microstate
+				\end{ants}
 			\subsubsection{Libet Experiments}
@@
 
-	\section{Phenomenology (conscious processing)}
-
-		Binocular rivalry
-		Hallucinations
-		Dream / non-dream sleep
-		planning 
-		imagination
-
+	\section{About Phenomenology (conscious processing)}
 		\subsection{Perceptual overflow}
+		\subsection{Planning}
+		\subsection{Imagination}
+		\subsection{Dream vs non-dream sleep}
+		\subsection{Binocular rivalry}
+		\subsection{Hallucinations}
+		\subsection{Synaesthesia}
 
 	\section{Comparison with other theories}
-		\subsection{Intermediate Level Theory}
-
-			\begin{ants}
+
+		\subsection{Theories about level of abstraction and coarse-graining}
+			\begin{ants}
+				@ Before the current theory, several theories and perspectives of consciousness have proposed the notion that links level of abstraction or coarse-graining in the neural system to consciousness.
+
+				@ We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal. 
+			\end{ants}
+
+			\subsubsection{Intermediate Level Theory}
+				\begin{ants}
+					@ Intermediate Level Theory (ILT) proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy.
+\citep{prinz2007intermediate, jackendoff1987consciousness}.
+This theory claims that consciousness only associates with the representation at  intermediate levels rather than the ones at lower-level or higher-level.
+
+					@ A critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of  anatomical processing levels along cortical hierarchies.
+				\end{ants}
+
+				\begin{comment}
+					%% Back up materials
 					@ \rewrite{
@@
 Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}
-			\end{ants}
+
+					%% Our theory
+					@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain.
+The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}
+				\end{comment}
 
@@
 
-		\subsection{first-order theories}
-			\begin{ants}
-				@\cite{lau2011empirical}
-					@@ \rewrite{
-						ddThe ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.\\
-						Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26].\\
+		\subsection{First-order theories}
+			\begin{writingMaterials}
+				@\rewrite{
+					The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
+Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.
+Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26].
 Most ﬁrst-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g.
@@
 ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33].
-In other words, they typically associate task performance with awareness.}
-
-			\end{ants}
-
-		\subsection{Global Workspace Theory (GWT)}
+In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}
+
+				@ Among those are first-order theories, on which a mental state is conscious if being in that state results in one’s being conscious of something;
+
+				@  According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action.
+So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.
+
+			\end{writingMaterials}
+
+		\subsection{Global workspace theory}
+
+			\begin{ants}
+
+				%% Introduction
+				@ Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules.
+Only the information that is accessed by the global workspace can be conscious aware of.
+The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules.
+Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.
+
+				%% Our theory
+
+				@ GW in previous data is the place that form NTIC.
+
+				@ non-linearity and emergence
+
+				@ what's the different prediction?
+
+				@ We predict that when the new
+
+			\end{ants}
+
 			\subsubsection{Global availability and Broadcasting}
@@
 
-				\end{ants}
-
-			\subsubsection{broadcasting}
+					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and ampliﬁed non-linearly into a full-blown state of high-level activity.
+This global ‘ignition’ has been proposed as a marker of conscious perception [70].
+Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear ampliﬁcation of activation which invades a distributed set of parietal, prefrontal and cingulate areas
+				\end{ants}
+
+			\subsubsection{Broadcasting}
 
 			\subsubsection{Ignition}
-				\toWrite{Explain ignite}
+				\begin{writingMaterials}
+					@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
+Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
+A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
+Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed
+				\end{writingMaterials}
 
@@
 		\subsection{Sensorimotor contingency}
+			\begin{ants}
+				%% SMC
+
+				@ Sensorimotor contingency (SMC) theory of consciousness is proposed to account of conscious perception.
+It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
+
+				@ The theory radically rejects the view that conscious contents is associated with information encoded in internal representations in the neural system.
+
+				@ Rather, the quality of conscious perception depends on agents' mastery of SMCs.
+
+				@ It emphasizes the importance of the interactions between a system (the neural system) and its.
+
+				@ Counter-intuitively, because consciousness inhabits in interactions between agents and environments, this theory suggests that consciousness is not driven by brain activities.
+Instead, consciousness should be shaped by the way of interaction, i.e.
+SMCs, between agents and environments.
+
+				%% Our theory
+
+				@ Similar to the SMC theory, our theory predicts that the interaction between the neural system and the environment shapes the quality of conscious perception.
+
+				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \todo[color=red]{I NEED A EQUATION!}).
+
+				@ This suggests the to maximise NTIC the NTIC process needs to involve the information about the environmental transition and dynamic after agent preforms an action.
+
+				@ Therefore, as a consequence of maximising NTIC, the representation forming NTIC implicitly encodes information about SMCs.
+
+				@ In the long-term, once NTIC neural dynamic interoperates the environmental state transition given actions via maximising NTIC, the state space of XXX then is shaped by the new learned SMC
+
+				@ Accordingly, the way how the agent interacts with the environment influences the structure of the NTIC representation.
+
+				@ \todo{Need to involve some sentence from  }
+
+				@ \idea{Do I need a figure here?}
+
+				@ However, in contrast to the SMC theory, our theory suggests the state of NTIC process correlate conscious contents.
+Therefore, if the NTIC process is formed inside the neural system, we should have correspondent conscious contents in our conscious experience without interacting with the environment.
+
+				@ \idea{Not sure here} This can easily explain that the conscious experience of dream is just induced by self-evolved state changes of the NTIC process.
+
+				@ Further more the SMC and our theories make complete different prediction about the relationship between SMC and consciousness.
+
+				@ Contrary to the SMC theory which suggests that consciousness resides on SMCs, our theory predicts that pure S-R contingency between the neural system and the environment can not achieve informational closure within the neural system and therefore is not conscious (please see section \ref{sec:reflexive})
+
+			\end{ants}
+
+			\begin{comment}
+
+				%% Intro about this theory
+				@ O’Regan and Noë
+
+				@ In their seminal article O’Regan and Noe¨ (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.
+
+				@ In short, different types of SMCs give rise to different qualities of sensory experience
+
+				@  Second, vision, audition, touch, etc., correspond to domains of knowledge of the respective SMCs that are exercised by an agent as part of its habitual behavior.This ‘‘mastery of SMCs’’ is what lets an agent perceive its environment and adapt its behavior accordingly
+
+				@ And third, sensory awareness arises when SMCs are integrated with planning, reasoning, and generation of behavior
+
+				@ The theory is a radical departure from the classical view that the brain constructs an internal representation of the outside world on which higher cognitive processes such as memorizing, reasoning, and planning operat
+
+				@ perception depends on a practical mastery of sensorimotor dependencies or “sensorimotor contingencies” (SMCs)
+
+				@ s the importance of brain-body-world interactions in cognitive processes.
+On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.
+
+				@ ways of acting or as something we do, rather than an internal phenomenal experience or an internal representation of the world (O’Regan \& Noë, 2001)
+
+				@ \rewrite{I advance this truly astonishing hypothesis: To understand consciousness in humans and animals, we must look not inward, into the recesses of our insides; rather, we need to look to the ways in which each of us, as a whole animal, carries on the processes of living in and with and in response to the world around us .
+.
+.
+You are not your brain .
+.
+.
+Meaningful thought arises only for the whole animal dynamically engaged with its environment .
+.
+.
+And indeed the same is true for the quality of our conscious episodes .
+.
+.
+The taste of licorice is not something that happens in our brains.} (Noë, 2009, pp.
+7–8)
+
+				@ Because consciousness resides in our behavioural interactions with the world rather than in our brain, the theory postulates that consciousness does not derive from brain activity at all.
+Consequently, there is no need to explain how brain activity causes or constitutes consciousness, because it does not.
+
+				@ O ’ Regan, J.K. and Noë, A. (2001) A sensorimotor account of vision and visual consciousness. Behav. Brain Sci. 24, 939 – 973
+
+				@ SMC theory argues that consciousness arises from the execution of SMCs, resulting in brain – environmental interactions.
+
+				@ The second variant of SMC theory postulates that ‘ it is not movement as such, but the consequences of potential movement that play a role ’ (in perceptual experience) ([5], p.
+1015; see also [9,10,19,20]).
+This ‘ non-acute ’ or dispositional variant marks a signi ﬁ cant shift in position because it de-emphasizes actual movement.
+\cite{pennartz2017consciousness}
+
+				@ It stipulates that for us to be conscious of something in the environment (or of our way of interacting with the environment)
+
+			\end{comment}
+
 		\subsection{Predictive Brain}
@@
 
-		\subsection{Internal simulation and self-modelling}
-
-	\section{Counter-intuitive prediction}
+		\subsection{Internal simulation and self-modelling theory}
+
+	\section{Theory predictions (Counter-intuitive prediction)}
 
@@
 
-			@
-
-		\end{ants}
-
-		\subsection{Brain area}
-		\subsection{attention}
-		\subsection{How to coarse-grain in the neural system}
+		\end{ants}
+
+		\subsection{About location of NTIC}
+		\subsection{Attention}
+%		\subsection{We didn't specify what dynamic in the NTIC process associates with conscious contents.}
+		\subsection{Finding coarse-grain function}
 			\begin{ants}
@@
 
-	\section{Evolution of conscious mind (not sure but if I have time)}
-		\cite{dennett2008kinds}
+%	\section{Evolution of conscious mind (not sure but if I have time)}
+%		\cite{dennett2008kinds}
 

### 2018-07-02 Paper_neural_coarse_graining_of_consciousness.tex
Save before branching

@@
 			%% our claim 
+				@
+
 				@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
@@
 					@ Reflexive systems is not informational closured. 
-					@ Based on our theory, 
+					@ Base	d on our theory, 
 					@ x -> s -> a
@@
 		\subsection{Perceptual overflow}
+		\subsection{Volition and freewill}
+			\begin{ants}
+				@ Volition is a result of coarse-graining
+
+				@ Lebel's experiment can be well explained by the experiment.
+			\end{ants}
+
 		\subsection{Planning}
@@
 
-			\begin{comment}
+			\begin{comment} % materials
 
@@
 				@ O’Regan and Noë
+
+				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan & Noë, 2001).
+The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson & Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes.
+On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.
+A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan & Noë, 2001).
+}
 
@@
 
-		\subsection{Predictive Brain}
-
-			* Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}
-
-			* Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.
-
-			* More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.
-
-			* Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.
-
-			* Note that, a system showing some predictive power is not sufficient to be conscious.
-
-			* For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future.
+		\subsection{Predictive Processing}				
+			\begin{ants}
+				%% Introduce PP
+				@ The predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, "Bayesian brain hypothesis"
+
+				@ is a powerful framework
+
+				@ a recent emerged theoretical framework of perception and brain function, which suggests that the brain continuously generates and updates predictions about incoming sensory signals, represents a general principle of neural functioning.
+
+				@ According to predictive processing (PP) account of perception, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment.
+The perceptual contents are the "best guess" about the environment 	\cite{clark_2013}			\cite{Hohwy2013}
+
+				@ Bperceptual content is the result of probabilistic inference on the hidden causes of sensory signals.
+
+				@ Because it is well integrated with Bayesian brain hypothesis, the PP framework has been used to interpret conscious perception in many perceptual domain. \cite{Hohwy2013} \cite{SethPP2014}
+
+				%% The gaps between pp and consciousness
+				@ However, to link PP to consciousness, there are still two major gaps.
+
+					@@ First, previous studies have demonstrated many brain processes following the principle of Bayesian inference and Bayesian integration.
+But not all these processes are conscious.
+This indicates that PP is not a sufficient mechanism for conscious perception.
+Some other factors may be involved to determine which PPs can be conscious or not.
+
+					@@ Second, it has been emphasized that only the results of the inference or prediction can be consciously accessed. The process of inference in completely unconscious. So WHY?
+
+				@ Even though PP has been acquiring attention in different discipline in neuroscience, So far, to our knowledge, no detailed explanation has been given to account for the two questions.
+
+				%% Our theory
+
+				% 2018/06/15 15:10
+				@ We first hypothesize that predictive processing stays unconscious is because it is not able to achieve NTIC.
+
+					@@ \toWrite{Example from PID controller}
+
+				@ Second, according to our theory, it is obvious that the computation of predictive processing is unconscious and only the result is conscious.
+Because the computational details is not at the coarse-grained level which achieves NTIC.
+
+					@@ So far, many neuronal models and coding schema have been proposed to explain how to implement Bayesian inference and prediction at the neuronal level.
+
+					@@ However?
+
+				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.
+
+			\end{ants}
+
+			\begin{writingMaterials}
+
+				%% About the unconscious Bayesian processing
+				@ \cite{lamme2015predictive}
+					@@ To my knowledge, this is the first time this has been so explicitly laid out—writers on predictive coding thus far have always stayed a little vague on where exactly consciousness sits in the Bayesian framework.
+
+					@@ Yet the two points seem contradictory. In the Bayesian predictive coding framework, consciousness is the result of the unconscious inferential processes.
+
+					@@ However, these authors have so far been very reticent about how exactly consciousness ﬁts into the PC framework.
+For now, there is an emerging idea that understands consciousness as the ﬁnal result of unconsciousness processing.
+According to Hohwy (2013), perceptual consciousness ﬁts in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences.
+Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process.
+Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs.
+Karl Friston agrees to a certain extent with this interpretation of consciousness.
+According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).
+
+				@ Link PP and c
+					@@ \cite{hobson2016response}
+					@@ \cite{Melloni2015}
+
+				%% ----------------------------------------------------------------------------
+				@ \cite{SethPP2014}
+
+				@ When uncertainty is high, we should expect an increase in the ability of ever higher-level prior beliefs to determine conscious experience. I
+
+				@ determine conscious experience.
+
+				@ PP combines and builds upon previous ideas about the role of “unconscious inference” in perception (Helmholtz, 1925; Barlow, 1961; Gregory, 1970), the process of “analysis by synthesis” in psychology (Neisser, 1967), the “predictive coding” approach in neuroscience (Srinivasan et al., 1982; Rao and Ballard, 1999; Huang and Rao, 2011) and “generative models” and related probabilistic computational principles (MacKay, 1956; Mumford, 1992; Dayan et al., 1995; Hinton, 2007a,b; Tenenbaum et al., 2011).
+
+				@ \rewrite{The brain is constantly confronted with a wealth of sensory information that must be processed efficiently to facilitate appropriate reactions.
+One way of optimizing this processing effort is to predict incoming sensory information based on previous experience so that expected information is processed efficiently and resources can be allocated to novel or surprising information.
+Theoretical and computational studies led to the formulation of the predictive coding framework (Friston 2005, Hawkins and Blakeslee 2004, Mumford 1992, Rao and Ballard 1999).
+Predictive coding states that the brain continually generates models of the world based on context and information from memory to predict sensory input.
+In terms of brain processing, a predictive model is created in higher cortical areas and communicated through feedback connections to lower sensory areas.
+In contrast, feedforward connections process and project an error signal, i.e.
+the mismatch between the predicted information and the actual sensory input (Rao \& Ballard, 1999).
+The predictive model is constantly updated according to this error signal.
+}
+
+				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is speciﬁed by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals.
+According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1).
+Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to ﬁt the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to ﬁt the model).}
+
+				@ \rewrite{In terms of brain function, Hermann von Helmholtz’s 19th Century notion of perception as unconscious inference has found new momentum in modern formulations of ‘predictive processing’, the Bayesian brain, and the ‘free energy principle’ (Clark, 2013; Friston, 2010; Hohwy, 2013).
+On these formulations, which can all be subsumed under the general term ‘prediction error minimization’ (PEM, (Hohwy, 2013)) perceptual content is the result of probabilistic inference on the hidden causes of sensory signals.
+}
+
+				@ \rewrite{Generative models encoded by brain structure and dynamics make predictions about sensory inputs, based on prior expectations.
+Action (e.g., body movements) and perception conspire to reduce sensory prediction errors, giving rise to perceptual content and}
+
+				@ \rewrite{More informally, what we perceive is the brain’s ‘best guess’ of what’s out there (or ‘in here’, for perceptions of body and self).}
+
+				@ \rewrite{“ predictive processing ” (PP) 1 or the “ Bayesian brain ” this holds that perceptual content is determined by hierarchically organized generative (i.e., predictive) models (HGMs) of the external causes of sensory signals, induced by a process approximating Bayesian inference (Friston, 2009).}
+
+				@ Not all predictive mechanism are conscious.
+
+				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.
+
+				@ we can also explain why only the result (posterior) of predictive processing is conscious.
+
+				@ Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}
+
+				@ Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.
+
+				@ More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.
+
+				@ Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.
+
+				@ Note that, a system showing some predictive power is not sufficient to be conscious.
+
+				@ For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future.
 Derivative action predicts system behaviour and thus improves settling time and stability of the system.
 
-			* However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.
+				@ However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.
 
@@
 
-			* Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.
+				@ Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.
+
+			\end{writingMaterials}
 
@@
 		\subsection{Attention}
+			Attention can be when the neural want to output a specific information in NTIC.
+
 %		\subsection{We didn't specify what dynamic in the NTIC process associates with conscious contents.}
+
 		\subsection{Finding coarse-grain function}

### 2018-07-05 Paper_neural_coarse_graining_of_consciousness.tex
Rearranged

@@
 
-			\begin{figure}
-				\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-07_17-45-59.png} 
-				\cite{BERTSCHINGER.2006} I need something like this 
-				\caption{xxxx}
-				\label{fig:AgentAndEnv}			
-			\end{figure}
-
-			\begin{ants}				
-				@ Formally, then, a system is informationally closed if (almost) no information flows into it from the environment.
-
-				@ \rewrite{
-					The notion of informational closure refers to a situation where the information flow between the environment and the system tends to zero.} \cite{BERTSCHINGER.2006}
-
-				@ Mathematically, informational closure can be define and measured by as the degree of information flowing from the environment to a system.
+			\noindent Information flow $J_{t}$ from environment $E$ to a system $Y$ at time $t$ can be defined as			
 				\begin{equation}\label{eq:InformationFlow}
 				\left.\begin{array}
-				{rl}{J_{n}(E \rightarrow S )} & { = MI(S_{n+1};E_{n}|S_{n})} \\
-				{ } & { = H(S_{n+1}|S_{n})-H(S_{n+1}|S_{n},E_{n})} \\
-				{ } & { = H(E_{n}|S_{n})-H(E_{n}|S_{n},S_{n+1})} \\
-				{ } & { = H(E_{n}|S_{n})-H(E_{n}|S_{n},S_{n+1})}
+				{rl}{J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} \\
+				%{ } & { \ = H(Y_{t+1}|Y_{t})-H(Y_{t+1}|Y_{t},E_{t})} \\
+				%{ } & { \ = H(E_{t}|Y_{t})-H(Y_{t}|Y_{t},Y_{t+1})} \\
+				%{ } & { \ = H(E_{t}|Y_{t})-H(E_{t}|Y_{t},Y_{t+1})}\\
+				{ } & { \ = I(Y_{t+1};E_{t}) - (I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}))}
 				\end{array}\right.
@@
 
-				@ \ref{eq:InformationFlow} can be rewritten as 
+				\begin{figure}
+					\includegraphics[width=\textwidth]{WritingMaterials/SystemAndEnv.pdf} 
+					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
+					\label{fig:SystemAndEnv}	
+				\end{figure}
+
+			\noindent
+			Based on the definition from \cite{BERTSCHINGER.2006}, a system is informational closured when information flow between the environment and the system is close to zero.
+
+			\noindent However, achieving information closure (minimising $J_t$) could be trivial, which means the environment and the system are entirely independent of each other.
 				\begin{equation}
-				MI(S_{n+1};E_{n}|S_{n}) = 
-				MI(S_{n+1};E_{n}) - (MI(S_{n+1};S_{n})-MI(S_{n+1};S_{n}|E_{n}))
+				\begin{aligned}
+				{I(Y_{t+1};E_{t})=0}&&{\Rightarrow}&&{J_{t}(E \rightarrow Y )=0}
+				\end{aligned}
 				\end{equation}
 
-			\end{ants}
+			\noindent In the non-trivial case, the system trying to encode environmental dynamic can also achieve informational closure. This means
+				\begin{equation}
+				I(Y_{t+1};E_{t})\neq0, 
+				\end{equation}
+
+			\noindent And, non-trivial informational closure can be defined as 		
+				\begin{equation}
+				\left.\begin{array}
+				{rl}{NTIC} & {:=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})}\\
+				{ } & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
+				\end{array} \right.
+				\end{equation}
+
+			\noindent Therefore, Maximising NTIC is equivalent to
+				\begin{equation}
+				\begin{aligned}
+				& \text{maximise} & { } & I(Y_{t+1};Y_{t}) & { } & \text{and} \\
+				& \text{minimise} & { } & I(Y_{t+1};Y_{t}|E_{t}) & { }
+				\end{aligned}
+				\end{equation}
 
@@
 	\section{A neural coarse graining theory of consciousness}
-		\toWrite{Need to describe my intuition more concretely }
+		\ideaBox{Need to describe my intuition more concretely}
+
+		\begin{ants}
+			\toWrite{Do I need to start with my philosophical intuition?}
+
+			@ Through coarse-graining, we can define a new set of variables.
+
+			@ If the new set of variables are informational closured, then this creates a new "reality" for all the variables inside.
+
+			@ Reality means the all the information (include variables and the relationships) within the boundary of causal or informational influence between variables.
+
+			@ This is the same as "if a tree falls in a forest" thought experiment.
+
+			@
+
+		\end{ants}
+
+		% ----------------------------------------------------------------------------
 
@@
 			%% our claim
-				@
 
@@
 			\begin{figure}[H]
-				\includegraphics[width=\textwidth]{WritingMaterials/HierachyDiscussion (1).jpg}
+				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
 %				{Coarse-grain and sensory anatomical hierarchies}
@@
 
-	\section{Biological evidence of informational closure in neural system}
-
-		\begin{ants}		
-			% ============================================================================ %
-			%                             sederberg2018learning                            %
-			% ============================================================================ %
-
-			@ So far, not so much research on non-trivial informational closure in biological neural systems.
-
-			@ However, \rewording{XXX}
-
-			% Internal self-predictive mechanism	
-			@ Recent biological evidence suggests that low-level neurons encodes predictive information about external  and
-
-			@ \toWrite{
-				need to say this is exactly the non-trivial informational closure, and refer to equation XXX}
-
-			@ \cite{sederberg2018learning}
-			@ \rewrite{
-				in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
-
-			@ \rewrite{
-				We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
-
-			@ \rewrite{
-				We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
-
-			@ \rewrite{
-				Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
-This suggests that bottom-up prediction may play an important role in sensory processing}
-
-			@ \rewrite{
-				Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
-
-			@ \rewrite{
-				Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
-
-			@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
-
-			@ \rewrite{
-				The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
-
-			@ \cite{Palmer2015}
-			@ \rewrite{
-				Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
-
-			@ \rewrite{
-				It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
-3, but the brain has no direct access to visual stimuli except that provided by the retina.
-Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
-More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future?
-The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
-
-			@ \rewrite{
-				larger groups of cells carry predictive information for hundreds of milliseconds, }
-
-		\end{ants}
-
-	\section{Relation to empirical findings in neuroscience and studies of consciousness}
-
-		\subsection{Unconscious Processing}
-			\begin{ants}
-				@ According the theory, there are two factor that renders neural processes unconscious.
-
-				@ First, processes are reflexive. This causes non-closured
-
-				@ Second, the abstraction level of the information is below the non-trivial informational closure scale. 
-			\end{ants}
-
-		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
-			\subsubsection{Reflection}
-				\begin{ants}
-					@ Reflexive systems is not informational closured. 
-					@ Base	d on our theory, 
-					@ x -> s -> a
-						@@ the system state is determined by environmental state, then it is not conscious. 
-					@ Therefore, in general, a simple policy network is not conscious. 
-				\end{ants}
-
-			\subsubsection{Blindsight}
-				\begin{ants}
-					@ This also blindsight. 
-					@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
-					@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
-					@ Patient B.F. reactions are stimulus driven. 
-				\end{ants}
-
-			\subsubsection{procedure memory}
-
-			\subsubsection{cerebellum}
-				\begin{ants}
-					@ cerebellum feed-forward connections, maybe just a policy network.\needref{cerebellum} 
-				\end{ants}
-
-		\subsection{Under the level of informational closure}
-			\subsubsection{statistical inference}
-				\begin{ants}
-					@ The computation of Bayesian brain is unconscious.			 
-				\end{ants}
-
-			\subsubsection{subliminal perception}
-				\begin{ants}
-					@ Above chance performance can be performed through non-closure pathway (reflexive behaviours)
-
-					@ Due to coarse-graining, mapping between changes of microstate
-				\end{ants}
-			\subsubsection{Libet Experiments}
-
-		\subsection{Deterministic vs probabilistic}
-			\cite{dehaene2017consciousness}
-			\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}
-
-	\section{About Phenomenology (conscious processing)}
-		\subsection{Perceptual overflow}
-		\subsection{Volition and freewill}
-			\begin{ants}
-				@ Volition is a result of coarse-graining
-
-				@ Lebel's experiment can be well explained by the experiment.
-			\end{ants}
-
-		\subsection{Planning}
-		\subsection{Imagination}
-		\subsection{Dream vs non-dream sleep}
-		\subsection{Binocular rivalry}
-		\subsection{Hallucinations}
-		\subsection{Synaesthesia}
+	\section{Conscious vs unconscious processing}
+		\ideaBox{Now we can combine "Relation to empirical findings in neuroscience and studies of consciousness" and "About Phenomenology (conscious processing)" in to this}
 
 	\section{Comparison with other theories}
+		\ideaBox{Main points should be same/diff, our advantages, and predictions}
 
@@
 
-	\section{Theory predictions (Counter-intuitive prediction)}
-
-		\subsection{informational closure}
-			\begin{ants}
-				@ We predict that through coarse-graining, conscious agents create 
-			\end{ants}
-
-		\subsection{Prediction on split-brain (vs IIT)}
-			* IIT suggests that cutting, two subparts may both still have MIP, therefore, have two conscious mind.
-
-			* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.
-
 	\section{Future works}
@@
 
+	\section*{=== backup ===}	
+	\section*{Biological evidence of informational closure in neural system}
+		\begin{ants}		
+			% ============================================================================ %
+			%                             sederberg2018learning                            %
+			% ============================================================================ %
+
+			@ So far, not so much research on non-trivial informational closure in biological neural systems.
+
+			@ However, \rewording{XXX}
+
+			% Internal self-predictive mechanism	
+			@ Recent biological evidence suggests that low-level neurons encodes predictive information about external  and
+
+			@ \toWrite{
+				need to say this is exactly the non-trivial informational closure, and refer to equation XXX}
+
+			@ \cite{sederberg2018learning}
+			@ \rewrite{
+				in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
+
+			@ \rewrite{
+				We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
+
+			@ \rewrite{
+				We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
+
+			@ \rewrite{
+				Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
+This suggests that bottom-up prediction may play an important role in sensory processing}
+
+			@ \rewrite{
+				Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
+
+			@ \rewrite{
+				Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
+
+			@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
+
+			@ \rewrite{
+				The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
+
+			@ \cite{Palmer2015}
+			@ \rewrite{
+				Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
+
+			@ \rewrite{
+				It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
+3, but the brain has no direct access to visual stimuli except that provided by the retina.
+Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
+More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future?
+The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
+
+			@ \rewrite{
+				larger groups of cells carry predictive information for hundreds of milliseconds, }
+
+		\end{ants}
+
+	\section*{Relation to empirical findings in neuroscience and studies of consciousness}
+
+		\subsection{Unconscious Processing}
+		\begin{ants}
+			@ According the theory, there are two factor that renders neural processes unconscious.
+
+			@ First, processes are reflexive. This causes non-closured
+
+			@ Second, the abstraction level of the information is below the non-trivial informational closure scale. 
+		\end{ants}
+
+		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
+		\subsubsection{Reflection}
+		\begin{ants}
+			@ Reflexive systems is not informational closured. 
+			@ Base	d on our theory, 
+			@ x -> s -> a
+			@@ the system state is determined by environmental state, then it is not conscious. 
+			@ Therefore, in general, a simple policy network is not conscious. 
+		\end{ants}
+
+		\subsubsection{Blindsight}
+		\begin{ants}
+			@ This also blindsight. 
+			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
+			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
+			@ Patient B.F. reactions are stimulus driven. 
+		\end{ants}
+
+		\subsubsection{procedure memory}
+
+		\subsubsection{cerebellum}
+		\begin{ants}
+			@ cerebellum feed-forward connections, maybe just a policy network.\needref{cerebellum} 
+		\end{ants}
+
+		\subsection{Under the level of informational closure}
+		\subsubsection{statistical inference}
+		\begin{ants}
+			@ The computation of Bayesian brain is unconscious.			 
+		\end{ants}
+
+		\subsubsection{subliminal perception}
+		\begin{ants}
+			@ Above chance performance can be performed through non-closure pathway (reflexive behaviours)
+
+			@ Due to coarse-graining, mapping between changes of microstate
+		\end{ants}
+		\subsubsection{Libet Experiments}
+
+		\subsection{Deterministic vs probabilistic}
+		\cite{dehaene2017consciousness}
+		\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}
+
+	\section*{About Phenomenology (conscious processing)}
+\subsection{Perceptual overflow}
+\subsection{Volition and freewill}
+\begin{ants}
+	@ Volition is a result of coarse-graining
+
+	@ Lebel's experiment can be well explained by the experiment.
+\end{ants}
+
+\subsection{Planning}
+\subsection{Imagination}
+\subsection{Dream vs non-dream sleep}
+\subsection{Binocular rivalry}
+\subsection{Hallucinations}
+\subsection{Synaesthesia}
+
+	\section*{Theory predictions (Counter-intuitive prediction)}
+
+\subsection{informational closure}
+\begin{ants}
+	@ We predict that through coarse-graining, conscious agents create 
+\end{ants}
+
+\subsection{Prediction on split-brain (vs IIT)}
+* IIT suggests that cutting, two subparts may both still have MIP, therefore, have two conscious mind.
+
+* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.
+
 \end{document}

### 2018-07-26 Paper_neural_coarse_graining_of_consciousness.tex
ATOM try

@@
 \newacro{ncg}{neural coarse-graining}
+
+% The name of our theory
+\newcommand{\tnamefull}{[TheoryNameFull]}
+\newcommand{\tname}{[TheoryNameShort]}
+\newacro{\tname}{\tnamefull}
 
@@
 
-				@ ====================================
-
 				% @ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour.
@@
 			%% scale
+				@ ============ About scale ===========
 
@@
 
-				@ ====================================
-
 			%% our argument
-				@ In this article, we propose that consciousness \highlightAndComment[YellowGreen]{correlates}{Is this proper?} information processing at a certain coarse-grained level where the neural system creates a high degree of non-trivial informational closure.
-We further predict that \textit{levels} of consciousness are determined by the levels of informational closure and \textit{contents} of consciousness are determined by the concurrent states of the informational closure \citep{laureys2005neural, overgaard2010neural}.\todo{There must be a better way to reword this part}
+				@ =========== our argument ===========
+
+				@ In this article, we propose new theory of consciousness, called \ac{\tname}, which states that consciousness \highlightAndComment[YellowGreen]{correlates}{Is this proper?} information processing at a certain coarse-grained level where the neural system creates a high degree of non-trivial informational closure (NTIC).
+We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
 
 			%% About this paper
-				@ In the following sections, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
-
-				@ We argue that through coarse-graining the human neural system can achieves non-trivial informational closure at a specific coarse-grained level.
-
-				@ We then propose that the state of the informational closure correlates the state of consciousness for both levels and contents which can be explained and computationally quantified and predicted in this theory.
-
-				@ We discuss how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness.
-
-				@ We finally provide predictions and testable approaches for this theory.
+				@ ========= About this paper =========
+
+				@ Since this theory rests on two core concepts: non-trivial informational closure and neural coarse-graining, in the following sections, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
+
+				@ We next argue that through coarse-graining the human neural system can achieves non-trivial informational closure at a specific coarse-grained level.
+
+				@ We then propose that the state of the informational closure correlates the state of consciousness for both levels and contents which can be explained and computationally quantified and predicted by this theory.
+
+				@ We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness.
+
+				@ Finally, we provide predictions and testable approaches for this theory.
 
@@
 
-%		==================================================
-%		\begin{ants}
-%			
-%			@ consciousness is information
-%			
-%			@ conscious contents
-%				@@ \toWrite{lower level}
-%				@@ Information processing of individual neurons are noisy.
-%				@@ We don't have conscious content changes when individual neurons fire action potentials. 				
-%				@@ Don't even mention ion channel dynamic. 
-%				
-%				
-%				@@ \toWrite{Higher-level dynamic}
-%
-%				
-%				
-%				
-%				
-%			
-%			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic. 
-%			
-%			
-%			@ \toWrite{Human tendency for active prediction }
-%				@@ \cite{Stahl2015} \rewrite{
-%					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore?
+		%% backup point
+		\begin{comment}			
+			@ consciousness is information
+
+			@ conscious contents
+				@@ \toWrite{lower level}
+				@@ Information processing of individual neurons are noisy.
+				@@ We don't have conscious content changes when individual neurons fire action potentials. 				
+				@@ Don't even mention ion channel dynamic.
+
+				@@ \toWrite{Higher-level dynamic}
+
+			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.
+
+			@ \toWrite{Human tendency for active prediction }
+				@@ \cite{Stahl2015} \rewrite{
+					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore?
 We found that 11-month-old infants (N = 110) used violations of prior expectations as special opportunities for learning.
@@
 Thus, early in life, expectancy violations offer a wedge into the problem of what to learn.}
-%			
-%			@ Intuitive physics \needref{Intuitive physics}
-%			
-%			@ However, sensory signal are always noisy. 			
-%			
-%			
-%			@ We propose that consciousness is not related to particular neural architectures or location of the neural system.
-%			
-%
-%		\end{ants}
+
+			@ Intuitive physics \needref{Intuitive physics}
+
+			@ However, sensory signal are always noisy.
+
+			@ We propose that consciousness is not related to particular neural architectures or location of the neural system.			
+		\end{comment}
 
 	\section{Non-trivial informational closure\martin{todo}}
+		\ideaBox{Not easy. Should we go for NTIC without describe an intuition about consciousness? Or we should start from intuition? Or explain the intuition in Chapter 4?}
 
@@
 			\begin{ants}
+				@ In systems theory the concept of closure \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}
+
+				@ The notion of non-trivial informational closure (NTIC) is proposed by \cite{BERTSCHINGER.2006}.
+
+				@ The concept of closure is closely related to system identification in systems theory. One can define a system from its environment by computing the closureness of the system.
+
+				a prominent role in systems theory where it is used to identify or define the system in distinction from its environment
+
+				@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.
+
+				@ ============================================================================
+
 				@ \rewrite{
@@
 
-			\noindent However, achieving information closure (minimising $J_t$) could be trivial, which means the environment and the system are entirely independent of each other.
+		% trivial
+			\noindent 
+			Achieving information closure (minimising $J_t$) could be trivial, which means the environment and the system are entirely independent of each other.
 				\begin{equation}
@@
 
-			\noindent In the non-trivial case, the system trying to encode environmental dynamic can also achieve informational closure. This means
+		% non-trivial
+			\noindent 
+			However, informational closure can be achieved non-trivially.
+In the non-trivial case, the system trying to encode information about the environmental dynamics can also be informational closured.
+This means
 				\begin{equation}
-				I(Y_{t+1};E_{t})\neq0, 
+				I(Y_{t+1};E_{t}) > 0
 				\end{equation}
 
-			\noindent And, non-trivial informational closure can be defined as 		
+			\noindent
+			This also implies
+				\begin{equation}
+					I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}) > 0
+				\end{equation}
+
+			\noindent Therefore, non-trivial informational closure can be defined as 		
 				\begin{equation}
@@
 
-			\noindent Therefore, Maximising NTIC is equivalent to
-				\begin{equation}
+			\noindent And, Maximising NTIC is equivalent to
+				\begin{equation}\label{eq:nticObjective}
 				\begin{aligned}
@@
 
-		\subsection{Trivial case}
-			\begin{ants}
-				@ However, informational closure could be trivial.
-
-				@ Information closure could be trivial.
-That is, when a system is fully independent from the environment, no information can flow into the system from the environment and also leak to the environment from the system.
-Equa.
-xxxx shows the mathematical description of trivial informational closure.
-When mutual information between the environment and system future state close to 0, and the system transition is independent from the environment, the system can reach informational closure.
-However, such systems do not have any functional meaning and evolutional advantages.
-
-				@ \rewrite{
-					A system that is independent from its environment trivially achieves informational closure.}  \cite{BERTSCHINGER.2006}
-					\begin{equation}
-						\left.\begin{array}
-						{l}{MI(S_{n+1};E_{n})=0}\\
-						{MI(S_{n+1};S_{n})-MI(S_{n+1};S_{n}|E_{n})=0}
-						\end{array}\right.
-					\end{equation}
-			\end{ants}
-
-		\subsection{Non-trivial informational closure}
-			\begin{ants}
-
-				@ \citep{BERTSCHINGER.2006}
-				@ \citep{guttenberg2016neural}
-
-				@ \rewrite{The “informational closure” becomes non-trivial if the state contains information about the environment, i.e. $MI(S_{n+1};E_{n})\neq0$}
-
-				@ We can define non-trivial informational closure (NTIC)
-
-				@ Definition:\callforhelp{Which def is better? }
-
-					@@
-					\begin{equation}
-					N T I C = H ( Y _ { t + 1} ) - H ( Y _ { t + 1} | Y _ { t } )
-					\end{equation}
-					\citep{guttenberg2016neural}
-
-					@@
-					\begin{equation}
-					\left.\begin{array}{l}{ N T I C  : = M I ( S _ { n + 1} ; E _ { n } ,\dots ,E _ { n - m } ) - M I ( S _ { n + 1} ; E _ { n } ,\dots ,E _ { n - m } | S _ { n } ) }\\{  = M I ( S _ { n + 1} ; E _ { n } ,\dots ,E _ { n - m } ) - M I ( S _ { n + 1} ; E _ { n } | S _ { n } ) }\end{array} \right.
-					\end{equation}
-					\cite{BERTSCHINGER.2006}
-
-				@ \rewrite{Modeling: The system reaches synchronization and internalizes the correlations observed in the environment by building up own structures.}
-
-			\end{ants}
-
-		\subsection{Achieve non-trivial informational closure}
-			\begin{ants}
-
+			\toWrite{need to elaborate this part more}
+			When a system achieve NTIC, the system internalizes and synchronises the dynamics of the environment, which also means modelling the environment.
+Having high degrees of NTIC entails predictive power about the environment.
+This gives biological agents a great functional meaning and an evolutional reason reason to achieve NTIC in their information processing systems.
+Practically, \cite{guttenberg2016neural} proposed that NTIC can be achieved by maximising the predictive power about the environment and the self-predictive information of the system concurrently .
+\callforhelp{Do we need to say we also maximise entropy of latent layers?
+}
+
+		\subsection{Biological evidence of informational closure in the neural system}
+			\begin{figure}[H]
+				\includegraphicsTodo[width=\textwidth]{WritingMaterials/Palmer2015.png} 
+				\caption{Figure adapted from \cite{sederberg2018learning}}
+				\label{fig:sederberg2018learning}	
+			\end{figure}
+
+			\begin{ants}
+				@ So far, not much studies directly examine NTIC in biological systems.
+
+				@ Some very recent studies have showed relevant properties.\todo{Perhaps we should put a picture about this study here.}
+
+				@ By examining salamander retina, \cite{Palmer2015, sederberg2018learning} found that neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states on two different classes of stimuli.
+
+				@ This property matches Eq. (\ref{eq:nticObjective})
+
+				@ Therefore, self-predictive information of the neural populations can guides  prediction about external stimuli without reference to stimulus parameters explicitly.
+
+				@ efficient readouts of one type of information were likely to be efficient readouts of the other.
+The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli.
+
+				@ \rewrite{ Internal predictability reflects the timescale of correlation in the stimulus }
+
+				@ The two studies provides a empirical evidence that NTIC may serve as an objective in the neural system. 
+			\end{ants}
+
+			\begin{writingMaterials}
+				@ ===
+
+				@ \rewrite{
+					Internal information reflects the spatial and temporal correlations in the stimulus.}
+
+				@ \rewrite{predictive information is encoded synergistically.}
+
+				@ \rewrite{
+					in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
+
+				@ \rewrite{
+					We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
+
+				@ \rewrite{
+					We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
+
+				@ \rewrite{
+					Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
+This suggests that bottom-up prediction may play an important role in sensory processing}
+
+				@ \rewrite{
+					Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
+
+				@ \rewrite{
+					Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
+
+				@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
+
+				@ \rewrite{
+					The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
+
+				@ \cite{Palmer2015}
+				@ \rewrite{
+					Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
+
+				@ \rewrite{
+					It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
+3, but the brain has no direct access to visual stimuli except that provided by the retina.
+Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
+More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future?
+The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
+
+				@ \rewrite{
+					larger groups of cells carry predictive information for hundreds of milliseconds, }
+
+			\end{writingMaterials}
+
+			%% backup
+			\begin{comment}
 				@ Accurately model deterministic environment 
@@
 				@ In the next section, we claim that the neural system achieve NTIC through coarse-graining.				
-
-			\end{ants}
+			\end{comment}
 
@@
 	\section{Neural coarse-graining}
-
-		\begin{ants}
+		\subsection{intro}
+			\begin{ants}
+				@ As we mentioned above, to construct the NTIC process can bring agents great survival advantage.
+
+				@ However, to achieve NTIC (or even IC) is challenging for highly stochastic systems. Due to the stochasticity, the current states of the system have low predictability of its future states.
+
+				@ Previous research has been showing that the neural system are suffered from multiple noise sources  during information processing, including sensory, cellular, electrical, synaptic noises and have large trial-to-trial variability at the cellular level.
+\citep{faisal2008noise}.
+neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.
+
+				@ These noises sabotaged the predictability of future states and prevent the neural system from creating NTIC processes at the cellular level.
+
+				@ And every individual sensor only receives a little amount of information about the environment.
+
+				@ We argues that the human neural system to achieve NTIC through coarse-graining. 
+			\end{ants}
+
+		\begin{writingMaterials}
 
 			%% About coarse-graining			
-%			@ \rewrite{
-%				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
-%			
-%			
-%			@ \rewrite{
-%				a number of different microstates,First, typically a number of different microstates, will realize the same value of the macro-variables of upper level causal theories.}
-%			
-%			
-%			@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
+			@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
 
@@
 
-		\end{ants}
+		\end{writingMaterials}
 
@@
 			\begin{ants}
+				@
+
+				@ \rewrite{Neurons are subject to thermal fluctuations and other physical noise (Faisal et al., 2008).} \cite{faisal2008noise}
 
 				@ We have known that the neural system uses various coding strategies to encode information at coarse-grained levels.
+
+				@ \rewrite{Because the sequence of action potentials generated by a given stimulus varies from trial to trial, neuronal responses are typically treated statistically or probabilistically}
 
@@
 
-					@@ firing rate coding
+					@@ Rate coding
+						\cite{stein2005neuronal}
 
@@
 						@@@ \cite{QuianQuiroga2009}
+
+					@@ \rewrite{
+						Averaging is used in many neural systems in which information is encoded as patterns of activity across a population of neurons that all subserve a similar function (for example, see REFs 140,141 )}
+										140.
+Georgopoulos, A., Schwartz, A.
+\& Kettner, R.
+Neuronal population coding of movement direction.
+Science 233, 1416–1419 (1986).
+141.
+Lee, C., Rohrer, W.
+H.
+\& Sparks, D.
+L.
+Population coding of saccadic eye movements by neurons in the superior colliculus.
+Nature 332, 357–360 (1988).
+
+					@@ \rewrite{
+						Electrophysiological studies in the monkey have shown that behaviourally relevant signals are averaged not only across neuronal populations but also over time in the formation of a behavioural decision 156 .} 156.
+Gold, J.
+I.
+\& Shadlen, M.
+N.
+Representation of a perceptual decision in developing oculomotor commands.
+Nature 404, 390–394 (2000).
+
+					@@ \rewrite{A distributed representation of information of this type is more robust to the effects of noise.}
 
@@
 
+		\subsection{NTIC at specific levels of neural coarse-graining\callforhelp{any reference?}}
+			\ideaBox{Do we need to discuss Hoel's theory here?}
+			\begin{ants}
+				@ The relation between the degrees of NTIC and coarse-graining is not monotonic.
+
+				@ Overly coarse-graining a system can lead to low degrees of NTIC.
+
+				@ Imagining an extreme scenario that all microscopic states are mapped to a macroscopic state, the macroscopic process losses all the information can be used to make self-prediction.
+
+				@ \cite{sederberg2018learning} showed similar results in salamander retina neural populations.
+
+				@ They found that
+
+				@ \rewrite{
+					We found that while the efficiency of the learned readouts relative to optimal single-bit readouts remained high the efficiency relative to the full input group decreased, such that readouts of groups of 10 cells typically preserved 30\% of the total predictive information}
+
+				@ \rewrite{
+					In other words, reading out from groups of four cells can be accomplished with high absolute efficiency.
+Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}
+			\end{ants}
+
+	% ============================================================================ %
+	%                                  Out theory                                  %
+	% ============================================================================ %
 	\section{A neural coarse graining theory of consciousness}
@@
 
-			@
+			@ Therefore, to understand this system, you don't need more information from external environment.
+
+			@ It also means everything in this system is self-defined.
 
@@
 			%% reasoning
+
+				@ ============= reasoning ============
+
 				@ Information processing in the neural system exists at different level of abstraction.
@@
 			%% our claim 
+				@ ============ our claim  ============
 
@@
 			\end{ants}
+
+		\subparagraph{more information theory and philosophy relevance}
+			\begin{writingMaterials}
+				@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
+
+				@ This means the fine-grain variable does not exist at the coarse-grained causal chain. 
+			\end{writingMaterials}
 

### 2018-10-25 Paper_neural_coarse_graining_of_consciousness.tex
Chapter_2_clean

@@
 \usepackage{tikz}
+\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}
 
@@
 % The name of our theory
-\newcommand{\tnamefull}{[TheoryNameFull]}
-\newcommand{\tname}{[TheoryNameShort]}
+% ----------------------------------------------------------------------------
+\newcommand{\tnamefull}{The Neural Coarse-graining Theory of Consciousness} 
+\newcommand{\tname}{NCGT} 	% TheoryNameShort
 \newacro{\tname}{\tnamefull}
+%\newacro{NCGT}{the neural coarse-graining theory of consciousness}
 
@@
 
-		\begin{ants}
-
 		%% Story about a cell
-				@ Imagining you are a neuron in Bill's brain.
-Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials.
-
-				@ You have no idea that you are one of neurons in Bill's supplementary motor area and is now involved in motor control processing while Bill is reaching his hand to grab a cup.
-
-				@ You are totally ignorant of the intension, the goal, and the motor plan that Bill is having now even thought you are part of the physiological substrate responsible for this action.
-
-				@ The same story also happens to Bill's conscious mind. In his conscious experience, he is unaware of everything you do and even not able to know your existence if Bill never studies neuroscience.
-
-				@ It seems that information you are processing and information shows in Bill's conscious percept are divorced from each other.
-
-				@ \idea{Need a ending sentence here}
-
-				% @ Strikingly, not only you are ignorance of Bill's intention but also Bill has no conscious awareness of your behaviour.
-If your work contributes some part of Bill's conscious perception or intention to act.
+		Imagine you are a neuron in Alice's brain.
+Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons.
+However, you have no idea that you are one of neurons in Bill's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup.
+You are totally ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
+
+		A similar story also happens to Alice's conscious mind.
+To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action.
+However, her conscious experience does not show the dynamic of your membrane potential and about action potentials you send to other neurons every second.
+That is, information in Alice's conscious experience does not contain information involved in your information processing.
+
+		\toWrite{maybe need a transition sentence here}
 
 		%% scale
-				@ ============ About scale ===========
-
-				@ It seems to be true that we are unable to consciously access information processed at every scale in the neural system.
-Only information at certain levels of coarse-graining is able to be parts of conscious contents.
-
-				@ When we focus on microscopic level of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are highly stochastic \citep{Goldwyn2011, White2000}.
+		It seems to be true that we are unable to consciously access information processed at every scale in the neural system.
+Only information at certain levels of coarse-graining can become conscious contents.
+At microscopic levels of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are extremely stochastic \citep{Goldwyn2011, White2000}.
 However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious contents shows astonishing stability and high robustness against to ubiquitous noise in the neural system \citep{mathis1995computational}.
-
-				% Neurons fires all the time. However, those massive action potentials do not appear in our  conscious contents.
-
-				@ Likewise, at the macroscopic level, conscious experience does not associate with joint states of the full neural system because we have known that some parts of the neural system process information unconsciously (cerebellum for example \citep{lemon2010life}).
-
-				@ Meanwhile, we don't experience "super-consciousness" when we have massive inter-individual interactions with other human-beings.
-Even though evidence has shown several types of collective information processing at human social groups levels \needref{collective intelligent in human, collective memory, collective behavioural, etc.}, those processes seem to depart from our individual conscious contents.
-
-				@ \idea{Need a ending sentence here}
+Likewise, conscious experience does not associate with states of the whole brain level because we have known that some parts of the neural system may contributes conscious experience very little (cerebellum for example \citep{lemon2010life}).
+Additionally, we don't experience "super-consciousness" when we have massive inter-individual interactions with other human-beings.
+Even though evidence has shown several types of collective information processing at human social groups levels \citep{malone2015handbook}.
+information processed at this level seems to depart from our individual conscious contents.
 
 		%% our argument			
-				@ =========== our argument ===========
-
-				@ In this article, we propose new theory of consciousness, called \ac{\tname}, which states that consciousness \highlightAndComment[YellowGreen]{correlates}{Is this proper?} information processing at a certain coarse-grained level where the neural system creates a high degree of non-trivial informational closure (NTIC).
+		In this article, we propose a new theory of consciousness, called \ac{\tname}.
+This proposal states that consciousness does not rest to particular neural architectures or location of the neural system.
+Instead, we argue that consciousness correlates information processing at a certain coarse-grained level where the neural system creates a high degree of non-trivial informational closure (NTIC).
 We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
@@
 		%% About this paper			
-				@ ========= About this paper =========
-
-				@ Since this theory rests on two core concepts: non-trivial informational closure and neural coarse-graining, in the following sections, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
-
-				@ We next argue that through coarse-graining the human neural system can achieves non-trivial informational closure at a specific coarse-grained level.
-
-				@ We then propose that the state of the informational closure correlates the state of consciousness for both levels and contents which can be explained and computationally quantified and predicted by this theory.
-
-				@ We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness.
-
-				@ Finally, we provide predictions and testable approaches for this theory.
-
-				@ \todo{Do I need a figure?}
-					\begin{figure}
-						\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
-						\cite{pennartz2017consciousness}
-						\caption{xxxx}
-	   			   	\end{figure}
-
-		\end{ants}
+		Our theory rests on two core concepts: non-trivial informational closure and neural coarse-graining.
+In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
+We next argue that through coarse-graining the human neural system can achieves non-trivial informational closure at a specific coarse-grained level.
+We then propose that the state of the informational closure correlates the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by this theory.
+We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness.
+Finally, we provide predictions and testable approaches for this theory.
+
+%				@ \todo{Do I need a figure?}
+%					\begin{figure}
+%						\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
+%						\cite{pennartz2017consciousness}
+%						\caption{xxxx}
+%	   			   	\end{figure}
 
@@
 
-			@ However, sensory signal are always noisy.
-
-			@ We propose that consciousness is not related to particular neural architectures or location of the neural system.			
 		\end{comment}
@@
 	\section{Non-trivial informational closure\martin{todo}}
-		\ideaBox{Not easy. Should we go for NTIC without describe an intuition about consciousness? Or we should start from intuition? Or explain the intuition in Chapter 4?}
-
-		\subsection{Meaning of informational closure}
-			\begin{ants}
-				@ In systems theory the concept of closure \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}
-
-				@ The notion of non-trivial informational closure (NTIC) is proposed by \cite{BERTSCHINGER.2006}.
-
-				@ The concept of closure is closely related to system identification in systems theory. One can define a system from its environment by computing the closureness of the system.
-
-				a prominent role in systems theory where it is used to identify or define the system in distinction from its environment
-
+		\ideaBox{I am still not sure we should go for NTIC without describe my intuition about consciousness and closure?
+Or we should start with my intuition.
+Or we should postpone to explain the intuition in Chapter 4?}
+
+		The notion of non-trivial informational closure (NTIC) is introduced by \cite{BERTSCHINGER.2006}.
+The concept of closure is closely related to system identification in systems theory.
+One can define a system from its environment by computing the closureness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
+The closureness can be further quantified by information theory.
+
+		\begin{writingMaterials}			
 			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.
+
+			@ \idea{should we describe the intuition of boundary problem here?}
 
@@
 
-			\end{ants}
-
-		\subsection{Definition of informational closure}
-
-			\noindent Information flow $J_{t}$ from environment $E$ to a system $Y$ at time $t$ can be defined as			
+		\end{writingMaterials}
+
+		% Definition of informational closure				
+			\noindent
+			Information flow $J_{t}$ from the environment $E$ to a system $Y$ at time $t$ can be defined as the conditional mutual information $I$ between the system future state $Y_{t+1}$ and the current environment current state $E_{t}$ given the current system state $Y_{t}$
+
 				\begin{equation}\label{eq:InformationFlow}
@@
 			\noindent
-			Based on the definition from \cite{BERTSCHINGER.2006}, a system is informational closured when information flow between the environment and the system is close to zero.
-
-		% trivial
+			\cite{BERTSCHINGER.2006} defines that a system is informational closured when information flow from the environment to the system is close to zero.
+
+				\begin{equation}
+				J_{t}(E \rightarrow Y )=0
+				\end{equation}
+
+			% ------------------------------- trivial case ------------------------------- %
 			\noindent 
 			Achieving information closure (minimising $J_t$) could be trivial, which means the environment and the system are entirely independent of each other.
+
 				\begin{equation}
@@
 
-		% non-trivial
+			% -------------------------------- non-trivial ------------------------------- %
 			\noindent 
@@
 This means
+
 				\begin{equation}
@@
 
-			\noindent Therefore, non-trivial informational closure can be defined as 		
+			\noindent 
+			And, non-trivial informational closure can be defined as 		
 				\begin{equation}
@@
 
-			\noindent And, Maximising NTIC is equivalent to
+			\noindent 
+			And, Maximising NTIC is equivalent to
 				\begin{equation}\label{eq:nticObjective}
@@
 
-			\toWrite{need to elaborate this part more}
-			When a system achieve NTIC, the system internalizes and synchronises the dynamics of the environment, which also means modelling the environment.
-Having high degrees of NTIC entails predictive power about the environment.
-This gives biological agents a great functional meaning and an evolutional reason reason to achieve NTIC in their information processing systems.
-Practically, \cite{guttenberg2016neural} proposed that NTIC can be achieved by maximising the predictive power about the environment and the self-predictive information of the system concurrently .
-\callforhelp{Do we need to say we also maximise entropy of latent layers?
-}
-
-		\subsection{Biological evidence of informational closure in the neural system}
+			\noindent
+			This implies the system contains in itself the information of its own future and the self-predictive information is gained from the information about the environment.
+Therefore, to achieve NTIC, the system can internalizes and synchronises the dynamics of the environment, i.e.
+modelling the environment.
+Furthermore, having high degrees of NTIC entails having high predictive power about the environment.
+This gives biological agents a great functional and evolutional advantage to achieve NTIC in their information processing systems.
+Practically, \cite{guttenberg2016neural} proposed that NTIC can be achieved by maximising the predictive power about the environment and the self-predictive information of the system concurrently.
+
+			% Biological evidence of informational closure in the neural system
+			Though the significant advantage for biological systems to achieve NTIC, to our knowledge, studies directly examining NTIC in biological systems are limited.
+However,  recent studies have showed relevant properties in the visual system of salamanders.
+By examining the salamander retina, in two studies \citep{Palmer2015, sederberg2018learning} the authors found that the a large groups of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Figure~\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC.
+Therefore, the self-predictive information of the neural populations can guides prediction about external stimuli without reference to stimulus parameters explicitly.
+Moreover, the internal predictability can be generalised to different stimulus classes suggesting the tendency to internalise the information of environmental dynamics in the neural populations.
+\toWrite{Add Some ending sentences}
+
 			\begin{figure}[H]
@@
 
-			\begin{ants}
-				@ So far, not much studies directly examine NTIC in biological systems.
-
-				@ Some very recent studies have showed relevant properties.\todo{Perhaps we should put a picture about this study here.}
-
-				@ By examining salamander retina, \cite{Palmer2015, sederberg2018learning} found that neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states on two different classes of stimuli.
-
-				@ This property matches Eq. (\ref{eq:nticObjective})
-
-				@ Therefore, self-predictive information of the neural populations can guides  prediction about external stimuli without reference to stimulus parameters explicitly.
-
-				@ efficient readouts of one type of information were likely to be efficient readouts of the other.
-The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli.
-
-				@ \rewrite{ Internal predictability reflects the timescale of correlation in the stimulus }
-
-				@ The two studies provides a empirical evidence that NTIC may serve as an objective in the neural system. 
-			\end{ants}
-
-			\begin{writingMaterials}
+			\begin{comment}
 				@ ===
@@
 
-			\end{writingMaterials}
+			\end{comment}
 
@@
 
+				@ \rewrite{Neurons are subject to thermal fluctuations and other physical noise (Faisal et al., 2008).} \cite{faisal2008noise}
+
 				@ These noises sabotaged the predictability of future states and prevent the neural system from creating NTIC processes at the cellular level.
@@
 
-			%% About coarse-graining			
-			@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
+			@ One way to encode a stable information in neural system is to encode the information in the coarse-grained variables.
+
+			@ \rewrite{
+				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
+
+			@ \rewrite{
+				a number of different microstates,First, typically a number of different microstates, will realize the same value of the macro-variables of upper level causal theories.}
+
+			@ This is a common strategy that we can see in large number of previous physiological studies.
+
+			@ neural system use population coding and temporal coding to fight against noise.
+
+			@ Therefore, even though the low level information processing is noisy, it is possible that the neural system achieve NTIC at a coarse-grained level.
+
+			@ This implies that the information about the environmental dynamic should be represented at a certain coarse-grained level rather then other levels.
+
+			@ It is important to note that NTIC should not be a monotonic function of scale of coarse-graining. For the extreme case xxxxx
 
@@
 			\begin{ants}
-				@
-
-				@ \rewrite{Neurons are subject to thermal fluctuations and other physical noise (Faisal et al., 2008).} \cite{faisal2008noise}
+
+				@ Coarse-graining can be defined as a function that maps multiple microscopic states to a macroscopic states.
+
+				@ One way to encode a stable information in neural system is to encode the information in the coarse-grained variables.
+
+				@ Studies have shown that coarse-graining is a common way that the neural system cope with inevitable noise at microscopic levels.
 
@@
 
-				@ \toWrite{For examples}
-
-				%% temporal 
-				@ temporal coarse-graining
-
-					@@ Rate coding
-						\cite{stein2005neuronal}
-
+				@ In the temporal domain, rate coding can be seem as coarse-graining on temporal events at the neuronal level \cite{stein2005neuronal}.
+
+				@ contained in the firing rate of the neuron
+
+				@ Firing rate of sensory neurons correlate stimulus intensities.  \citep{kandel2000principles}
+
+				@ This coding strategy is highly robust against noise causing variation of interspike intervals.
+
+				@ Another example is population coding.
+
+				@ Population coding is
+
+				the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
+
+				@ \rewrite{
+						Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
+					} \cite{binder2009encyclopedia}
+
+				@ In such case, single neurons are not informative. Instead, coarse-grained variables such as population averaging encode the information.
+
+				@ Encoding information at coarse-grained levels allow the neural system ignores certain causal interactions relevant to fine-grained level of description. \cite{price2007causation}
+
+				@ Note that, information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
+
+			\end{ants}
+
+			\begin{writingMaterials}
 				@ Population coding
@@
 
-					@@ Population coding is the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
-
-					@@ \rewrite{
-						As single neurons are not very informative, to obtain accurate information about sensory or motor variables some sort of population averaging must be performed.}
-
 					@@ \rewrite{
@@
 
-					@@ \rewrite{
-						Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
-					} \cite{binder2009encyclopedia}
-
 				@ sensory hierarchy		
@@
 
-			\end{ants}
+			\end{writingMaterials}
 
@@
 			\begin{ants}
+				@ NTIC can be more easily achieved by coarse-graining.
+
 				@ \citep{guttenberg2016neural} proposed an architecture, called neural coarse-graining (NCG), which aims to captures the emergent large-scale dynamics in the environment.
@@
 
-				@ During training, the objective of the architecture is to XXXXX\martin{todo}
-
-				@ \rewrite{
-					The transform can learn to discard uninformative and unpredictable components of the signal in favor of the features which are both highly predictive and highly predictable.}\citep{guttenberg2016neural}
-
-				@ \rewrite{
-					The result is a semi-supervised algorithm which is capable of extracting latent parameters, segmenting sections of time-series with diﬀering statistics, and building a higher-level representation of the underlying dynamics from unlabeled data}\citep{guttenberg2016neural}
-
+				@ Through two objectives during training, the model can achieve NTIC. \martin{todo}
+
+				@ this can be achieved by maximising the self-predictive power of deep layers and its entropy through all training data.
+
+				@ With the objectives, NCG network learns to coarse-grain input signals and  extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.
+
+				@ Agents can process information and act at abstract levels		
 			\end{ants}
@@
 		\subsection{The advantage of NCG}
-			\begin{comment}
-				@ Resistant to noise
-				@ Predictive power
-				@ Agents can process information and act at abstract levels
-			\end{comment}
+			\begin{ants}
+				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics.
+This means that it is possible for agents living at this physical scale to build NTIC process internally.
+
+				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC. 							
+			\end{ants}
 
 		\subsection{NTIC at specific levels of neural coarse-graining\callforhelp{any reference?}}
-			\ideaBox{Do we need to discuss Hoel's theory here?}
-			\begin{ants}
-				@ The relation between the degrees of NTIC and coarse-graining is not monotonic.
+			\begin{ants}
+				@ It is important to note that the relationship between degrees of NTIC and coarse-graining is not monotonic.
 
@@
 
-				@ Imagining an extreme scenario that all microscopic states are mapped to a macroscopic state, the macroscopic process losses all the information can be used to make self-prediction.
-
-				@ \cite{sederberg2018learning} showed similar results in salamander retina neural populations.
-
-				@ They found that
-
-				@ \rewrite{
-					We found that while the efficiency of the learned readouts relative to optimal single-bit readouts remained high the efficiency relative to the full input group decreased, such that readouts of groups of 10 cells typically preserved 30\% of the total predictive information}
-
-				@ \rewrite{
-					In other words, reading out from groups of four cells can be accomplished with high absolute efficiency.
+				@ Imagining an extreme scenario that all microscopic states map to a single macroscopic state, the macroscopic process losses all the predictive information about the environment.
+
+				@ This is evidenced by empirical data as well.
+
+				@ Study by \cite{sederberg2018learning} found that self-predictive information of 4-cell sets readout by an optimal perceptron is higher than 7 and 10-cell sets.
+
+				@ The authors indicated that \blockquote[{\citep{sederberg2018learning}}]{reading out from groups of four cells can be accomplished with high absolute efficiency.
 Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}
 			\end{ants}
+
+\blockquote{reading out from groups of four cells can be accomplished with high absolute efficiency.
+Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}
 

### 2018-10-25 Paper_neural_coarse_graining_of_consciousness.tex
Change a lot of macro

@@
 %	Blue: Topic and Guideline
-%	Purple: Murmur, talking to myself
+%	Purple: Murmur
 %	Green: Question, Call for help, Open for opinions and comments
@@
 % Funcitonal content
-	% Quotes
+	% Quotes: green
 		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}
 
-	% todo
-		% figure
+	% todo: orange
+		% text todo
+		\newcommand{\toWrite}[1]{\noindent
+			\textcolor{Orange}{\textbf{[[ #1 ]]}}}
+
+		% figure todo
 		\newcommand{\includegraphicsTodo}[2][]{%
@@
 
-	% Highlight
-		\newcommand{\highlight}[2][Yellow]{\colorbox{#1}{#2}}
-
-		% Highlight and comment
-		\newcommand{\highlightAndComment}[3][Yellow]{\todo[color=#1]{#3}\colorbox{#1}{#2}}
-
 		% rewording
@@
 			\ifthenelse{\equal{#1}{}}{%
-				\todo[color=White, linecolor=BlueViolet]{\textcolor{BlueViolet}{Ref}}}{%
-				\todo[color=White, linecolor=BlueViolet]{\textcolor{BlueViolet}{Ref: #1}}%
+				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref}}}{%
+				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref: #1}}%
 			}%
@@
 
-	% idea
+	% Highlight
+		% Highlight only
+		\newcommand{\highlight}[2][Thistle!50!white]{\colorbox{#1}{#2}}
+
+		% Highlight and comment
+		\newcommand{\highlightAndComment}[3][Thistle!50!white]{\todo[color=#1]{#3}\colorbox{#1}{#2}}
+
+		% Critical point
+		\newcommand{\critical}[1]{%
+			\todo[color=OrangeRed!70!white]{#1}
+		}
+
+	% idea: Purple 
 		% text idea
@@
 			\newcommand{\ideaBox}[1]{
-				\begin{tcolorbox}[hyphenationfix, width=12cm, colback=Thistle!50!white, flush right]
+				\begin{tcolorbox}[%
+					width=12cm,
+					sharp corners=downhill, 
+					hyphenationfix, 
+					arc=8pt,
+					colback=Thistle!50!white, 
+					flush right,
+					halign=flush right,
+					]%
 					#1
@@
 		% callout idea
-			\newcommand{\ideaCallout}[1]{\todo[color=Thistle, size=\small]{#1}}
-
-	% guildline and direction
-		\newcommand{\toWrite}[1]{\noindent
-			\textcolor{Cyan}{\textbf{[[ #1 ]]}}}
-
+			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}
+
+	% communication: green
 		% call for help
-		\newcommand{\callforhelp}[1]{\todo[color=SpringGreen]{#1}}
-		\newcommand{\martin}[1]{\todo[color=SpringGreen]{@Martin:\\#1}}
+			\newcommand{\callforhelp}[1]{\todo[color=SpringGreen]{[Call For Help]: #1}}
+
+		% comment
+			% comment by authers
+			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}
+
+			% usage: 
+			% \addcomment{auther}{comment text} 
+			% or
+			% \addcomment[highlighted text]{auther}{comment text}
+			%
+			% e.g.
+			% It's a \addcomment[beautiful]{Acer}{need a reference} day
 
@@
 
-	\section{Non-trivial informational closure\martin{todo}}
+	\section{Non-trivial informational closure}
 		\ideaBox{I am still not sure we should go for NTIC without describe my intuition about consciousness and closure?
@@
 
-		\subsection{\martin{todo}Neural coarse-graining}
+		\subsection{Neural coarse-graining}
 			\begin{figure}
@@
 
-				@ Through two objectives during training, the model can achieve NTIC. \martin{todo}
+				@ Through two objectives during training, the model can achieve NTIC.
 
@@
 
-				@ \idea[red]{I need to somehow acknowledge \cite{pennartz2017consciousness}}
+				@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
 					@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}
@@
 		\subsection{Sensory hierarchy and neural coarse-graining
-			\todo[color=Red]{This is super important. I need to deal with this very carefully. Need to completely rewording}}\label{sec:SensoryHierarchy}
+			\critical{This is super important. I need to deal with this very carefully. Need to completely rewording}}\label{sec:SensoryHierarchy}
 
@@
 
-				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \todo[color=red]{I NEED A EQUATION!}).
+				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \critical{I NEED A EQUATION!}).
 
@@
 
-					@@ \toWrite{Example from PID controller}
+					@@ \idea{Example from PID controller?}
 
@@
 
-					@ Because the forward model build on the informational closure representation can be seen as part of the closure. \todo[color=red]{IS THIS TRUE? NEED DISCUSSION}
+					@ Because the forward model build on the informational closure representation can be seen as part of the closure. \critical{IS THIS TRUE? NEED DISCUSSION}
 
@@
 			\begin{ants}
-				@ It's not clear what the coarse-graining function is.\todo[color=red]{this should be explained by environmental deterministic}
+				@ It's not clear what the coarse-graining function is.\critical{this should be explained by environmental deterministic}
 

### 2018-10-25 Paper_neural_coarse_graining_of_consciousness.tex
Updates from ShareLaTeX

@@
 
-%% Language and font encodings
+%% Language and font encoding
 \usepackage[english]{babel}
@@
 
-% Funcitonal content
+% Functional content
 	% Quotes: green
@@
 
-		% callout idea
+		% call-out idea
 			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}
@@
 		% comment
-			% comment by authers
+			% comment by authors
 			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}
@@
 Besides, we have no conscious experience from interpersonal activities albeit massive interactions among individuals.
-Instead, neurophysiological evidence has been showing that conscious experience tends to covary with information encoded in coarse-grained neural states such as neural population codes.
+Instead, neurophysiological evidence has been showing that conscious experience tends to co-vary with information encoded in coarse-grained neural states such as neural population codes.
 We argue that the neural states within the scope of the informational closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious.

### 2018-10-26 Paper_neural_coarse_graining_of_consciousness.tex
After PF from Ryota for chapter 1

--- 2018-10-25 Paper_neural_coarse_graining_of_consciousness.tex
@@
 Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons.
-However, you have no idea that you are one of neurons in Bill's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup.
-You are totally ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
-
-		A similar story also happens to Alice's conscious mind.
+However, you have no idea that you are one of neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup.
+You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
+		A similar story also applies to Alice's conscious mind.
 To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action.
@@
 At microscopic levels of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are extremely stochastic \citep{Goldwyn2011, White2000}.
-However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious contents shows astonishing stability and high robustness against to ubiquitous noise in the neural system \citep{mathis1995computational}.
-Likewise, conscious experience does not associate with states of the whole brain level because we have known that some parts of the neural system may contributes conscious experience very little (cerebellum for example \citep{lemon2010life}).
-Additionally, we don't experience "super-consciousness" when we have massive inter-individual interactions with other human-beings.
-Even though evidence has shown several types of collective information processing at human social groups levels \citep{malone2015handbook}.
-information processed at this level seems to depart from our individual conscious contents.
+However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}.
+Likewise, conscious experience does not associate with states of the whole brain level because we have known that some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}).
+Additionally, we do not  experience "super-consciousness" when we have massive inter-individual interactions with other human-beings.
+Even though evidence has shown several types of collective information processing at human social groups levels exist \citep{malone2015handbook}, information processed at this level seems to depart from our individual conscious contents.
 
 		%% our argument		
-		In this article, we propose a new theory of consciousness, called \ac{\tname}.
-This proposal states that consciousness does not rest to particular neural architectures or location of the neural system.
-Instead, we argue that consciousness correlates information processing at a certain coarse-grained level where the neural system creates a high degree of non-trivial informational closure (NTIC).
-We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
+		In this article, we propose a new theory of consciousness, called\ac{\tname}.
+This proposal states that consciousness does not rest on particular neural architectures or locations in the neural systems.
+Instead, we argue that consciousness correlates with information processing at a certain coarse-grained level where the neural systems create a high degree of non-trivial informational closure (NTIC).
+We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
 
 		%% About this paper			
-		Our theory rests on two core concepts: non-trivial informational closure and neural coarse-graining.
+		Our theory rests on two core concepts: non-trivial informational closure and neural coarse- graining.
 In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
-We next argue that through coarse-graining the human neural system can achieves non-trivial informational closure at a specific coarse-grained level.
-We then propose that the state of the informational closure correlates the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by this theory.
+We next argue that through coarse-graining the human neural system can achieve non-trivial informational closure at a specific coarse-grained level.
+We then propose that the state of the informational closure correlates with the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by this theory.
 We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness.
@@
 
-%				@ \todo{Do I need a figure?}
-%					\begin{figure}
-%						\includegraphicsTodo[width=\textwidth]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
-%						\cite{pennartz2017consciousness}
-%						\caption{xxxx}
-%	   			   	\end{figure}
+		% TODO: is figure needed?
+		\idea{Do I need a figure?, Something like this one?}
+		\begin{figure}[H]
+			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
+			\cite{pennartz2017consciousness}
+			\caption{xxxx}
+	   	\end{figure}
 

### 2018-10-26 Paper_neural_coarse_graining_of_consciousness.tex
Updates from ShareLaTeX
Update

@@
 	\section{Neural coarse-graining}
-		\subsection{intro}
-			\begin{ants}
-				@ As we mentioned above, to construct the NTIC process can bring agents great survival advantage.
-
-				@ However, to achieve NTIC (or even IC) is challenging for highly stochastic systems. Due to the stochasticity, the current states of the system have low predictability of its future states.
-
-				@ Previous research has been showing that the neural system are suffered from multiple noise sources  during information processing, including sensory, cellular, electrical, synaptic noises and have large trial-to-trial variability at the cellular level.
-\citep{faisal2008noise}.
-neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.
-
-				@ \rewrite{Neurons are subject to thermal fluctuations and other physical noise (Faisal et al., 2008).} \cite{faisal2008noise}
-
-				@ These noises sabotaged the predictability of future states and prevent the neural system from creating NTIC processes at the cellular level.
-
-				@ And every individual sensor only receives a little amount of information about the environment.
-
-				@ We argues that the human neural system to achieve NTIC through coarse-graining. 
-			\end{ants}
+
+		Nevertheless, to achieve information closure (so as NTIC) in highly stochastic systems (e.g., the neural system) is challenging.
+The current states of the system have low predictability of its future states due to the stochasticity.
+Information processing in the neural system is suffered from multiple noise sources throughout, including sensory, cellular, electrical, and synaptic noises.
+Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level.
+That is, the same pattern of activity never occurs twice even when the same stimulus is presented.
+Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
+Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment.
+Therefore, self and environmental predictive information is difficult to be represented at the cellular level.
+It is implausible to construct NTIC processes at this level.
+
+		However, to overcome the difficulty, the neural system to achieve NTIC through coarse-graining.
 
@@
 
-				@ Therefore, most of the high level cognitions can utilise the state of informational closure.
+				@ Therefore, most of the high level cognition can utilise the state of informational closure.
 

### 2018-11-08 Paper_neural_coarse_graining_of_consciousness.tex
Update from local

@@
 
-		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}
+		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}1
 
@@
 
+		%% stochasticity at microscopic levels
 		Nevertheless, to achieve information closure (so as NTIC) in highly stochastic systems (e.g., the neural system) is challenging.
@@
 Therefore, self and environmental predictive information is difficult to be represented at the cellular level.
-It is implausible to construct NTIC processes at this level.
-
-		However, to overcome the difficulty, the neural system to achieve NTIC through coarse-graining.
+It is implausible to construct NTIC processes at microscopic levels.
+
+		%% encoding information via coarse-graining
+		However, to overcome the difficulty, one way to encode a stable information in neural system is to encode information in coarse-grained variables.
+Coarse-graining here is referred to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}
+
+		%% Our argument
+
+		%% not monotonic
+		It is important to note that NTIC should not be a monotonic function of scale of coarse-graining.
+Overly coarse-graining system states can lead to low degrees of NTIC.
+For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have enough information capacity and thus losses  the self and environmental predictive power.
+This notion is also supported by empirical evidence.
+\cite{sederberg2018learning} showed that the efficiency of reading out  self-predictive information of neural population is higher when cell number in populations is 4 than 7 and 10-cell sets.
+This implies an optimal coarse-graining scale for NTIC processes.
+% Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}
 
@@
 			@ This implies that the information about the environmental dynamic should be represented at a certain coarse-grained level rather then other levels.
-
-			@ It is important to note that NTIC should not be a monotonic function of scale of coarse-graining. For the extreme case xxxxx
 
@@
 			@ However, information processing at the microscopic levels in the neural system is noisy.
-
-			@ \rewrite{
-				neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.}
-
-			%% Partial observable 
-			@ And every individual sensor only receives a little amount of information about the environment.
 

### 2018-12-18 Paper_neural_coarse_graining_of_consciousness.tex
Updates from ShareLaTeX

@@
 
-		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}1
+		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}
 
@@
 
-		%% encoding information via coarse-graining
-		However, to overcome the difficulty, one way to encode a stable information in neural system is to encode information in coarse-grained variables.
-Coarse-graining here is referred to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}
-
         %% Our argument
+		However, we argue that, by coarse-graining microscopic neural states, the neural system is able to achieve NTIC at certain coarse-grained macroscopic levels.
+To encode information in coarse-grained variables is a way to encode stable and robust information in neural system and overcome the difficulties to achieve NTIC at microscopic levels.
+Coarse-graining in this paper is referred to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}.
+In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}.
+This is a common strategy that we can see in large number of previous neurophysiological studies.
+For example, in the temporal domain, neural spikes across time can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
+Neurons encode stimulus intensity by increasing or decreasing firing rate.
+\citep{kandel2000principles}.
+In this coding scheme, individual neural spikes in a transient time span is not meaningful and stochastic \citep{stein2005neuronal}.
+In contrast, rate codes are relative stable and are highly robust against noise causing variation of inter-spike intervals.
+
+		% population code
+		Another example of coding strategy using coarse-graining is population coding.
+In this coding scheme, information is represented by joint spatiotemporal activities of several neurons.
+Therefore, the information is encoded in coarse-grained variables whose values are jointly determined by neural activation patterns within a neural population \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
+In such case, activities of every single neuron is not informative and stochastic.
+Instead, coarse-grained variables (such as population averaging and population vector) are able to represent information stably.
+Encoding information at coarse-grained levels allow the neural system ignores certain causal interactions relevant to fine-grained level of description \citep{Woodward2007-WOOCWA}.
+
+		% neural coarse-graining by Nic
+		It has been empirically implemented that NTIC can be achieved by coarse-graining snesory inputs in artificial neural networks.
+\citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture (fig.\ref{fig:NCG}) which aims to captures the emergent large-scale dynamics in the environment.
+The NCG network learns to coarse-grain input signals and extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.
+More importantly, using this architecture, agents can process information and act at coarse-grained macroscopic levels.
+
+		\begin{figure}
+			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
+			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
+			\label{fig:NCG}
+		\end{figure}
 
@@
 
+        %% Link to consciousness
+
+        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
+It gives agents living at this physical scale great advantages if the agents can build NTIC process internally.
+Therefore, to coarse-grain microscopic states is necessary
+
+        %This means that it is possible for agents to live at this physical scale to build NTIC process internally.
+        % More importantly, the information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
+
 		\begin{writingMaterials}
-
-			@ One way to encode a stable information in neural system is to encode the information in the coarse-grained variables.
-
 			@ \rewrite{
@@
 
-			@ \rewrite{
-				a number of different microstates,First, typically a number of different microstates, will realize the same value of the macro-variables of upper level causal theories.}
-
-			@ This is a common strategy that we can see in large number of previous physiological studies.
-
 			@ neural system use population coding and temporal coding to fight against noise.
@@
 			@ This implies that the information about the environmental dynamic should be represented at a certain coarse-grained level rather then other levels.
-
-			%% Our argument
-			@ We argues that the human neural system to achieve NTIC at a certain level of coarse-graining.
 
@@
 
-			%% Noise
-			@ However, information processing at the microscopic levels in the neural system is noisy.
-
-			@ Therefore, the dynamic of microscopic level is highly stochastic
-
 			%% coarse-graining is necessary
@@
 
-			%% About consicousness
-			@ More importantly, the information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
-
 		\end{writingMaterials}
 
-		\subsection{Coarse-graining in neural system}
-			\begin{ants}
-
-				@ Coarse-graining can be defined as a function that maps multiple microscopic states to a macroscopic states.
-
-				@ One way to encode a stable information in neural system is to encode the information in the coarse-grained variables.
+		\begin{comment}
 
@@
 
-				@ We have known that the neural system uses various coding strategies to encode information at coarse-grained levels.
-
 			@ \rewrite{Because the sequence of action potentials generated by a given stimulus varies from trial to trial, neuronal responses are typically treated statistically or probabilistically}
 
-				@ In the temporal domain, rate coding can be seem as coarse-graining on temporal events at the neuronal level \cite{stein2005neuronal}.
-
-				@ contained in the firing rate of the neuron
-
-				@ Firing rate of sensory neurons correlate stimulus intensities.  \citep{kandel2000principles}
-
-				@ This coding strategy is highly robust against noise causing variation of interspike intervals.
-
-				@ Another example is population coding.
-
-				@ Population coding is
-
-				the idea that nervous systems signal and compute parameters using large populations of imprecise neurons, rather than one or a few precise neurons.
-
-				@ \rewrite{
-						Population code (also ensemble code) denotes a code by which neural information is encoded in the spatiotemporal activity patterns of many neurons.
-					} \cite{binder2009encyclopedia}
-
-				@ In such case, single neurons are not informative. Instead, coarse-grained variables such as population averaging encode the information.
-
-				@ Encoding information at coarse-grained levels allow the neural system ignores certain causal interactions relevant to fine-grained level of description. \cite{price2007causation}
-
 			@ Note that, information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
 
-			\end{ants}
+		\end{comment}
 
@@
 
-		\subsection{Neural coarse-graining}
-			\begin{figure}
-				\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
-				\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
-				\label{fig:NCG}
-			\end{figure}
-
-			\begin{ants}
-				@ NTIC can be more easily achieved by coarse-graining.
-
-				@ \citep{guttenberg2016neural} proposed an architecture, called neural coarse-graining (NCG), which aims to captures the emergent large-scale dynamics in the environment.
-
+			\begin{comment}
 				@ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.
@@
 				@ Agents can process information and act at abstract levels
-			\end{ants}
-
-		\subsection{The advantage of NCG}
-			\begin{ants}
+			\end{comment}
+
+			\begin{comment}
 				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics.
@@
 				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
-			\end{ants}
-
-		\subsection{NTIC at specific levels of neural coarse-graining\callforhelp{any reference?}}
-			\begin{ants}
-				@ It is important to note that the relationship between degrees of NTIC and coarse-graining is not monotonic.
-
-				@ Overly coarse-graining a system can lead to low degrees of NTIC.
-
-				@ Imagining an extreme scenario that all microscopic states map to a single macroscopic state, the macroscopic process losses all the predictive information about the environment.
-
-				@ This is evidenced by empirical data as well.
-
-				@ Study by \cite{sederberg2018learning} found that self-predictive information of 4-cell sets readout by an optimal perceptron is higher than 7 and 10-cell sets.
-
-				@ The authors indicated that \blockquote[{\citep{sederberg2018learning}}]{reading out from groups of four cells can be accomplished with high absolute efficiency.
-Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}
-			\end{ants}
-
-\blockquote{reading out from groups of four cells can be accomplished with high absolute efficiency.
-Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}
+			\end{comment}
 

### 2019-01-21 Paper_neural_coarse_graining_of_consciousness.tex
Updates from ShareLaTeX
20190121_151428

@@
 
-	% ============================================================================ %
-	%                                  Out theory                                  %
-	% ============================================================================ %
 	\section{A neural coarse graining theory of consciousness}
-		\ideaBox{Need to describe my intuition more concretely}
-
-		\begin{ants}
-			\toWrite{Do I need to start with my philosophical intuition?}
+
+	    \subsection{reasoning about this idea}
+		\begin{ants}
+	    % Intuition
 
@@
 
-		\end{ants}
-
-		% ----------------------------------------------------------------------------
-
-		\begin{ants}
-
-			%% reasoning
-
-				@ ============= reasoning ============
+		% Reasoning
 
@@
 
-			%% our claim
-				@ ============ our claim  ============
-
+        % our claim   
 			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
@@
 
-			%% Following
+		% Following
 			@ In the following part, we....\todo{todo}
@@
 				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
-				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press .
+				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
 
@@
 
-		\subsection{Measure of conscious level}
-			\begin{ants}
-				@ The level of consciousness can be computed from how much degree of the non-trivial informational closure in a coarse-grained scale.
+		\subsection{Measure of consciousness/information correlate of consciousness}
+
+			\begin{ants}
+
+			@ In this framework, we postulate that the NTIC process is the core entity of information correlate of consciousness.
+
+			@ The content of consciousness corresponds to the state of the NTIC process.
+				\begin{equation}\label{eq:cContent}
+					C_{t}^{Content} = Y_{t}
+				\end{equation}
+
+			@ Furthermore, we can compute the level of consciousness via knowing the amount of information enclosed in a NTIC process.
+
+			@ We postulate that levels of consciousness $C_{t}^{Level}$ corresponds to the degree of NTIC at the coarse-grained level $NTIC_{t}$ at time $t$.
+
+				\begin{equation}\label{eq:cLevel}
+					C_{t}^{Level} = NTIC_{t}
+				\end{equation}
+
+			@ Therefore, this framework well integrates the two key but debated concepts in consciousness research \citep{laureys2005neural, bayne2016there}.
+
+			\subsubsection{consicous level}
+			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.
+
+			@ This also suggests that the richness of the environment being modelled by the			NTIC process has a direct contribution to the level of consciousness.
+
+			\end{ants}
+
+			\begin{writingMaterials}
 
@@
 
-			\end{ants}
-
-		\subsection{Conscious contents}
+			\end{writingMaterials}
+
+		\subsection{Coarse-graining states correlates conscious contents}
 			\begin{ants}
@@
 Therefore, a conscious percept reduces a huge amount of uncertainty.
+
+			@ This is similar to the the \textit{Information} axiom in integrated information theory which claims that
+
+\textquote[\citep[p. 2]{oizumi2014phenomenology}]{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...}
+
+``...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...''\citep[p. 2]{oizumi2014phenomenology}
 

### 2019-03-24 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

--- 2018-12-18 Paper_neural_coarse_graining_of_consciousness.tex
@@
 \usepackage{tikz}
-\usepackage[threshold=2, autopunct=true, autostyle=true]{csquotes}
 
@@
 % Real content
-	% Finished part
 	% Outline items that can be integrated into main text
@@
 			\end{easylist}
-			}
+			} %
 
 	% Writing Materials
-		\newenvironment{writingMaterials}
+\newenvironment{writingMaterials} %
 	{
@@
 	\end{tcolorbox}
-
 	\begin{easylist}[itemize]
@@
 
+% review loop annotation
+    \usepackage[xcolor, outerbars]{changebar}
+    \cbcolor{red}
+
+    % start anchor: \rlstart
+    \newcommand{\rlstart}[1]{  %
+        \setlength\changebarwidth{#1pt*2}  %
+        \hspace*{-40pt}
+        \cbstart{\textcolor{red}{\newline\textbf{iteration #1}}\newline}}
+
+    % end anchor: \rlend
+    \newcommand{\rlend}{\cbend}
+
+% quote
+\newcommand{\myQuote}[1]{\textit{``#1''}}
+
 % ============================================================================ %
@@
 \author[1]{Martin Biehl\thanks{martin@araya.org}}
+\author[1]{Yen Yu\thanks{martin@araya.org}}
 \author[1]{Ryota Kanai\thanks{kanair@araya.org }}
@@
 
+		% information-based claim 
+		Our theory takes a strong assumption that consciousness is information-based, information correlates of consciousness (ICC)\todo{Complete this argument}
+
 		%% About this paper
@@
 
-	% ============================================================================ %
-	%                                  Out theory                                  %
-	% ============================================================================ %
 	\section{A neural coarse graining theory of consciousness}
-		\ideaBox{Need to describe my intuition more concretely}
-
-		\begin{ants}
-			\toWrite{Do I need to start with my philosophical intuition?}
+
+\rlstart{3}
+        In this section, we formally introduce our theory \tnamefull \todo{We need a good name}.
+
+        We starts our argument from a presumptive fact that every human conscious precept is ex trimly informative.
+Our conscious experience always consists of high multidimensional information involved multiple modalities.
+Considering information as resolved uncertainty, every conscious percept rules out enormous other possible conscious states in the state space, therefore, gives huge amount of of information.
+This notion is similar to one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0, \cite{oizumi2014phenomenology}) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
+2]{oizumi2014phenomenology}.
+
+        Based on this presumptive fact, we further take a radical standpoint and postulate that consciousness fundamentally associate with information in the physical reality (information correlates of consciousness, \cite{chalmers1996conscious, tononi2004information, gamez2011information}) rather than neuronal states (neural correlates of consciousness).
+That is, consciousness should be information-based.
+The amount of information comprising a conscious percept should be equivalent to information we can obtain from a specific physical event.
+
+        Nevertheless, even though information involved in every conscious percept is extremely rich, it is still bounded, i.e.
+boundary exists.
+Presuming consciousness is information-based, we can deal with the boundary problem \cite{goff2006experiences} by information closure.
+Additionally, our conscious experience contains not merely trivial informational rather it always provides rich information about the environmental and our bodily states.
+Therefore, we argue that NTIC is the core entity \highlightAndComment{responsible}{Help me to think of a better term} for consciousness.
+
+		\begin{ants}
+
+        @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.
+
+        @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
+
+		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
+
+		@ This drives the neural system to create a non-trivial informational closure.
+
+        @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.
+
+        @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.
+
+		@ Therefore, coarse-graining becomes necessary because every individual sensor and neuron at the microscopic scale can only access and process a small part of information.
+
+		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})
+
+        @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.
 
@@
 
-			@ If the new set of variables are informational closured, then this creates a new "reality" for all the variables inside.
-
-			@ Reality means the all the information (include variables and the relationships) within the boundary of causal or informational influence between variables.
+        @ information is scale-dependent
+
+		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.        
+		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.
+
+        @
+
+        @ Relationship between coarse-graining, scale and interaction with environment
+
+		@ \rewrite{
+			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
+
+			@@ conscious perception are very stable and time invariant.
+			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
+
+        @ To summaries, in our framework, consciousness is 
+			    @@ Intrinsic
+
+			    @@ Informative
+
+				@@ scale-dependent
+
+        % our claim   
+			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
+
+			@ We further postulate that level of consciousness corresponds to informational closureness of processes.
+
+			@ The contents of consciousness correspond to the states of the non-trivial informational closure.
+
+		% Following
+			@ In the following part, we....\todo{todo}
+
+		\end{ants}
+
+		\begin{writingMaterials}
 
@@
 			@ It also means everything in this system is self-defined.
-
-		\end{ants}
-
-		% ----------------------------------------------------------------------------
-
-		\begin{ants}
-
-			%% reasoning
-
-				@ ============= reasoning ============
-
-				@ Information processing in the neural system exists at different level of abstraction.
-
-				@ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
-
-				@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
-
-				@ This drives the neural system to create a non-trivial informational closure.
-
-				@ \idea{okay, I need to be very careful about the causal relation here.}
-
-				@ Therefore, coarse-graining becomes necessary because every individual sensor and neuron at the microscopic scale can only access and process a small part of information.
-
-				@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:CGandIC})
-
-			%% our claim
-				@ ============ our claim  ============
-
-				@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
-
-				@ We further postulate that level of consciousness corresponds to informational closureness of processes.
-
-				@ The contents of consciousness correspond to the states of the non-trivial informational closure.
 
@@
 \cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}
-
-			%% Following
-				@ In the following part, we....\todo{todo}
-
-		\end{ants}
-
-		\begin{figure}[H]
-			\includegraphicsTodo[width=\textwidth]{CGandIC.png}
-			\caption{informational closure through neural coarse-graining}
-			\label{fig:CGandIC}
-		\end{figure}
-
-		% ==================================== %
-		% Backup
-		% ==================================== %
-		\begin{ants}
 
@@
 				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
-				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press .
-
+				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
 			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
 
-			@ Consciousness is information
-				@@ Information is level-dependent.
-
-				@@ Information is different at microscopic and macroscopic levels
-
-				@@ Consciousness must be level-dependent
-
-			@ \rewrite{
-				This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
-
-				@@ conscious perception are very stable and time invariant.
-				@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
-		\end{ants}
-		% ==================================== %
-
-		\subsection{Measure of conscious level}
-			\begin{ants}
-				@ The level of consciousness can be computed from how much degree of the non-trivial informational closure in a coarse-grained scale.
-
-				@ Based on Equation xxx\todo{equation}, the measure of non-trivial informational closure can be decomposed to XXX and XXX.
-
-				@ use \includegraphics{WritingMaterials/PDFXCview_2018-06-01_17-44-30.png}
-
-				@ or use \includegraphics{WritingMaterials/PDFXCview_2018-06-04_19-18-12.png}
+		\end{writingMaterials}
+
+\rlend
+
+\rlstart{3}
+		\subsection{Measure of consciousness/information correlate of consciousness}
+
+			\begin{ants}
+			@ In this thesis, we postulate that NTIC is the core entity of information correlate of consciousness.
+
+			@ We further propose properties of consciousness correlate properties of NTIC
+
+			quantitative hypotheses of conscious level and conscious content.
+
+			@ We first hypothesise that, at time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of NTIC at coarse-grained levels $NTIC_{t}$.
+
+				\begin{equation}\label{eq:cLevel}
+					C_{t}^{Level} = NTIC_{t}
+				\end{equation}
+
+			@ We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
+				\begin{equation}\label{eq:cContent}
+					C_{t}^{Content} = Y_{t}
+				\end{equation}
+
+			@ We discuss the implications of the two hypotheses in the following. 					
+			\end{ants}
+			`
+
+			\subsubsection{Level of Consciousness correlates degrees of NTIC of a process}
+    			\begin{ants}
+    			@ Several key insights about the conscious level can be derived from our theory.
+
+    			@ Equation \ref{eq:nticObjective} implies that conscious level positive correlates the complexity of the environment that the NTIC process encoded.
+
+    			@ This implies that an agent who forms an NTIC process to lives and adapt to a more complex environment should have a higher conscious level than another agent who lives in an environment with more simple dynamics.
+
+    			@ Channel capacity between the current state and the future state of the NTIC process also determines the level of consciousness.
+
+    			@ \todo{Need an example here} A small creatures may live in a simple environment and forms a NTIC process.
+The predictive information for the next state of the process may be very low.
+It has consciousness but the levels of consciousness is low.
+
+    			@ Another implication about levels of consciousness from Equation \ref{eq:nticObjective} predictability of the system future state given the current state is crucial for the conscious level.
+This indicates that the if the system dynamics are highly scholastic and much unpredictable, the conscious level should be low.
+This notion explicitly indicates that information processed at neuronal scales which encounter heavy noise and are highly scholastic cannot form high level of consciousness.
+
+    			@ Similarly, at macro-scales, if coarse-graining causes coarse-grained macro-variable lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well.
+K
+
+    			@ \todo{modify this figure}
+
+    				\begin{figure}[H]				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
+    				\label{fig:LevelOfConsciousness}
+    				\caption{Level of coarse-graining and level of consciousness.
+The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
+    				\end{figure}
+
+    			@ This non-monotonic relationship bwetween the level of coarse-graining in the neural system and the degree of NTIC explains why only information processed at a certain level can become conscious contents.
+
+    			\end{ants}
+
+    		\subsubsection{Coarse-graining states correlates conscious contents}
+    			\begin{ants}
+				@ We claim that conscious contents correspond to the state of the NTIC process.
+
+				@ This implies that the complexity of conscious contents is determined by the amount of information encompassed in the NTIC process.
+
+				@ Therefore, larger state space of the NTIC process has, richer  experience the process can be conscious of (e.g., a NTIC process with high dimensionality).
+
+				@ Crucially, even experience of darkness is rich because it rules out other enormous potential state that the NTIC process can be in.
+Equivalently, knowing the state of the NTIC process when the process experiences darkness also mean acquisition of information of the system.\todo{bad wording}
+
+    			@ This is similar to the the \textit{Information} axiom in integrated information theory which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
+2]{oizumi2014phenomenology}
+
+    			@ \todo{Need an example here} Follow the example in the last section, a small creatures may live in a simple environment and forms a NTIC process.
+The predictive information for the next state of the process may be very low.
+This also implies the richness of the conscious experience this agent has is very limited.
+
+    			@ Our theory naturally explains why consciousness is compositional, because the joint states of entities in the NTIC process determine the contents of consciousness.
+\ideaCallout{think about it}
+
+				@ Importantly, note that because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale.
+
+				@ This supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.
+
+			\end{ants}
+
+	    \subsubsection{Reconcile level and content of consciousness}
+	        \begin{ants}
+	            @ Our theory link conscious level and conscious content together via the state space of the NTIC process.
+
+	            @ When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness.
+Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system.
+
+	            @ levels and contents of consciousness are just two different measures of a NTIC process.
+
+	            @ this indicates an important prediction in which the conscious level is determined by states that the NTIC process potentially can reach rather the current state of a system.
+
+	            @ For example, some neural states may map to simple sensory experience, e.g.
+visual experience in a dark room.
+However, this does not degrade the conscious level.
+This experience still provides a huge amount of information because it excludes enormous possibilities of visual experience and decrease a large amount of uncertainty.
+
+    			@ Therefore, this framework well integrates the two key but debated concepts in consciousness research \citep{laureys2005neural, bayne2016there}.
+
+				@ \rewording{Note that, our claim is that informational closure is a more fundamental property that correlates consciousness.
+A species acquiring advantage to model a complex environment through evolution and , therefore, achieving a high-level non-trivial informational closure has a high level of consciousness, is the consequence of the evolution process.
+}
+
+	        \end{ants}
+
+			\begin{writingMaterials}
+    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.
+
+    			@ This also suggests that the richness of the environment being modelled by the			NTIC process has a direct contribution to the level of consciousness.
 
@@
 
-				@ \rewording{Note that, our claim is that informational closure is a more fundamental property that correlates consciousness.
-A species acquiring advantage to model a complex environment through evolution and , therefore, achieving a high-level non-trivial informational closure has a high level of consciousness, is the consequence of the evolutional process.
-}
-
-			\end{ants}
-
-		\subsection{Conscious contents}
-			\begin{ants}
-				@ We claim that conscious contents correspond to the state of the informational closure.
-
-				@ \idea{= not sure I want to say this here =}
-
-				@ Consciousness is informative.
-A conscious percept including volition and intention is a unique state that narrowing down all possible states into one.
-Therefore, a conscious percept reduces a huge amount of uncertainty.
-
-				@ This is the same claim as the third axiom called "information" in IIT. \needref{information axiom and need to say more about this.}
-
-				@ ====================================
-
-				@ Note that because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale.
-			\end{ants}
-
-		\subsection{Sensory hierarchy and neural coarse-graining
-			\critical{This is super important. I need to deal with this very carefully. Need to completely rewording}}\label{sec:SensoryHierarchy}
+			\end{writingMaterials}
+
+\rlend
+
+\rlstart{1}
+		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
 
 			\begin{figure}[H]
-				\includegraphicsTodo[width=0.8\textwidth]{hierarchy.pdf}
-				\caption{Coarse-grain and sensory anatomical hierarchies}
+				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
 				\label{fig:hierarchy}
@@
 
-			\begin{figure}[H]
-				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
-%				{Coarse-grain and sensory anatomical hierarchies}
-			\end{figure}
-
-			\begin{ants}
-				@ It's important to note that the coarse-graining direction is not necessary to be align with anatomical sensory hierarchy in the neural system.
-
-				@ the coarse-grained information is needed and computed only when the information is required for microscopic scale processing.
-
-				@ \toWrite{I need a strong example here}
-
-				@ Of course, from evolutional perspective, neural system should develop a better hardware to support neural coarse-graining
+			\begin{ants}
+				@ It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough.
+Need better expression} anatomical sensory hierarchy in the neural system.
+
+				@ the coarse-grained information is needed and computed only when the information is required for microscopic scale processing (readout).
+
+				@ Therefore, our theory is very different from consciousness theories focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
+
+				@ The truth is that due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
+
+				@ Nevertheless, to exercise causal power in actuators and environments, to read out information at coarse-grained levels is necessary.
+
+				@ In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
+
+				@ We argue that the neural correlates of consciousness may not be the fundamental principles for consciousness. The data may contaminate the understanding of consciousness. 
+			\end{ants}
+
+            \begin{writingMaterials}
+    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining
 
@@
 				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
-
-			\end{ants}
-
-		\subparagraph{more information theory and philosophy relevance}
-			\begin{writingMaterials}
-				@ One consequence of coarse-graining is that it makes it permissible to ignore certain causal factors that would be relevant at more fine-grained level of description. \cite{price2007causation}
-
-				@ This means the fine-grain variable does not exist at the coarse-grained causal chain.
             \end{writingMaterials}
-
-		% ============================================================================ %
-		%                         Information and system theory                        %
-		%                                                                              %
-		% ============================================================================ %
-		\subsection{Information and system theory}
-			\idea{A closure can define a system, consciousness is information}
-
-			\idea{Could be linked to system theory, but may need help}
-
-			\rewrite{
-				This self-referential distinction from its environment therefore gives rise to the specific autonomy of such a system.
-Consequently, in systems theory, closure properties and autonomy are considered to be closely related concepts which are both at the heart of defining the system itself.}
-
-		\subsection{Empirical approaches of measuring neural informational closure}
-
-	\section{Conscious vs unconscious processing}
+\rlend
+
+        \subsection{About boundary}
+            \begin{ants}
+                @ boundary is fluid 
+            \end{ants}
+
+\rlstart{1}
+	\section{Conscious versus unconscious processing}
 		\ideaBox{Now we can combine "Relation to empirical findings in neuroscience and studies of consciousness" and "About Phenomenology (conscious processing)" in to this}
+
+		\begin{ants}
+		    @ Our theory indicates that conscious information needs to fulfil two necessary conditions.
+
+		    @ 1. The information is processed at a certain coarse-grained
+
+		    @ 2. encoded in the NTIC process
+
+		    @ Based on the two conditions, we can classify brain processes into conscious and unconscious processing based on the two conditions.
+
+		\end{ants}
+
+		\subsection{Conscious Processing}
+		    \begin{ants}
+		        @ To achieve high NTIC has evolutionary advantage.
+
+		        @ The current state of the process contains the information about its future state.
+Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process.
+
+		        @ Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning, imagination, dreaming)
+		    \end{ants}
+
+		\subsection{Unconscious Processing}
+		    \begin{ants}
+    		    @ When processes fail to satisfy either of the two conditions, they remain unconscious.
+
+    		    @ When processes do not meet the first condition, i.e. the information processed not at the certain coarse-grained level, the information will not be included in conscious contents.
+
+    		    @ For example, we are never conscious of neural spike activities at microscopic levels (e.g.
+single cell activities) because information passing among individual neurons are not at the certain coarse-grained level.
+
+    		    @ Libet's free will experiment can be also explained by our theory.
+
+    		    @ The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.
+
+    		    @ When processes do not meet the second condition, i.e. processes which do not achieve high NTIC will remain unconscious.
+
+    		    @ This can explain why many "policy-based" processes are not conscious.
+
+    		    @ Policy-based here features those processes taking sensory information as input and directly outputting actions.
+Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure.
+
+    		    @ Several neural processes are included in this category, e.g. reflexive neural circuit, blindsight, procedure memory. 
+		    \end{ants}
+
+        \subsection*{}
+            \begin{ants}
+                @ To summarise, our theory can well explain the various findings with parsimonious assumptions. 
+            \end{ants}
+
+\rlend
 
@@
 		\ideaBox{Main points should be same/diff, our advantages, and predictions}
-
-		\subsection{Theories about level of abstraction and coarse-graining}
-			\begin{ants}
-				@ Before the current theory, several theories and perspectives of consciousness have proposed the notion that links level of abstraction or coarse-graining in the neural system to consciousness.
+		\begin{ants}
+		    @ In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness. 
+		\end{ants}
+
+\rlstart{1}
+		\subsection{Theories about multilevel views on consciousness and cognition}
+			\begin{ants}
+			    @ Previously, multilevel views on consciousness and cognition have been proposed.
+
+			    @ In the following, we discussed the differences between our theory and other theories about multilevel views.
+
+			\end{ants}
+
+			\begin{writingMaterials}
+			    @ LEVELS OF ORGANIZATION \cite{wimsatt1994ontology}
+
+			    @ As mentioned previously, the level of coarse-graining is different from the anatomical level.
+
+			    @ \ideaBox{Should I also deal with Marr's level of abstraction?}
+
+			    @ See the discussion in \cite{pennartz2015brain}. But Pennartz focus more on multimodal representation as the most important factor.
+
+			    @ Our proposal is inline with Pennartz's Neurorepresentational theory (Neurorepresentationalism). \cite{pennartz2018consciousness,pennartz2015brain}.
+
+			    @ Some theories also address the relationship between level of processing and consciousness.
+
+			    @ However, it’s crucial to note that our theory claims only the level of coarsegraining achieving NTIC matters to connsciousness rather than the anatomical level of sensory hierarchy
 
 				@ We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.			    
-			\end{ants}
-
-			\subsubsection{Intermediate Level Theory}
+			\end{writingMaterials}
+
+			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
 				\begin{ants}
 				@ Intermediate Level Theory (ILT) proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy.
-\citep{prinz2007intermediate, jackendoff1987consciousness}.
 This theory claims that consciousness only associates with the representation at  intermediate levels rather than the ones at lower-level or higher-level.
 
-					@ A critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of  anatomical processing levels along cortical hierarchies.
-				\end{ants}
-
-				\begin{comment}
+				@ As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).
+				\end{ants}
+
+			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
+			    \begin{ants}
+			    @ Our theory shares some similar concepts with Pennartz's Neurorepresentationalism.
+
+		        @ However, Neurorepresentationalism focuses on multimodal representation.
+
+		        @ Neurorepresentationalism also focuses on "making sense" between representation
+
+		        @ We focus on informational closure which suggests the closure of causal interaction in a system.
+
+		        @ We don't assume any functional properties as the criteria of consciousness. Instead, we propose information as a more fundamental principle correlates consciousness.  
+			    \end{ants}
+
+				\begin{writingMaterials}
 					%% Back up materials
+
+					@ Prinz suggested that \rewrite{as.
+Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously.
+} \cite{prinz2007inter    mediate}
+
+				    @ Our prediction is, if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.
+
 					@ \rewrite{
@@
 						I conclude that the intermediate level plays a distinctive and important computational role.
-Some researchers fi nd this puzzling.
+Some researchers find this puzzling.
 In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels.
@@
 					@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain.
-The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}
-				\end{comment}
-
-			\subsubsection{The difference between ILT and our theory}
-				Prinz suggested that \rewrite{as.
-Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously.
-} \cite{prinz2007intermediate}
-
-				* Our prediction is, if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.
-
+The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
+				\end{writingMaterials}
+
+\rlend
+
+\rlstart{1}	
 		\subsection{First-order theories}
+
+            \begin{ants}
+
+		    @ The ﬁrst-order theories suggest that consciousness is determined by early sensory information or neural activities.\needref{First-order theories}
+
+		    @ We suggest that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness.
+
+		    @ However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.
+
+		    \end{ants}
+
 			\begin{writingMaterials}
-				@\rewrite{
+				@ \rewrite{
 					The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
@@
 
-				@ Among those are first-order theories, on which a mental state is conscious if being in that state results in one’s being conscious of something;
+				@ Among those are first-order theories, on which a mental state is conscious if being in that state results in one's being conscious of something;
 
@@
 
+\rlend
+
+\rlstart{1}
+		\subsection{Higher Order Thought theory of consciousness}
+			\idea{
+				People think a high order representation receives information from the first order representation.
+This may be a misunderstanding.
+This may be the result of neural coarse-graining.
+Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it}
+
+			============================================================================
+			\begin{ants}
+			    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
+
+			    @ Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
+
+			    @ It is true that the neural system does create  meta-representation to represent xxx.\needref{Maybe come studies about confidence represenatation}
+
+			    @ The higher-order representation may resemble coarse-grained variables.
+
+			    @ This may cause misidentify the entity which correlates conscious experience.
+
+			    @ ----------------------------------------------------------------------------
+
+				@ Information closure directly is critical for other systems to construct forward models.
+
+				@ Therefore, most of the high level cognition can utilise the state of informational closure.
+
+				@ For example, mental planning needs a precise forward model to infer the environmental dynamics.
+
+				@ \idea{This is way HOT always involve consciousness }
+
+				@ \cite{rosenthal2005consciousness}
+			\end{ants}
+
+            \begin{writingMaterials}
+			@ \rewrite{
+				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}
+
+			@ \rewrite{
+				According to this view, humans not only have first-order non-conceptual and/or analog perceptions of states of their environments and bodies, they also have second-order non-conceptual and/or analog perceptions of their first-order states of perception.
+And the most popular version of higher-order perception theory holds, in addition, that humans (and perhaps other animals) not only have sense-organs that scan the environment/body to produce fine-grained representations that can then serve to ground thoughts and action-planning, but they also have inner senses, charged with scanning the outputs of the first-order senses (i.e.
+perceptual experiences) to produce equally fine-grained, but higher-order, representations of those outputs (i.e.
+to produce higher-order experiences).
+A version of this view was first proposed by the British Empiricist philosopher John Locke (1690).
+In our own time it has been defended especially by Armstrong (1968, 1984) and by Lycan (1996).} \url{https://plato.stanford.edu/entries/consciousness-higher/#SelRepHigOrdThe}
+
+			@ \rewrite{
+				neutral about whether conscious awareness adds signiﬁcant utility or immediate impact on behavior and task performance [1,27].
+This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on ﬁrst-order rather than higher-order representations.
+Because conscious awareness can differ even if all ﬁrst-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
+				\ideaCallout{
+					My theory would have similar prediction.
+Because conscious contents are coarse-grained results from low-level information.
+It is possible that more than two low-level neural states all coarse-grained to a high-level state.
+}
+
+			@ \rewrite{
+					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world.
+In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efﬁcacy of a perceptual process.
+The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}
+
+			\end{writingMaterials}
+
+\rlend
+
+\rlstart{1}
 		\subsection{Global workspace theory}
@@
 
+				@ Submodule access and NTIC
+
 				%% Our theory
 
-				@ GW in previous data is the place that form NTIC.
-
-				@ non-linearity and emergence
-
-				@ what's the different prediction?
-
-				@ We predict that when the new
+				@ Our theory can well accommodate several claims by GWT.
+
+				@ Conscious perception necessitates representational stability: Our theory rests upon self-predictability which formally encompasses stability.
+
+				@ Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC.
+The neural system can extract the information for specific task goals.
+This is equivalent to the function of broadcasting.
+
+				@ Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates.
+In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process.
+This can cause a significant change of the brain states and resembles non-linear ignition of brain activities.
+
+				@ our theory re-explains the critical xxx from GWT.
+
+				@ The critical difference is that our theory does not suggest a neuronal core anatomical area for consciousness. We suggest coarse-grained information form NTIC is crucial for consciousness.
+
+				@ In sum, our theory is compatible with previous physiological evidence supporting GWT.
 
@@
 			\subsubsection{Global availability and Broadcasting}
-
-			\subsubsection{Code translation}
-				\begin{ants}
-					@ neural coarse-graining can natually solve this problem.
-					@ coarse-graining between levels can be thought as code translation\todo{is this true?}
-				\end{ants}
 
@@
 			\end{ants}
-
-		\subsection{Higher Order Thought theory of consciousness}
-			\idea{
-				People think a high order representation receives information from the first order representation.
-This may be a misunderstanding.
-This may be the result of neural coarse-graining.
-Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it}
-
-			============================================================================
-			\begin{ants}
-				@ Information closure directly is critical for other systems to construct forward models.
-
-				@ Therefore, most of the high level cognition can utilise the state of informational closure.
-
-				@ For example, mental planning needs a precise forward model to infer the environmental dynamics.
-
-				@ \idea{This is way HOT always involve consciousness }
-
-				@ \cite{rosenthal2005consciousness}
-			\end{ants}
-
-			\rewrite{
-				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}
-
-			\rewrite{
-				According to this view, humans not only have first-order non-conceptual and/or analog perceptions of states of their environments and bodies, they also have second-order non-conceptual and/or analog perceptions of their first-order states of perception.
-And the most popular version of higher-order perception theory holds, in addition, that humans (and perhaps other animals) not only have sense-organs that scan the environment/body to produce fine-grained representations that can then serve to ground thoughts and action-planning, but they also have inner senses, charged with scanning the outputs of the first-order senses (i.e.
-perceptual experiences) to produce equally fine-grained, but higher-order, representations of those outputs (i.e.
-to produce higher-order experiences).
-A version of this view was first proposed by the British Empiricist philosopher John Locke (1690).
-In our own time it has been defended especially by Armstrong (1968, 1984) and by Lycan (1996).} \url{https://plato.stanford.edu/entries/consciousness-higher/#SelRepHigOrdThe}
-
-			\rewrite{
-				neutral about whether conscious awareness adds signiﬁcant utility or immediate impact on behavior and task performance [1,27].
-This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on ﬁrst-order rather than higher-order representations.
-Because conscious awareness can differ even if all ﬁrst-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
-				\ideaCallout{
-					My theory would have similar prediction.
-Because conscious contents are coarse-grained results from low-level information.
-It is possible that more than two low-level neural states all coarse-grained to a high-level state.
-}
-
-			\subsubsection{Metacognition}
-				\rewrite{
-					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world.
-In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efﬁcacy of a perceptual process.
-The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}
+\rlend
 
@@
 
+\rlstart{1}
 		\subsection{Integrated information theory\callforhelp{Help from Jun?}}
 			\begin{ants}
+
+			@ One common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness. \needref{cite David Chalmers}
+
+			@ Our theory is different from IIT which proposes that consciousness is information integration in a system.
+
+			@ For level of consciousness, IIT predicts a system with higher level of integration produces a higher level of consciousness.
+In our theory, the level of consciousness corresponds to the level of NTIC, which suggests that level of consciousness is determined by self-predictive information and the information about the environment encoded in the process.
+
+			@ In terms of conscious content, IIT suggests that the causal structure of a system determines the quality of conscious contents.
+In the current version of our theory, how the state of NTIC process maps to conscious content has not been sophisticatedly specified.
+More work is needed to understand the relationship between the state of NTIC process and conscious contents.
+
+		    @ --------------------------------------------------------------------
 			@ \toWrite{Information integration without awareness}\cite{Mudrik_Faivre_Koch}
-				@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} I would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an informational closure representation.
+			@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} we would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an informational closure representation.
 
@@
 				\begin{ants}
+
+				    @ Our theory is closely related to causal emergence described by Hoel et al.
+(2013) which was examined by a following work using integrated information theory (Hoel et al.
+2016).
+More research on the precise mathematical relationship between causal emergence and our theory is needed
+
 					@ \cite{hoel2016can}
@@
 
+\rlend
+
 		\subsection{Internal simulation and self-modelling theory}
 
+    \section{Limitation}
+        \begin{ants}
+            @ Our theory does not explain the mapping
+        \end{ants}
+
 	\section{Future works}
@@
 
-			@ Lack of direct evidence because no one focus on informational closure
-
-		\end{ants}
-
-		\subsection{About location of NTIC}
-		\subsection{Attention}
-			Attention can be when the neural want to output a specific information in NTIC.
-
-%		\subsection{We didn't specify what dynamic in the NTIC process associates with conscious contents.}
+			@ Lack of direct evidence because no one focus on informational closure.
+
+			@ Physiological location of NTIC
+
+			@ Practical measure of NTIC.
+
+		\end{ants}
 

### 2019-04-04 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 \usepackage{tcolorbox}
+\tcbuselibrary{skins}
 \usepackage{comment}
+\usepackage[framemethod=tikz]{mdframed}
+\usetikzlibrary{shadows}
 
@@
 	{
-	\begin{tcolorbox}[size=small, colframe=black!20!white, toprule=1mm]
+        \begin{tcolorbox}[enhanced,
+            title=-,
+            size=small,
+            colbacktitle=Aquamarine,
+            drop fuzzy shadow,
+            fontupper=\small,
+            boxrule=0.4pt,
+            colback=Aquamarine!10!white,
+            sharp corners]
             Writing Materials
@@
         \end{easylist}  
-	\begin{tcolorbox}[size=small, bottomrule=1mm, halign=flush right, colframe=black!20!white]
-		Writing Materials
+        \begin{tcolorbox}[enhanced,
+            halign=flush right,
+            halign title=right,
+            size=small,
+            colbacktitle=Aquamarine,
+            drop fuzzy shadow,
+            fontupper=\small,
+            boxrule=0.4pt,
+            colback=Aquamarine,
+            colupper=White,
+            sharp corners]
+            Writing Materials -
         \end{tcolorbox}        
 	}	
+% 	\newenvironment{writingMaterials} %
+% 	{
+%         \begin{mdframed}[%
+%             frametitle=- Writing Materials,
+%             frametitlefont={\small\color{white}},
+%             middlelinecolor=Black,
+%             shadow=true,
+%             shadowsize=2mm,
+%             frametitlebackgroundcolor=Aquamarine,
+%             frametitlerule=true,
+%             backgroundcolor=Aquamarine!10!white]
+%         \noindent
+%         \begin{easylist}[itemize]
+% 	}
+% 	{
+%         \end{easylist}  
+%         \end{mdframed}
+% 	}
+% \newenvironment{writingMaterials} %
+% 	{
+%         \begin{tcolorbox}[enhanced,
+%         breakable,
+%         title=Writing Materials,
+%         colbacktitle=Aquamarine,
+%         drop fuzzy shadow,
+%         fontupper=\small,
+%         boxrule=0.4pt,
+%         colback=Aquamarine!10!white,
+%         sharp corners]
+
+%         \begin{easylist}[itemize]
+% 	}
+% 	{
+%         \end{easylist}  
+%         \end{tcolorbox}	
+% 	}	
+% \newenvironment{writingMaterials} %
+% 	{
+% 	\begin{tcolorbox}[size=small, colframe=black!20!white, toprule=1mm]
+% 		Writing Materials
+% 	\end{tcolorbox}
+% 	\begin{easylist}[itemize]
+% 	}
+% 	{
+% 	\end{easylist}
+% 	\begin{tcolorbox}[size=small, bottomrule=1mm, halign=flush right, colframe=black!20!white]
+% 		Writing Materials
+% 	\end{tcolorbox}
+% 	}
 
@@
 
+		% figure todo callout
+        \newcommand{\needfig}[1]{%
+			\ifthenelse{\equal{#1}{}}{%
+				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig}}}{%
+				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig: #1}}%
+			}%
+		}
+
 		% rewording
@@
 
-	% Highlight
+	% Highlight: Yellow or Red
 		% Highlight only
-		\newcommand{\highlight}[2][Thistle!50!white]{\colorbox{#1}{#2}}
+		\newcommand{\highlight}[2][Yellow!75!white]{\colorbox{#1}{#2}}
 
 		% Highlight and comment
-		\newcommand{\highlightAndComment}[3][Thistle!50!white]{\todo[color=#1]{#3}\colorbox{#1}{#2}}
+		\newcommand{\highlightAndComment}[3][Yellow!75!white]{\todo[color=#1, linecolor=Yellow]{#3}\fcolorbox{Black}{#1}{#2}}
 
@@
 		\newcommand{\critical}[1]{%
-			\todo[color=OrangeRed!70!white]{#1}
+			\todo[color=OrangeRed!80!white]{#1}
 		}
@@
 			\newcommand{\ideaBox}[1]{
-				\begin{tcolorbox}[%
-					width=12cm,
-					sharp corners=downhill,
-					hyphenationfix,
-					arc=8pt,
+				\begin{tcolorbox}[enhanced,%
+                    title=-,
+                    center,
+                    fontupper=\small,
+                    lifted shadow={1mm}{-2mm}{3mm}{0.1mm}{black!50!white},%
+                    boxrule=0.4pt,
+                    width=9cm,
                     colback=Thistle!50!white,
-					flush right,
-					halign=flush right,
-					]%
+                    sharp corners]
 					#1
@@
 % ============================================================================ %
-\title{A neural coarse graining theory of consciousness}
+\title{A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness }
 
@@
 
+    \newpage
+    \section*{Not decided terminology}
+        \begin{ants}
+            @ information * in the NTIC process
+            @ Full and short name of this theory
+            @ core "?" (entity) for conscious content 
+            @ our theory? framework? proposal? 
+            @ system? process?
+            @ variable? node? element? member?
+        \end{ants}
+
 	% ============================================================================ %
@@
 
+    \newpage
 	\section{Introduction}
@@
 
-		\begin{ants}
+        For example, in the physical world, if there exists two systems Alice and Bob, but there is no information flow between them (or we can say no causal influence from one to the other).
+If we assume that Alice has consciousness experience, the information enclosed in Alice's conscious contents must not include any information about Bob.
+
+        We can treat information as a common language between conscious experience and physical world.
+
+        Through coarse-graining, to achieve NTIC processes becomes possible in the neural system at macroscopic levels.
+Therefore, coarse-graining becomes necessary because every individual sensor and neuron at the microscopic scale can only access and process very limited partial information (Fig.
+\ref{fig:LevelOfConsciousness}).
+In the following, ...
+
+		\begin{writingMaterials}
 
@@
         @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.
-
-		@ Therefore, coarse-graining becomes necessary because every individual sensor and neuron at the microscopic scale can only access and process a small part of information.
 
@@
 		\subsection{Measure of consciousness/information correlate of consciousness}	
-
-			\begin{ants}
-			@ In this thesis, we postulate that NTIC is the core entity of information correlate of consciousness.
-
-			@ We further propose properties of consciousness correlate properties of NTIC
-
-			quantitative hypotheses of conscious level and conscious content.
-
-			@ We first hypothesise that, at time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of NTIC at coarse-grained levels $NTIC_{t}$.
-
+		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computes the properties of a NTIC process.
+\newline
+
+		\noindent
+		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of  $NTIC_{t}$ at a coarse-grained level.
 			\begin{equation}\label{eq:cLevel}
@@
 
-			@ We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
+		\newline
+		\noindent 
+		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
 			\begin{equation}\label{eq:cContent}
@@
 
-			@ We discuss the implications of the two hypotheses in the following. 					
-			\end{ants}
-			`
-
-			\subsubsection{Level of Consciousness correlates degrees of NTIC of a process}
-    			\begin{ants}
-    			@ Several key insights about the conscious level can be derived from our theory.
-
-    			@ Equation \ref{eq:nticObjective} implies that conscious level positive correlates the complexity of the environment that the NTIC process encoded.
-
-    			@ This implies that an agent who forms an NTIC process to lives and adapt to a more complex environment should have a higher conscious level than another agent who lives in an environment with more simple dynamics.
-
-    			@ Channel capacity between the current state and the future state of the NTIC process also determines the level of consciousness.
-
-    			@ \todo{Need an example here} A small creatures may live in a simple environment and forms a NTIC process.
-The predictive information for the next state of the process may be very low.
-It has consciousness but the levels of consciousness is low.
-
-    			@ Another implication about levels of consciousness from Equation \ref{eq:nticObjective} predictability of the system future state given the current state is crucial for the conscious level.
-This indicates that the if the system dynamics are highly scholastic and much unpredictable, the conscious level should be low.
-This notion explicitly indicates that information processed at neuronal scales which encounter heavy noise and are highly scholastic cannot form high level of consciousness.
-
-    			@ Similarly, at macro-scales, if coarse-graining causes coarse-grained macro-variable lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well.
-K
+		We discuss the implications of the two hypotheses in the following. 	
+	    \subsection{Level of Consciousness correlates degrees of NTIC of a process}
+
+	    Our theory indicates that conscious levels are determined by two key elements based on the definition of NTIC (Equation \ref{eq:nticObjective}).
+First, to achieve high level of NTIC, one needs to maximise the channel capacity between the current internal state and the future internal state $I(Y_{t+1};Y_{t})$.
+This indicates that the richer self-predictive information the NTIC process contained the higher level of consciousness the agent has.
+Considering two hypothetical systems composed of binary nodes, one has only three nodes and the other one has 1 million notes.
+Even thought the first system can reach the maximal the channel capacity, the maximal level of NTIC is only 3 bits.
+Comparing the first system, even though the second system does not have full self-predictability about its future state, the level of NTIC of this system can still far higher than the first system.
+This outcome naturally explains why people intuitively associate levels of consciousness with complexity of systems.\todo{Need to end this part and may need a reference} \toWrite{I want to say something about animal consciousness here}.
+
+	    Second, one can also minimise the conditional mutual information  $I(Y_{t+1};Y_{t}|E_{t})$.
+This suggests that conscious level positively correlates the level of information about the environment dynamic that the NTIC process encoded.
+Therefor, this implies that an agent who forms an NTIC process to lives and adapt to a more complex environment has a higher conscious level than an agent who interacts an environment with simpler dynamics.
+This also implies that agents who can explore, adapt model, and react to diverse environments should have higher level of consciousness.
+
+	    Note that the non-monotonic relationship between levels of NTIC and scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC.
+The self-predictive information is the key to achieve high conscious level.
+If a system dynamics is highly scholastic and unpredictable, the level of consciousness should be low.
+As a result, information processed at neuronal scales which is heavily noisy and highly scholastic cannot form a high level of consciousness.
+Similarly, after coarse-graining, macro-variables lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well.
+Consequently, human consciousness should be maximised at a certain coarse-grained level in the neural system.
+
+        Finally, which coarse-grained level can achieve high NTIC? 
+        agent-scale operation
+        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
+It gives agents living at this physical scale great advantages if the agents can build NTIC process internally.
+Therefore, to coarse-grain microscopic states is necessary
+
+		\begin{ants}
 
@@
 				\end{figure}
-
-    			@ This non-monotonic relationship bwetween the level of coarse-graining in the neural system and the degree of NTIC explains why only information processed at a certain level can become conscious contents.
-
-    			\end{ants}
-
-    		\subsubsection{Coarse-graining states correlates conscious contents}
-    			\begin{ants}
-				@ We claim that conscious contents correspond to the state of the NTIC process.
-
-				@ This implies that the complexity of conscious contents is determined by the amount of information encompassed in the NTIC process.
-
-				@ Therefore, larger state space of the NTIC process has, richer  experience the process can be conscious of (e.g., a NTIC process with high dimensionality).
-
-				@ Crucially, even experience of darkness is rich because it rules out other enormous potential state that the NTIC process can be in.
-Equivalently, knowing the state of the NTIC process when the process experiences darkness also mean acquisition of information of the system.\todo{bad wording}
-
-    			@ This is similar to the the \textit{Information} axiom in integrated information theory which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
-2]{oizumi2014phenomenology}
-
-    			@ \todo{Need an example here} Follow the example in the last section, a small creatures may live in a simple environment and forms a NTIC process.
-The predictive information for the next state of the process may be very low.
-This also implies the richness of the conscious experience this agent has is very limited.
-
-    			@ Our theory naturally explains why consciousness is compositional, because the joint states of entities in the NTIC process determine the contents of consciousness.
-\ideaCallout{think about it}
-
-				@ Importantly, note that because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale.
-
-				@ This supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.
-
-			\end{ants}
-
-	    \subsubsection{Reconcile level and content of consciousness}
-	        \begin{ants}
-	            @ Our theory link conscious level and conscious content together via the state space of the NTIC process.
-
-	            @ When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness.
+		\end{ants}
+
+\rlend
+\rlstart{3}
+		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
+        As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information.
+The state space of the correspondent physical system must have the same capacity of containing the same amount of information.
+We claim that conscious contents correspond to the state of the NTIC process.
+
+        This claim implies that the complexity of conscious contents correlates the amount of information encompassed in the NTIC process.
+Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer  conscious experience the process can have (e.g., a NTIC process involving a large amount of coarse-grained variables).
+Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents.
+Equivalently, in the physical system, to know the state of the NTIC process when there is no sensory input (darkness) also requires the same amount of information from the system.
+
+        Follow the example in the last section\todo{Do I have this example?}, a small creature lives in a simple environment with very limited environment dynamics.
+It may forms a simple NTIC process.
+However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small.
+As the result, the richness of the conscious experience this agent has will be very limited.
+
+        Importantly, because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale, our theory supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.
+
+		\begin{writingMaterials}
+            @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.
+
+		\end{writingMaterials}
+
+	    \subsection{Reconcile level and content of consciousness}
+	    Recently, the segregation of conscious level and conscious contents raise a debate \citep{bayne2016there, Fazekas2016}.
+Our framework reconciles conscious level and conscious content.
+When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness.
 Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system.
-
-	            @ levels and contents of consciousness are just two different measures of a NTIC process.
-
-	            @ this indicates an important prediction in which the conscious level is determined by states that the NTIC process potentially can reach rather the current state of a system.
-
-	            @ For example, some neural states may map to simple sensory experience, e.g.
-visual experience in a dark room.
-However, this does not degrade the conscious level.
-This experience still provides a huge amount of information because it excludes enormous possibilities of visual experience and decrease a large amount of uncertainty.
-
-    			@ Therefore, this framework well integrates the two key but debated concepts in consciousness research \citep{laureys2005neural, bayne2016there}.
-
-				@ \rewording{Note that, our claim is that informational closure is a more fundamental property that correlates consciousness.
-A species acquiring advantage to model a complex environment through evolution and , therefore, achieving a high-level non-trivial informational closure has a high level of consciousness, is the consequence of the evolution process.
-}
-
-	        \end{ants}
+From this perspective, levels and contents of consciousness are just two different properties of NTIC processes.
+An important prediction from our theory is that in which the conscious level is determined by the size of the state space of the NTIC process rather the transient state of a system.
+For example, when we experience monotonous environment (a dark room), this does not degrade the conscious level.
+
+	    Our framework also explains why in normal physiological states level and content are positively correlated \citep{laureys2005neural}\needfig{}.
+To achieve high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents.
+Therefore, this framework well integrates the two key but debated concepts in consciousness research.
 
@@
 
-\rlstart{1}
+\rlstart{2}
 		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
+
+        It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough.
+Need better expression} anatomical sensory hierarchy in the neural system.
+Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
+Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
+Nevertheless, to exercise causal power in actuators and environments, to read out information from coarse-grained levels is necessary.
+\needfig{Maybe need a figure discribing brain to hand}.
+Therefore, the neural system still implement readout decoders for the subsequent signal output.
+In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
+We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.
 
@@
 			\end{figure}
-
-			\begin{ants}
-				@ It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough.
-Need better expression} anatomical sensory hierarchy in the neural system.
-
-				@ the coarse-grained information is needed and computed only when the information is required for microscopic scale processing (readout).
-
-				@ Therefore, our theory is very different from consciousness theories focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
-
-				@ The truth is that due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
-
-				@ Nevertheless, to exercise causal power in actuators and environments, to read out information at coarse-grained levels is necessary.
-
-				@ In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
-
-				@ We argue that the neural correlates of consciousness may not be the fundamental principles for consciousness. The data may contaminate the understanding of consciousness. 
-			\end{ants}
 
@@
 
-        \subsection{About boundary}
-            \begin{ants}
-                @ boundary is fluid 
-            \end{ants}
+\rlstart{2}	
+        \subsection{Dynamical Boundary}
+        Our theory predicts that the physical boundary of a conscious system is dynamical.
+The boundary is determined by elements forming high NTIC.
+This implies that when the structure of interaction between elements changes the physical boundaries support consciousness should also change.
+If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC.
+In such case, these coarse-grained variables are "recruited" inside the boundary of conscious processes.
+Note that, due to synergetic information, even recruiting some new variables may largely increase the level of NTIC.
+        This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition.
+Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system.
+\needfig{Maybe I need a figure here as well}
+
+\rlend
+
+	\section{Conscious versus unconscious processing}
 
 \rlstart{1}	
-	\section{Conscious versus unconscious processing}
-		\ideaBox{Now we can combine "Relation to empirical findings in neuroscience and studies of consciousness" and "About Phenomenology (conscious processing)" in to this}
+		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
 
@@
         \begin{ants}
+            @ Our theory does not intent to solve the Hard problems. 
+            @ Inverted spectrum Inverted Qualia \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}
+
+            @ Considering that a system has only two possible physical states $X$ and $Y$ mapping to three different qualia (we can label them as $"red"$ and $"blue"$ respectively).
+A system cannot rest on two states at any moment, therefore, knowing the system state at $X$ excludes the the other possible state $Y$ and receives 1 bit information.
+Similarly, if conscious percept is $"red"$, it rules out the $"blue"$.
+Therefore, information provides by the conscious percept is also 1 bit.
+
+            @ However, our theory cannot tell why $X$ and $Y$ map to $red$ and $blue$ ,respectively, rather than the other way around.
+
+            @
+
             @ Our theory does not explain the mapping

### 2019-04-08 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 \usetikzlibrary{shadows}
+\usepackage{soul}
 
@@
     	}
-% 	\newenvironment{writingMaterials} %
-% 	{
-%         \begin{mdframed}[%
-%             frametitle=- Writing Materials,
-%             frametitlefont={\small\color{white}},
-%             middlelinecolor=Black,
-%             shadow=true,
-%             shadowsize=2mm,
-%             frametitlebackgroundcolor=Aquamarine,
-%             frametitlerule=true,
-%             backgroundcolor=Aquamarine!10!white]
-%         \noindent
-%         \begin{easylist}[itemize]
-% 	}
-% 	{
-%         \end{easylist}  
-%         \end{mdframed}
-% 	}
-% \newenvironment{writingMaterials} %
-% 	{
-%         \begin{tcolorbox}[enhanced,
-%         breakable,
-%         title=Writing Materials,
-%         colbacktitle=Aquamarine,
-%         drop fuzzy shadow,
-%         fontupper=\small,
-%         boxrule=0.4pt,
-%         colback=Aquamarine!10!white,
-%         sharp corners]
-
-%         \begin{easylist}[itemize]
-% 	}
-% 	{
-%         \end{easylist}  
-%         \end{tcolorbox}	
-% 	}	
-% \newenvironment{writingMaterials} %
-% 	{
-% 	\begin{tcolorbox}[size=small, colframe=black!20!white, toprule=1mm]
-% 		Writing Materials
-% 	\end{tcolorbox}
-% 	\begin{easylist}[itemize]
-% 	}
-% 	{
-% 	\end{easylist}
-% 	\begin{tcolorbox}[size=small, bottomrule=1mm, halign=flush right, colframe=black!20!white]
-% 		Writing Materials
-% 	\end{tcolorbox}
-% 	}
 
@@
 		% Highlight and comment
-		\newcommand{\highlightAndComment}[3][Yellow!75!white]{\todo[color=#1, linecolor=Yellow]{#3}\fcolorbox{Black}{#1}{#2}}
+        \newcommand{\highlightAndComment}[3][Yellow]{\sethlcolor{#1}\hl{#2}\todo[color=#1, linecolor=Yellow]{#3}}
 
@@
 			\newcommand{\ideaBox}[1]{
+			    \vspace{2mm}
 				\begin{tcolorbox}[enhanced,%
@@
 				\end{tcolorbox}
+				\vspace{2mm}
 			}
@@
 
-\rlstart{3}
-        In this section, we formally introduce our theory \tnamefull \todo{We need a good name}.
-
-        We starts our argument from a presumptive fact that every human conscious precept is ex trimly informative.
-Our conscious experience always consists of high multidimensional information involved multiple modalities.
-Considering information as resolved uncertainty, every conscious percept rules out enormous other possible conscious states in the state space, therefore, gives huge amount of of information.
-This notion is similar to one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0, \cite{oizumi2014phenomenology}) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
+\rlstart{4}
+        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\} \todo{We need a good name}.
+This framework proposes that NTIC is the fundamental properties for information processing to be conscious.
+Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.
+
+        We starts our argument from a presumptive fact that every human conscious precept is highly informative.
+Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities.
+If we consider information as resolved uncertainty, every conscious percept rules out other enormous possible conscious states that we are able to experience.
+Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.
+
+        This notion is in agreement with one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
 2]{oizumi2014phenomenology}.
 
-        Based on this presumptive fact, we further take a radical standpoint and postulate that consciousness fundamentally associate with information in the physical reality (information correlates of consciousness, \cite{chalmers1996conscious, tononi2004information, gamez2011information}) rather than neuronal states (neural correlates of consciousness).
-That is, consciousness should be information-based.
-The amount of information comprising a conscious percept should be equivalent to information we can obtain from a specific physical event.
-
-        Nevertheless, even though information involved in every conscious percept is extremely rich, it is still bounded, i.e.
-boundary exists.
-Presuming consciousness is information-based, we can deal with the boundary problem \cite{goff2006experiences} by information closure.
-Additionally, our conscious experience contains not merely trivial informational rather it always provides rich information about the environmental and our bodily states.
-Therefore, we argue that NTIC is the core entity \highlightAndComment{responsible}{Help me to think of a better term} for consciousness.
-
-        For example, in the physical world, if there exists two systems Alice and Bob, but there is no information flow between them (or we can say no causal influence from one to the other).
-If we assume that Alice has consciousness experience, the information enclosed in Alice's conscious contents must not include any information about Bob.
-
-        We can treat information as a common language between conscious experience and physical world.
+        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information that we can obtain from a particular physical event in the physical reality.
+For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between.
+Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.
+
+        \todo{Considering putting this para}
+        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
+        Imagining that in the future, one poor subject attend this experiment.
+We remove the subject's visual cortex from other brain areas.
+However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables.
+Because these cables are very long, we can move the visual cortex to the surface of Mars.
+Now the experimenters give visual cortex a input signal.
+If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth.
+We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds?
+We presume that in this three seconds subject's conscious experience should not contain any information about the visual input.
+Otherwise, the subject may be able to use the information to perform subsequent actions.
+This violates physics.
+This may look like a trivial questions.
+
+        We further take a radical standpoint and postulate that consciousness fundamentally associates with information in the physical reality, i.e.
+information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information}) and discard the notion of neural correlates of consciousness(NCC).
+In sum, we consider consciousness is an information-based phenomenon and information is a common language between conscious experience and the physical world.
+
+        We next consider the boundary problems of consciousness \cite{goff2006experiences}.
+Even though information involved in every conscious percept is extremely rich, it is still bounded, i.e.
+the boundaries of information exist in every conscious percept.
+Presuming consciousness is information-based, we can identify the boundaries by measures from information theory.
+Particularly in this case, boundaries can be defined by information closure.
+More importantly, our conscious experience always contains not merely trivial informational.
+Rather, it always provides rich information about the environmental and our bodily states.
+Therefore, we postulate that NTIC is a fundamental informational property associated with consciousness.
 
@@
 Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system.
-\needfig{Maybe I need a figure here as well}
+\needfig{Maybe I need a figure h  ere as well}
 
@@
 
-	\section{Conscious versus unconscious processing}
-
-\rlstart{1}	
+	\section{Conscious versus Unconscious Processing}
+
+\rlstart{2}	
 		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
-
-		\begin{ants}
-		    @ Our theory indicates that conscious information needs to fulfil two necessary conditions.
-
-		    @ 1. The information is processed at a certain coarse-grained
-
-		    @ 2. encoded in the NTIC process
-
-		    @ Based on the two conditions, we can classify brain processes into conscious and unconscious processing based on the two conditions.
-
-		\end{ants}
+		Our theory suggests two necessary conditions to make information conscious in the neural system.
+		\begin{enumerate}
+		    \item The information needs to be encode in NTIC processes
+		    \item \highlightAndComment{The information exists at coarse-grained levels which creates a high degree of NTIC and reduces stochasticity}{Need better expressions} 
+		\end{enumerate}
+
+		In this section, we discussed the implication of the two conditions for the empirical data in the literature of consciousness.
 
@@
 		        @ Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning, imagination, dreaming)
+
+		        @ It is important to note that we do suggest any functionalism of consciousness.
+Rather, we believe that information is fundamentally linked to consciousness.
+The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution.
+
+		        @@ Predictive information about the environment.
+
+		        @@ Stability
+
+		        @@ simulation environmental dynamics
+
 		    \end{ants}

### 2019-04-17 WritingMaterials/LimitCycle/NTIC.py
Add Limit cycle

@@ -1,0 +1,138 @@
+import dit
+import itertools
+import numpy as np
+from numpy import array as npa
+from pprint import pprint
+
+
+def genAllComb(stateSpace, nVar):
+    return list(itertools.product(stateSpace, repeat=nVar))
+
+
+def genAllSubsets(X):
+    subsets = [()]
+    for iLen in range(len(X)):
+        subset = list(itertools.combinations(X, iLen + 1))
+        subsets = subsets + subset
+    return subsets
+
+
+def genRandTranTable(comb, isManyToOne=True):
+    comb = npa(comb)
+    nComb = comb.shape[0]
+    prob = np.ones(nComb) / nComb
+    iComb_ = np.random.choice(range(nComb), nComb, replace=isManyToOne, p=prob)
+    comb_ = comb[iComb_]
+    comb_ = npa2tuple(comb_)
+    return comb, comb_, prob
+
+
+def npa2str(a):
+    """
+    :param a: numpy array
+    :return: string list
+    """
+    return [''.join(x) for x in a.astype(str)]
+
+
+def npa2tuple(a):
+    return [tuple(x) for x in a]
+
+
+def conditional_mutual_information(d, X, Y, Z):
+    """
+    I(X;Y|Z)
+    :param d: dit distribution obj
+    :param X: vars1
+    :param Y: vars2
+    :param Z: condition vars
+    :return: conditional mutual information
+    """
+    return dit.shannon.mutual_information(d, X, Y + Z) - dit.shannon.mutual_information(d, X, Z)
+
+
+def non_trivial_informational_closure(d, Yt, Et, Yt_):
+    return dit.shannon.mutual_information(d, Yt_, Yt) - conditional_mutual_information(d, Yt_, Yt, Et)
+
+
+def freqTable(samples):
+    comb, freq = np.unique(samples, return_counts=True, axis=0)
+    prob = freq / np.sum(freq)
+    return comb, prob
+
+
+class RandomVariableSet:
+    dd = None
+    iRV_now = None
+    iRV_next = None
+    nRV = None
+    Yt = None
+    Et = None
+    Yt_ = None
+    Et_ = None
+
+    def __init__(self):
+        pass
+
+    def CreateDistFromTimeSeries(self, ts):
+        ts = np.hstack([ts[0:-1], ts[1:]])
+        comb, prob = freqTable(ts)
+        comb = npa2tuple(comb)
+        self.__CreateDD(comb, prob)
+        return self.dd
+
[…]

### 2019-04-17 Paper_neural_coarse_graining_of_consciousness.tex

@@
 \usepackage{soul}
+\usepackage{version}
 
@@
 	% Writing Materials
-    \newenvironment{writingMaterials} %
+    \newenvironment{WritingMaterials} %
     	{
@@
 
+    % \excludeversion{WritingMaterials}
+
 % Functional content
@@
         \newcommand{\includegraphicsTodo}[2][]{%
-			\tcbox[%
-				adjusted title=\LARGE To Be Modified,
-				halign title=right,
-				colbacktitle=Orange!75!White,
-				coltitle=Black,
-				colframe=Red!60!White,
-				boxrule=1mm,
-				colback=white%
+            \tcbox[enhanced,
+                center,
+            	adjusted title=\large To Be Modified ...,
+            	halign title=center,
+            	attach boxed title to top left={yshift=-3mm, xshift=1cm,yshifttext=-1mm}, boxed title style={drop fuzzy shadow},
+            	colbacktitle=RedOrange!70!black,
+            	coltitle=white,
+            	colframe=RedOrange!50!black,
+            	colback=white
         	]{\includegraphics[#1]{#2}}}
@@
 		% call for help
-			\newcommand{\callforhelp}[1]{\todo[color=SpringGreen]{[Call For Help]: #1}}
+			\newcommand{\needhelp}[1]{\todo[color=SpringGreen]{[Need Help]: #1}}
 
@@
 			% It's a \addcomment[beautiful]{Acer}{need a reference} day
+
+    % backup: 
+    \newenvironment{backup}
+    {
+
+        \begin{tcolorbox}[enhanced,
+            title=-,
+            size=small,
+            colbacktitle=black!70!white,
+            colback=black!10!white,            
+            drop fuzzy shadow,
+            fontupper=\small,
+            boxrule=0.4pt,
+            sharp corners]
+            Backup
+        \end{tcolorbox}
+    }
+    {
+        \begin{tcolorbox}[enhanced,
+            halign=flush right,
+            halign title=right,
+            size=small,
+            colbacktitle=black!10!white,
+            colback=black!70!white,
+            drop fuzzy shadow,
+            fontupper=\small,
+            boxrule=0.4pt,
+            colupper=White,
+            sharp corners]
+            Backup -
+        \end{tcolorbox}    
+    }
+    % \excludeversion{backup}
 
@@
 
-		\begin{writingMaterials}
+		\begin{WritingMaterials}
 			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.
@@
 
-		\end{writingMaterials}
+		\end{WritingMaterials}
 
@@
 
-		\begin{writingMaterials}
+		\begin{WritingMaterials}
 			@ \rewrite{
@@
 			%% Macroscale Deterministic
-			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\callforhelp{Is there any good ref I can cite?}
+			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\needhelp{Is there any good ref I can cite?}
 
@@
 
-		\end{writingMaterials}
-
-		\begin{comment}
+		\end{WritingMaterials}
+
+		\begin{WritingMaterials}
 
@@
 
-		\end{comment}
-
-			\begin{writingMaterials}
+		\end{WritingMaterials}
+
+			\begin{WritingMaterials}
 				@ Population coding
@@
 
-			\end{writingMaterials}
-
-			\begin{comment}
+			\end{WritingMaterials}
+
+			\begin{WritingMaterials}
 				@ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.
@@
 				@ Agents can process information and act at abstract levels
-			\end{comment}
-
-			\begin{comment}
+			\end{WritingMaterials}
+
+			\begin{WritingMaterials}
 				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics.
@@
 				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
-			\end{comment}
+			\end{WritingMaterials}
 
@@
 
-\rlstart{4}
+\rlstart{5}
+
         In this section, we propose a new theoretical framework of consciousness \{\tnamefull\} \todo{We need a good name}.
@@
 
-        We starts our argument from a presumptive fact that every human conscious precept is highly informative.
+        We starts our argument from the first presumptive fact that every human conscious precept is highly informative.
 Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities.
-If we consider information as resolved uncertainty, every conscious percept rules out other enormous possible conscious states that we are able to experience.
+The notion of information referred to in this article is considered as resolved uncertainty.
+Being a certain conscious state rules out other enormous possible conscious experience in the state space of conscious experience.
 Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.
@@
 
-        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information that we can obtain from a particular physical event in the physical reality.
+        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality.
+Strictly speaking, we recognise information is a common language between conscious experience and the physical reality.
+We further take a radical standpoint and postulate that consciousness is fundamentally associated with information, i.e.
+information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).
+
+        Next, we next consider the second presumptive fact that the information in consciousness is bound.
+Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe.
+This leads to the boundary problems of consciousness \cite{goff2006experiences}.
+There should exist information boundaries for every conscious entity.
+Presuming consciousness is information-based phenomenon, we can identify the boundaries with measures from information theory.
+Particularly, in this case, boundaries can be defined by information closure.
+Therefore, information closure should be observed in conscious entities in the physical reality.
+
+        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level.
+Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}.
+This indicates that informational closed macroscopic levels can be treated as a complete reality.
+
+        Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e.
+non-trivial information.
+To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.
+
+        \begin{WritingMaterials}
         For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between.
@@
 
-        We further take a radical standpoint and postulate that consciousness fundamentally associates with information in the physical reality, i.e.
-information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information}) and discard the notion of neural correlates of consciousness(NCC).
-In sum, we consider consciousness is an information-based phenomenon and information is a common language between conscious experience and the physical world.
-
-        We next consider the boundary problems of consciousness \cite{goff2006experiences}.
-Even though information involved in every conscious percept is extremely rich, it is still bounded, i.e.
-the boundaries of information exist in every conscious percept.
-Presuming consciousness is information-based, we can identify the boundaries by measures from information theory.
-Particularly in this case, boundaries can be defined by information closure.
-More importantly, our conscious experience always contains not merely trivial informational.
-Rather, it always provides rich information about the environmental and our bodily states.
-Therefore, we postulate that NTIC is a fundamental informational property associated with consciousness.
-
-        Through coarse-graining, to achieve NTIC processes becomes possible in the neural system at macroscopic levels.
-Therefore, coarse-graining becomes necessary because every individual sensor and neuron at the microscopic scale can only access and process very limited partial information (Fig.
+        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity.
+Through coarse-graining, NTIC processes become possible at macroscopic levels.
+Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig.
 \ref{fig:LevelOfConsciousness}).
-In the following, ...
-
-		\begin{writingMaterials}
+In the following, we explained this framework and provide mathematical definitions and implications of ICC.
+        \end{WritingMaterials}
+
+		\begin{WritingMaterials}
 
@@
 			@ In the following part, we....\todo{todo}
-
-		\end{writingMaterials}
-
-		\begin{writingMaterials}
 
@@
 
-				\begin{figure}[H]				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
+				\begin{figure}[H]				
+				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
 				\label{fig:LevelOfConsciousness}
@@
 
-		\begin{writingMaterials}
+		\begin{figure}[H]
+			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
+			\label{fig:limitCycle}
+			\caption{Example of coarse-graining by a limit cycle process}
+		\end{figure}
+
+		\begin{equation}\label{eq:LimitCycleExample}
+            \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
+		\end{equation}
+
+		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and varance $\sigma^{2}=1$
+
+		\begin{WritingMaterials}
             @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.
 
-		\end{writingMaterials}
+		\end{WritingMaterials}
 
@@
 
-			\begin{writingMaterials}
+			\begin{WritingMaterials}
     			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.
@@
 
+				@ Consciousness and complexity \cite{Tononi1998}
+
 				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation.
@@
 
-			\end{writingMaterials}
+			\end{WritingMaterials}
 
@@
 
-            \begin{writingMaterials}
+            \begin{WritingMaterials}
     			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining
@@
 				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
-            \end{writingMaterials}
+            \end{WritingMaterials}
+
 \rlend
@@
 
-\rlstart{2}	
+\rlstart{3}	
 		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
+	    \ideaBox{I need to expend this section much more and more references}
 		Our theory suggests two necessary conditions to make information conscious in the neural system.
@@
 		\subsection{Conscious Processing}
-		    \begin{ants}
-		        @ To achieve high NTIC has evolutionary advantage.
-
-		        @ The current state of the process contains the information about its future state.
+		So far, previous consciousness research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.
+
+		\needhelp{I need some suggestions of conscious function here.}
+		\begin{ants}
+            @ response inhibition 
+            @ goal
+            @ planning            
+            @ conflict resolution
+            @ error detection         
+            @ task-switching
+            @ working memory
+            @ cognitive control 
+            @ overriding automatic responses
+            @ self-monitoring 
+            @ global availability 
+            @ integration             
+            @ stabilisation
+            @ information for off-line processing
+            @ flexible routing of information
+            @ integrates behaviour across time            
+            @ tasks for long duration
+            @ flexibility and the strategic use of that information for complex operations and decision-making 
+            @ flexible and adjust our behavior to different contexts and goals
+            @ complex visuomotor abilities
+            @ conscious thought, reflection, reasoning, and temporally extended sense of self. 
+            @ multiple alternative possibilities
+            @ simulate alternative realities 
+            @ imagination
+            @ dreaming 
+            @ anticipation
+            @ intending
+            @ replaying
+            @ interpreting
+            @ reflecting
+            @ reasoning
+            @ problem solving 
+            @ deciding            
+		\end{ants}
+
+		To achieve high NTIC has evolutionary advantage.
+When a process achieves NTIC, the current state of the process contains the information about its future state (Eq.
+(5)).
 Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process.
-
-		        @ Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning, imagination, dreaming)
-
-		        @ It is important to note that we do suggest any functionalism of consciousness.
+Cognitive functions recruiting forward models built upon it are conscious.
+(E.g., planning and imagination)
+
+		It is important to note that we do suggest any functionalism of consciousness.
 Rather, we believe that information is fundamentally linked to consciousness.
-The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution.
+The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution \cite{Seth2009Encyclopediaofconsciousness}.
+
+	    \begin{WritingMaterials}
+	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness.
+This evidences an important fact that consciousness is not necessay to these functions.
 
@@
 
-		    \end{ants}
+	        @ Replaying past events
+
+	        @ \rewrite{However, recent evidence also points out interesting dissociations between conscious and unconscious information processing when it comes to the duration, flexibility and the strategic use of that information for complex operations and decision-making} \cite{van2012role}
+
+	    \end{WritingMaterials}
 
 		\subsection{Unconscious Processing}
-		    \begin{ants}
-    		    @ When processes fail to satisfy either of the two conditions, they remain unconscious.
-
-    		    @ When processes do not meet the first condition, i.e. the information processed not at the certain coarse-grained level, the information will not be included in conscious contents.
-
-    		    @ For example, we are never conscious of neural spike activities at microscopic levels (e.g.
+		When processes fail to satisfy either of the two conditions, they remain unconscious.
+First, when processes do not meet the first condition, i.e.
+the information processed not at the certain coarse-grained level, the information will not be included in conscious contents.
+For example, we are never conscious of neural spike activities at microscopic levels (e.g.
 single cell activities) because information passing among individual neurons are not at the certain coarse-grained level.
-
-    		    @ Libet's free will experiment can be also explained by our theory.
-
-    		    @ The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.
-
-    		    @ When processes do not meet the second condition, i.e. processes which do not achieve high NTIC will remain unconscious.
-
-    		    @ This can explain why many "policy-based" processes are not conscious.
-
-    		    @ Policy-based here features those processes taking sensory information as input and directly outputting actions.
+\todo{Rewording}Libet's free will experiment can be also explained by our theory.
+The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.
+
+		Second, when processes do not meet the second condition, i.e.
+processes which do not achieve high NTIC will remain unconscious.
+This can explain why many "policy-based" processes are not conscious.\todo{Need a better term/way here} Policy-based here features those processes taking sensory information as input and directly outputting actions.
 Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure.
-
-    		    @ Several neural processes are included in this category, e.g. reflexive neural circuit, blindsight, procedure memory. 
-		    \end{ants}
-
-        \subsection*{}
-            \begin{ants}
-                @ To summarise, our theory can well explain the various findings with parsimonious assumptions. 
+Neural processes are included in this category, e.g.
+reflexive neural circuit, blindsight, procedure memory.
+
+		To summarise, our theory can well explain the various findings with parsimonious assumptions.
+
+	    \begin{ants}
+	        @ \rewrite{the nonsemantic processing of primes is enhanced and priming effects are boosted when the experimental context allows the formation of automatic stimulus–response mappings.}\cite{VandenBussche2009}
 	    \end{ants}
@@
 		\ideaBox{Main points should be same/diff, our advantages, and predictions}
-		\begin{ants}
-		    @ In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness. 
-		\end{ants}
-
-\rlstart{1}
+		In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness.
+
+\rlstart{2}
 		\subsection{Theories about multilevel views on consciousness and cognition}
-			\begin{ants}
-			    @ Previously, multilevel views on consciousness and cognition have been proposed.
-
-			    @ In the following, we discussed the differences between our theory and other theories about multilevel views.
-
-			\end{ants}
-
-			\begin{writingMaterials}
-			    @ LEVELS OF ORGANIZATION \cite{wimsatt1994ontology}
-
-			    @ As mentioned previously, the level of coarse-graining is different from the anatomical level.
-
-			    @ \ideaBox{Should I also deal with Marr's level of abstraction?}
-
-			    @ See the discussion in \cite{pennartz2015brain}. But Pennartz focus more on multimodal representation as the most important factor.
-
-			    @ Our proposal is inline with Pennartz's Neurorepresentational theory (Neurorepresentationalism). \cite{pennartz2018consciousness,pennartz2015brain}.
-
-			    @ Some theories also address the relationship between level of processing and consciousness.
-
-			    @ However, it’s crucial to note that our theory claims only the level of coarsegraining achieving NTIC matters to connsciousness rather than the anatomical level of sensory hierarchy
-
-				@ We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.			    
-			\end{writingMaterials}
+        Previously, multilevel views on consciousness and cognition have been proposed.
+We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.	% We discussed the differences between our theory and other theories about multilevel views.
+
+            \subsubsection{level of Organisation \cite{wimsatt1994ontology}}
+                As mentioned previously, the level of coarse-graining is different from the anatomical level.
+                Pennartz focus more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}).
+Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}.
+However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy.
+                \ideaBox{Should I also deal with Marr's level of abstraction?}
 
 			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
-				\begin{ants}
-				@ Intermediate Level Theory (ILT) proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy.
-This theory claims that consciousness only associates with the representation at  intermediate levels rather than the ones at lower-level or higher-level.
-
-				@ As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).
-				\end{ants}
+                One important theory linking consciousness to multilevel views is the Intermediate Level Theory (ILT).
+ILT proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy.
+This theory claims that consciousness only associates with the representation at intermediate levels rather than the ones at lower-level or higher-level discribed as 2.5D.
+However, ILT focuses on the levels in terms of anatomical direction.
+As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).
+
+                Different from ILT which suggests that the neural substrates responsible for the 2.5D computation is conscious, we predict that if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.
 
 			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
-			    \begin{ants}
-			    @ Our theory shares some similar concepts with Pennartz's Neurorepresentationalism.
-
-		        @ However, Neurorepresentationalism focuses on multimodal representation.
-
-		        @ Neurorepresentationalism also focuses on "making sense" between representation
-
-		        @ We focus on informational closure which suggests the closure of causal interaction in a system.
-
-		        @ We don't assume any functional properties as the criteria of consciousness. Instead, we propose information as a more fundamental principle correlates consciousness.  
-			    \end{ants}
-
-				\begin{writingMaterials}
+			    Our theory shares some similar concepts with Pennartz's Neurorepresentationalism.
+However, Neurorepresentationalism focuses on multimodal representation \cite{pennartz2018consciousness,pennartz2015brain}.
+Another focus of neurorepresentationalism is on "making sense" between representations\todo{Need something here}.
+Different from neurorepresentationalism, conscious contents in our framework are grounded by the informational relations between variables in NTIC because NTIC provides a closed relationship between states in a system.
+
+			    Similar to Neurorepresentationalism, our framwork is more close to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.\cite{pennartz2018consciousness,pennartz2015brain}
+
+			    Neurorepresentationalism is also a functionalist perspective.
+However, e don't assume any functional properties as the criteria of consciousness.
+Instead, we propose information as a more fundamental principle correlates consciousness.
+
+		        \begin{WritingMaterials}
 				%% Back up materials
@@
 } \cite{prinz2007inter    mediate}
-
-				    @ Our prediction is, if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.
 
@@
 The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
-				\end{writingMaterials}
+			\end{WritingMaterials}
 
@@
 
-\rlstart{1}	
+\rlstart{2}	
 		\subsection{First-order theories}
-
-            \begin{ants}
-
-		    @ The ﬁrst-order theories suggest that consciousness is determined by early sensory information or neural activities.\needref{First-order theories}
-
-		    @ We suggest that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness.
-
-		    @ However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.
-
-		    \end{ants}
-
-			\begin{writingMaterials}
+            The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}.
+The first-orde view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
+\rewrite{According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action.
+So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.}
+
+            We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness.
+However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.
+\todo{Need more here, espectially more counterintuitive predictions}
+
+			\begin{WritingMaterials}
 				@ \rewrite{
@@
 		\subsection{Higher Order Thought theory of consciousness}
-			\idea{
-				People think a high order representation receives information from the first order representation.
-This may be a misunderstanding.
+		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
+Meta-cognition is also associated with many conscious cognitive function.
+However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing.
+I need to rewrite this part}.
 This may be the result of neural coarse-graining.
-Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it}
-
-			============================================================================
-			\begin{ants}
+Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.
+Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
+It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}.
+The higher-order representation may resemble coarse-grained variables.
+This may cause misidentify the entity which correlates conscious experience.
+
+		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks.
+Therefore, most of the high level cognition can utilise the state of informational closure.
+For example, mental planning needs a precise forward model to infer the environmental dynamics.
+
+			\begin{WritingMaterials}
 		    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
@@
 			@ \cite{rosenthal2005consciousness}
-			\end{ants}
-
-            \begin{writingMaterials}
+
+            @ ============================================================================
 			@ \rewrite{
@@
 
-\rlstart{1}
+\rlstart{2}
 		\subsection{Global workspace theory}
-
-			\begin{ants}
-
+		Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules.
+Only the information that is accessed by the global workspace can be conscious aware of.
+The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules.
+Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.
+Our framework can well accommodate and interpret these claims by GWT.
+
+		Stability: Conscious perception necessitates representational stability. Our theory rests upon self-predictability which formally encompasses stability.
+
+		Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC.
+The neural system can extract the information for specific task goals.
+This is equivalent to the function of broadcasting.
+
+		Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates.
+In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process.
+This can cause a significant change of the brain states and resembles non-linear ignition of brain activities.
+Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
+Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
+A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
+Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed.
+\todo{Cite similar opinion from other theories}
+
+		A difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness.
+\todo{Link to Section 4}.
+Coarse-grained information in NTIC is more crucial for consciousness rather than neural substrates supporting the global workspace.
+
+		\begin{WritingMaterials}
 			%% Introduction
@@
 
-			\end{ants}
-
-			\subsubsection{Global availability and Broadcasting}
-
-			\subsubsection{Stability}
-				\begin{ants}
+		\end{WritingMaterials}
+
+% 			\subsubsection{Global availability and Broadcasting}
+% 			\subsubsection{Stability}
+				\begin{WritingMaterials}
 					@ the presence of contexts as stable coalitions shaping access to the workspace.
@@
 Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear ampliﬁcation of activation which invades a distributed set of parietal, prefrontal and cingulate areas
-				\end{ants}
-
-			\subsubsection{Broadcasting}
+				\end{WritingMaterials}
+
+% 			\subsubsection{Broadcasting}
 
 			\subsubsection{Ignition}
-				\begin{writingMaterials}
+				\begin{WritingMaterials}
 					@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
@@
 A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
-Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed
-				\end{writingMaterials}
-
-			\begin{ants}
+Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed.
+				\end{WritingMaterials}
+
+			\begin{WritingMaterials}
 				@ GWT is one of the current popular consciousness theories.
@@
 
-			\end{ants}
+			\end{WritingMaterials}
 \rlend
@@
 		\subsection{Sensorimotor contingency}
+		Sensorimotor contingency (SMC) theory of consciousness is proposed to account of conscious perception.
+It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
+The theory radically rejects the view that conscious contents is associated with information encoded in internal representations in the neural system.
+Rather, the quality of conscious perception depends on agents' mastery of SMCs.
+It emphasises the interactions between a system (the neural system) and its environment are crucial to form conscious perception
+
 			\begin{ants}
@@
 
-			\begin{comment} % materials
+			\begin{WritingMaterials} % materials
 
@@
 
-			\end{comment}
+			\end{WritingMaterials}
 
@@
 
-			\begin{writingMaterials}
+			\begin{WritingMaterials}
 
@@
 \rlstart{1}
-		\subsection{Integrated information theory\callforhelp{Help from Jun?}}
+		\subsection{Integrated information theory\needhelp{Help from Jun?}}
 			\begin{ants}
@@
 
-			\subsubsection{Hoel's theory\callforhelp{Help from Martin?}}
+			\subsubsection{Hoel's theory\needhelp{Help from Martin?}}
 				\ideaBox{This is very important. Need to be careful here.}
@@
     \section{Limitation}
+
+    \subsection{Finding potential coarse-graining functions}
+    To empirically verify the current theory, it is important to know what coarse-graining functions which maps microscopic variables to macroscopic variables in the neural system.
+So far, in this article, we have not speculated potential candidates of the coarse-graining function (or functions) that creates NTIC in the neural system.
+
+    \cite{Gamez2016} has systematically describe a similar issue in terms of finding data correlates of consciousness amount different 
+    level of abstraction.
+
         \begin{ants}
@@
 
-	\section*{=== backup ===}
+\newpage
+\begin{backup}
+\part*{Backup}
+\addcontentsline{toc}{part}{Backup}
+\setcounter{section}{0}
 	\section*{Biological evidence of informational closure in neural system}
@@
 
+\end{backup}
+
 \end{document}

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 
+	    Note that, the environment of a NTIC process in the nerual system includes not only the\todo{Werite this}
+
         Finally, which coarse-grained level can achieve high NTIC? 
@@
 		In this section, we discussed the implication of the two conditions for the empirical data in the literature of consciousness.
+
+		\subsection{Discuss items}
+		\begin{ants}
+		    @ Conscious
+
+		    @ Boundary 
+    		    @@ binocular rivalry
+    		    @@ Libet's experiment
+    		    @@ Priming
+    		    @@ Bistable perception
+    		    @@ Perceptual overflow
+    		    @@ Unconscious determinants of free decisions in the human brain
+    		    @@ Threshold of unconscious to consciousness
+    		    @@ Probabilistic information is always unconscious
+
+		    @ Unconscious
+
+		\end{ants}
 

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
add something in chapter 4 beginning

@@
 Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}.
-This indicates that informational closed macroscopic levels can be treated as a complete reality.
+        Information closure also implies that the system is ignorant of information outside of the system.
+Therefore, if a coarse-grained level achieves information closure, it suggests the NTIC process at the coarse-grained level is ignorant of information processing happening at microscopic levels and also higher coarse-grained levels.
+This virtually makes the informational closed macroscopic levels as a complete reality.
+        \todo{Due to my concern mentioned last week, I think I should also mention the closure is not only to the environment but also to the microscopic levels}
 

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
1. Deleted unnecessary newline 2. Fixed misplaced alignment tab characters & --> \&

--- 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
@@
 			\end{equation}
-
 		\newline
@@
 
-				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan & Noë, 2001).
-The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson & Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes.
+				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan \& Noë, 2001).
+The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson \& Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes.
 On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.
-A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan & Noë, 2001).
+A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan \& Noë, 2001).
 }

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
\ideaCallout outside \subsection bracket (otherwise build will fail)

@@
 
-		\subsection{Informational closure and level identification \ideaCallout{maybe not necessary}}
-
-		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}
+		\subsection{Informational closure and level identification}\ideaCallout{maybe not necessary}
+
+		\subsection{Biological Creature may try to achieve closure even the environment is not}\ideaCallout{Maybe not necessary}
 

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
separate sections

--- 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
@@
 \usepackage{tikz}
+\usepackage{ulem}
 
@@
 	\section{A neural coarse graining theory of consciousness}
-
-\rlstart{5}
-
-        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\} \todo{We need a good name}.
-This framework proposes that NTIC is the fundamental properties for information processing to be conscious.
-Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.
-
-        We starts our argument from the first presumptive fact that every human conscious precept is highly informative.
-Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities.
-The notion of information referred to in this article is considered as resolved uncertainty.
-Being a certain conscious state rules out other enormous possible conscious experience in the state space of conscious experience.
-Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.
-
-        This notion is in agreement with one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
-2]{oizumi2014phenomenology}.
-
-        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality.
-Strictly speaking, we recognise information is a common language between conscious experience and the physical reality.
-We further take a radical standpoint and postulate that consciousness is fundamentally associated with information, i.e.
-information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).
-
-        Next, we next consider the second presumptive fact that the information in consciousness is bound.
-Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe.
-This leads to the boundary problems of consciousness \cite{goff2006experiences}.
-There should exist information boundaries for every conscious entity.
-Presuming consciousness is information-based phenomenon, we can identify the boundaries with measures from information theory.
-Particularly, in this case, boundaries can be defined by information closure.
-Therefore, information closure should be observed in conscious entities in the physical reality.
-
-        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level.
-Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}.
-This indicates that informational closed macroscopic levels can be treated as a complete reality.
-
-        Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e.
-non-trivial information.
-To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.
-
-        \begin{WritingMaterials}
-        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between.
-Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.
-
-        \todo{Considering putting this para}
-        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
-        Imagining that in the future, one poor subject attend this experiment.
-We remove the subject's visual cortex from other brain areas.
-However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables.
-Because these cables are very long, we can move the visual cortex to the surface of Mars.
-Now the experimenters give visual cortex a input signal.
-If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth.
-We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds?
-We presume that in this three seconds subject's conscious experience should not contain any information about the visual input.
-Otherwise, the subject may be able to use the information to perform subsequent actions.
-This violates physics.
-This may look like a trivial questions.
-
-        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity.
-Through coarse-graining, NTIC processes become possible at macroscopic levels.
-Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig.
-\ref{fig:LevelOfConsciousness}).
-In the following, we explained this framework and provide mathematical definitions and implications of ICC.
-        \end{WritingMaterials}
-
-		\begin{WritingMaterials}
-
-        @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.
-
-        @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
-
-		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
-
-		@ This drives the neural system to create a non-trivial informational closure.
-
-        @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.
-
-        @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.
-
-		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})
-
-        @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.
-
-		@ Through coarse-graining, we can define a new set of variables.
-
-        @ information is scale-dependent
-
-		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.        
-		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.
-
-        @
-
-        @ Relationship between coarse-graining, scale and interaction with environment
-
-		@ \rewrite{
-			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
-
-			@@ conscious perception are very stable and time invariant.
-			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
-
-        @ To summaries, in our framework, consciousness is 
-			    @@ Intrinsic
-
-			    @@ Informative
-
-				@@ scale-dependent
-
-        % our claim   
-			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
-
-			@ We further postulate that level of consciousness corresponds to informational closureness of processes.
-
-			@ The contents of consciousness correspond to the states of the non-trivial informational closure.
-
-		% Following
-			@ In the following part, we....\todo{todo}
-
-			@ This is the same as "if a tree falls in a forest" thought experiment.
-
-			@ Therefore, to understand this system, you don't need more information from external environment.
-
-			@ It also means everything in this system is self-defined.
-
-			@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
-				@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}
-
-				@@ pennartz levels are defined by functional elements call "functional ensembles".
-\cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}
-
-			@ \rewrite{
-				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}
-
-				@@ Oppenheim , P.
-, \& Putnam , H.
-( 1958 ).
-Unity of science as a working hypothesis .
-In H.
-Feigl , G.
-Maxwell , \& M.
-Scriven (Eds.), Concepts, theories, and the mind – body problem (pp.
-3 – 36 ).
-Minneapolis : University of Minnesota Press .
-				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
-				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
-				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
-				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
-				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
-			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
-
-		\end{WritingMaterials}
-
-\rlend
-
-\rlstart{3}
-		\subsection{Measure of consciousness/information correlate of consciousness}	
-		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computes the properties of a NTIC process.
-\newline
-
-		\noindent
-		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of  $NTIC_{t}$ at a coarse-grained level.
-			\begin{equation}\label{eq:cLevel}
-				C_{t}^{Level} = NTIC_{t}
-			\end{equation}
-		\newline
-		\noindent 
-		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
-			\begin{equation}\label{eq:cContent}
-				C_{t}^{Content} = Y_{t}
-			\end{equation}
-
-		We discuss the implications of the two hypotheses in the following. 	
-	    \subsection{Level of Consciousness correlates degrees of NTIC of a process}
-
-	    Our theory indicates that conscious levels are determined by two key elements based on the definition of NTIC (Equation \ref{eq:nticObjective}).
-First, to achieve high level of NTIC, one needs to maximise the channel capacity between the current internal state and the future internal state $I(Y_{t+1};Y_{t})$.
-This indicates that the richer self-predictive information the NTIC process contained the higher level of consciousness the agent has.
-Considering two hypothetical systems composed of binary nodes, one has only three nodes and the other one has 1 million notes.
-Even thought the first system can reach the maximal the channel capacity, the maximal level of NTIC is only 3 bits.
-Comparing the first system, even though the second system does not have full self-predictability about its future state, the level of NTIC of this system can still far higher than the first system.
-This outcome naturally explains why people intuitively associate levels of consciousness with complexity of systems.\todo{Need to end this part and may need a reference} \toWrite{I want to say something about animal consciousness here}.
-
-	    Second, one can also minimise the conditional mutual information  $I(Y_{t+1};Y_{t}|E_{t})$.
-This suggests that conscious level positively correlates the level of information about the environment dynamic that the NTIC process encoded.
-Therefor, this implies that an agent who forms an NTIC process to lives and adapt to a more complex environment has a higher conscious level than an agent who interacts an environment with simpler dynamics.
-This also implies that agents who can explore, adapt model, and react to diverse environments should have higher level of consciousness.
-
-	    Note that the non-monotonic relationship between levels of NTIC and scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC.
-The self-predictive information is the key to achieve high conscious level.
-If a system dynamics is highly scholastic and unpredictable, the level of consciousness should be low.
-As a result, information processed at neuronal scales which is heavily noisy and highly scholastic cannot form a high level of consciousness.
-Similarly, after coarse-graining, macro-variables lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well.
-Consequently, human consciousness should be maximised at a certain coarse-grained level in the neural system.
-
-	    Note that, the environment of a NTIC process in the nerual system includes not only the\todo{Werite this}
-
-        Finally, which coarse-grained level can achieve high NTIC? 
-        agent-scale operation
-        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
-It gives agents living at this physical scale great advantages if the agents can build NTIC process internally.
-Therefore, to coarse-grain microscopic states is necessary
-
-		\begin{ants}
-
-			@ \todo{modify this figure}
-
-				\begin{figure}[H]				
-				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
-				\label{fig:LevelOfConsciousness}
-				\caption{Level of coarse-graining and level of consciousness.
-The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
-				\end{figure}
-		\end{ants}
-
-\rlend
-\rlstart{3}
-		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
-        As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information.
-The state space of the correspondent physical system must have the same capacity of containing the same amount of information.
-We claim that conscious contents correspond to the state of the NTIC process.
-
-        This claim implies that the complexity of conscious contents correlates the amount of information encompassed in the NTIC process.
-Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer  conscious experience the process can have (e.g., a NTIC process involving a large amount of coarse-grained variables).
-Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents.
-Equivalently, in the physical system, to know the state of the NTIC process when there is no sensory input (darkness) also requires the same amount of information from the system.
-
-        Follow the example in the last section\todo{Do I have this example?}, a small creature lives in a simple environment with very limited environment dynamics.
-It may forms a simple NTIC process.
-However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small.
-As the result, the richness of the conscious experience this agent has will be very limited.
-
-        Importantly, because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale, our theory supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.
-
-		\begin{figure}[H]
-			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
-			\label{fig:limitCycle}
-			\caption{Example of coarse-graining by a limit cycle process}
-		\end{figure}
-
-		\begin{equation}\label{eq:LimitCycleExample}
-            \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
-		\end{equation}
-
-		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and varance $\sigma^{2}=1$
-
-		\begin{WritingMaterials}
-            @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.
-
-		\end{WritingMaterials}
-
-	    \subsection{Reconcile level and content of consciousness}
-	    Recently, the segregation of conscious level and conscious contents raise a debate \citep{bayne2016there, Fazekas2016}.
-Our framework reconciles conscious level and conscious content.
-When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness.
-Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system.
-From this perspective, levels and contents of consciousness are just two different properties of NTIC processes.
-An important prediction from our theory is that in which the conscious level is determined by the size of the state space of the NTIC process rather the transient state of a system.
-For example, when we experience monotonous environment (a dark room), this does not degrade the conscious level.
-
-	    Our framework also explains why in normal physiological states level and content are positively correlated \citep{laureys2005neural}\needfig{}.
-To achieve high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents.
-Therefore, this framework well integrates the two key but debated concepts in consciousness research.
-
-			\begin{WritingMaterials}
-    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.
-
-    			@ This also suggests that the richness of the environment being modelled by the	NTIC process has a direct contribution to the level of consciousness.
-
-				@ To have high level non-trivial informational closure, the states of the coarse-grained scale need to
-
-				@ First, maximise the mutual information between environment and the representation.
-				This term implies that the agent need to maximise predictive power of environmental state.
-This also suggest that the environmental complexity is a crucial factor to the level of consciousness.
-The more rich and complex environment the agent try to predict the higher level of consciousness the agent has.
-
-				@ Consciousness and complexity \cite{Tononi1998}
-
-				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation.
-This term suggests that the representation is self-predicable and it mimics the environmental transition.
-
-				@ Therefore, this theory predicts that level of consciousness determined by the environment that the agent adapts to.
-To form a high non-trivial informational closure, the agent will need to live in a complex environment and model the environmental transition precisely.
-
-			\end{WritingMaterials}
-
-\rlend
-
-\rlstart{2}
-		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
-
-        It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough.
-Need better expression} anatomical sensory hierarchy in the neural system.
-Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
-Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
-Nevertheless, to exercise causal power in actuators and environments, to read out information from coarse-grained levels is necessary.
-\needfig{Maybe need a figure discribing brain to hand}.
-Therefore, the neural system still implement readout decoders for the subsequent signal output.
-In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
-We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.
-
-			\begin{figure}[H]
-				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
-				\label{fig:hierarchy}
-			\end{figure}
-
-            \begin{WritingMaterials}
-    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining
-
-				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.
-
-				@ It is possible that the neural system represents higher-level information processing by low level physical subtract.
-For example, studies have found representation for summery statistics of signal and neural.
-population.\needref{neural representation for summery statistics}\\
-				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
-            \end{WritingMaterials}
-
-\rlend
-
-\rlstart{2}	
-        \subsection{Dynamical Boundary}
-        Our theory predicts that the physical boundary of a conscious system is dynamical.
-The boundary is determined by elements forming high NTIC.
-This implies that when the structure of interaction between elements changes the physical boundaries support consciousness should also change.
-If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC.
-In such case, these coarse-grained variables are "recruited" inside the boundary of conscious processes.
-Note that, due to synergetic information, even recruiting some new variables may largely increase the level of NTIC.
-        This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition.
-Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system.
-\needfig{Maybe I need a figure h  ere as well}
-
-\rlend
+	\input{section4}
 

### 2019-04-23 sections/4/section-4-main.tex
separate sections

% SECTION 
% 	A neural coarse graining theory of consciousness

\rlstart{5}

        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\}\todo{We need a good name}. This framework proposes that NTIC is the fundamental property for information processing to be conscious. Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.

        We starts our argument from the first presumptive fact that every human conscious precept is highly informative. Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities. The notion of information referred to in this article is considered as resolved uncertainty. Being a certain conscious state rules out other enormous possible conscious experience in the state space of conscious experience. Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.

        This notion is in agreement with one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p. 2]{oizumi2014phenomenology}.

        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality. Strictly speaking, we recognise information is a common language between conscious experience and the physical reality. We further take a radical standpoint and postulate that consciousness is fundamentally associated with information, i.e. information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).

        Next, we next consider the second presumptive fact that the information in consciousness is bound. Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe. This leads to the boundary problems of consciousness \cite{goff2006experiences}. There should exist information boundaries for every conscious entity. Presuming consciousness is information-based phenomenon, we can identify the boundaries with measures from information theory. Particularly, in this case, boundaries can be defined by information closure. Therefore, information closure should be observed in conscious entities in the physical reality.

        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level. Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}. 
        Information closure also implies that the system is ignorant of information outside of the system. Therefore, if a coarse-grained level achieves information closure, it suggests the NTIC process at the coarse-grained level is ignorant of information processing happening at microscopic levels and also higher coarse-grained levels. This virtually makes the informational closed macroscopic levels as a complete reality. 
        \todo{Due to my concern mentioned last week, I think I should also mention the closure is not only to the environment but also to the microscopic levels}

        Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e. non-trivial information. To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.

        \begin{WritingMaterials}
        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between. Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.

        \todo{Considering putting this para}
        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
        Imagining that in the future, one poor subject attend this experiment. We remove the subject's visual cortex from other brain areas. However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables. Because these cables are very long, we can move the visual cortex to the surface of Mars. Now the experimenters give visual cortex a input signal. If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth. We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds? We presume that in this three seconds subject's conscious experience should not contain any information about the visual input. Otherwise, the subject may be able to use the information to perform subsequent actions. This violates physics. This may look like a trivial questions.

        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity. Through coarse-graining, NTIC processes become possible at macroscopic levels. Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig. \ref{fig:LevelOfConsciousness}). In the following, we explained this framework and provide mathematical definitions and implications of ICC.  
        \end{WritingMaterials}

		\begin{WritingMaterials}

        @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.

        @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}

		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.

		@ This drives the neural system to create a non-trivial informational closure.

        @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.

        @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.

		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})

        @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.

		@ Through coarse-graining, we can define a new set of variables.

        @ information is scale-dependent

		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.        
		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.

        @

        @ Relationship between coarse-graining, scale and interaction with environment

		@ \rewrite{
			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}

			@@ conscious perception are very stable and time invariant.
			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.

        @ To summaries, in our framework, consciousness is 
			    @@ Intrinsic

			    @@ Informative

				@@ scale-dependent

        % our claim   
			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

			@ We further postulate that level of consciousness corresponds to informational closureness of processes.

			@ The contents of consciousness correspond to the states of the non-trivial informational closure.

		% Following
			@ In the following part, we....\todo{todo}

			@ This is the same as "if a tree falls in a forest" thought experiment.

			@ Therefore, to understand this system, you don't need more information from external environment.

			@ It also means everything in this system is self-defined.

			@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
				@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}

				@@ pennartz levels are defined by functional elements call "functional ensembles". \cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}

			@ \rewrite{
				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}

				@@ Oppenheim , P. , \& Putnam , H. ( 1958 ). Unity of science as a working hypothesis . In H. Feigl , G. Maxwell , \& M. Scriven (Eds.), Concepts, theories, and the mind – body problem (pp. 3 – 36 ). Minneapolis : University of Minnesota Press .
				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.

		\end{WritingMaterials}

\rlend

\rlstart{3}
		\subsection{Measure of consciousness/information correlate of consciousness}	
		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computes the properties of a NTIC process. \newline

		\noindent
		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of  $NTIC_{t}$ at a coarse-grained level.
			\begin{equation}\label{eq:cLevel}
				C_{t}^{Level} = NTIC_{t}
			\end{equation}
		\newline
		\noindent 
		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
			\begin{equation}\label{eq:cContent}
				C_{t}^{Content} = Y_{t}
			\end{equation}

		We discuss the implications of the two hypotheses in the following. 	
	    \subsection{Level of Consciousness correlates degrees of NTIC of a process}

	    Our theory indicates that conscious levels are determined by two key elements based on the definition of NTIC (Equation \ref{eq:nticObjective}). First, to achieve high level of NTIC, one needs to maximise the channel capacity between the current internal state and the future internal state $I(Y_{t+1};Y_{t})$. This indicates that the richer self-predictive information the NTIC process contained the higher level of consciousness the agent has. Considering two hypothetical systems composed of binary nodes, one has only three nodes and the other one has 1 million notes. Even thought the first system can reach the maximal the channel capacity, the maximal level of NTIC is only 3 bits. Comparing the first system, even though the second system does not have full self-predictability about its future state, the level of NTIC of this system can still far higher than the first system. This outcome naturally explains why people intuitively associate levels of consciousness with complexity of systems.\todo{Need to end this part and may need a reference} \toWrite{I want to say something about animal consciousness here}.

	    Second, one can also minimise the conditional mutual information  $I(Y_{t+1};Y_{t}|E_{t})$. This suggests that conscious level positively correlates the level of information about the environment dynamic that the NTIC process encoded. Therefor, this implies that an agent who forms an NTIC process to lives and adapt to a more complex environment has a higher conscious level than an agent who interacts an environment with simpler dynamics. This also implies that agents who can explore, adapt model, and react to diverse environments should have higher level of consciousness.

	    Note that the non-monotonic relationship between levels of NTIC and scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC. The self-predictive information is the key to achieve high conscious level. If a system dynamics is highly scholastic and unpredictable, the level of consciousness should be low. As a result, information processed at neuronal scales which is heavily noisy and highly scholastic cannot form a high level of consciousness. Similarly, after coarse-graining, macro-variables lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well. Consequently, human consciousness should be maximised at a certain coarse-grained level in the neural system.

	    Note that, the environment of a NTIC process in the nerual system includes not only the\todo{Werite this}

        Finally, which coarse-grained level can achieve high NTIC? 
        agent-scale operation
        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics. It gives agents living at this physical scale great advantages if the agents can build NTIC process internally. Therefore, to coarse-grain microscopic states is necessary

		\begin{ants}

			@ \todo{modify this figure}

				\begin{figure}[H]				
				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
				\label{fig:LevelOfConsciousness}
				\caption{Level of coarse-graining and level of consciousness. The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
				\end{figure}
		\end{ants}

\rlend
\rlstart{3}
		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
        As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information. The state space of the correspondent physical system must have the same capacity of containing the same amount of information. We claim that conscious contents correspond to the state of the NTIC process.

        This claim implies that the complexity of conscious contents correlates the amount of information encompassed in the NTIC process. Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer  conscious experience the process can have (e.g., a NTIC process involving a large amount of coarse-grained variables). Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents. Equivalently, in the physical system, to know the state of the NTIC process when there is no sensory input (darkness) also requires the same amount of information from the system.

        Follow the example in the last section\todo{Do I have this example?}, a small creature lives in a simple environment with very limited environment dynamics. It may forms a simple NTIC process. However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small. As the result, the richness of the conscious experience this agent has will be very limited.

        Importantly, because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale, our theory supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.

		\begin{figure}[H]
			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
			\label{fig:limitCycle}
			\caption{Example of coarse-graining by a limit cycle process}
		\end{figure}

		\begin{equation}\label{eq:LimitCycleExample}
            \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
		\end{equation}

		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and varance $\sigma^{2}=1$

		\begin{WritingMaterials}
            @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.

		\end{WritingMaterials}

	    \subsection{Reconcile level and content of consciousness}
	    Recently, the segregation of conscious level and conscious contents raise a debate \citep{bayne2016there, Fazekas2016}. Our framework reconciles conscious level and conscious content. When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness. Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system. From this perspective, levels and contents of consciousness are just two different properties of NTIC processes. An important prediction from our theory is that in which the conscious level is determined by the size of the state space of the NTIC process rather the transient state of a system. For example, when we experience monotonous environment (a dark room), this does not degrade the conscious level.

	    Our framework also explains why in normal physiological states level and content are positively correlated \citep{laureys2005neural}\needfig{}. To achieve high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents. Therefore, this framework well integrates the two key but debated concepts in consciousness research.

			\begin{WritingMaterials}
    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.

    			@ This also suggests that the richness of the environment being modelled by the	NTIC process has a direct contribution to the level of consciousness.

				@ To have high level non-trivial informational closure, the states of the coarse-grained scale need to

				@ First, maximise the mutual information between environment and the representation.
				This term implies that the agent need to maximise predictive power of environmental state. This also suggest that the environmental complexity is a crucial factor to the level of consciousness. The more rich and complex environment the agent try to predict the higher level of consciousness the agent has.

				@ Consciousness and complexity \cite{Tononi1998}

				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation. This term suggests that the representation is self-predicable and it mimics the environmental transition.

				@ Therefore, this theory predicts that level of consciousness determined by the environment that the agent adapts to. To form a high non-trivial informational closure, the agent will need to live in a complex environment and model the environmental transition precisely.

			\end{WritingMaterials}

\rlend

\rlstart{2}
		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}

        It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough. Need better expression} anatomical sensory hierarchy in the neural system. Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}. Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels. Nevertheless, to exercise causal power in actuators and environments, to read out information from coarse-grained levels is necessary. \needfig{Maybe need a figure discribing brain to hand}. Therefore, the neural system still implement readout decoders for the subsequent signal output. In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system. We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
				\label{fig:hierarchy}
			\end{figure}

            \begin{WritingMaterials}
    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining

				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.

				@ It is possible that the neural system represents higher-level information processing by low level physical subtract. For example, studies have found representation for summery statistics of signal and neural. population.\needref{neural representation for summery statistics}\\
				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
            \end{WritingMaterials}

\rlend

\rlstart{2}	
        \subsection{Dynamical Boundary}
        Our theory predicts that the physical boundary of a conscious system is dynamical. The boundary is determined by elements forming high NTIC. This implies that when the structure of interaction between elements changes the physical boundaries support consciousness should also change. If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC. In such case, these coarse-grained variables are "recruited" inside the boundary of conscious processes. Note that, due to synergetic information, even recruiting some new variables may largely increase the level of NTIC. 
        This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition. Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system. \needfig{Maybe I need a figure h  ere as well}

\rlend

### 2019-04-25 sections/4/section-4-main.tex
Language *before* 4.1; commented out Writing Materials

@@
 % 	A neural coarse graining theory of consciousness
+\rlstart{5}
+		In this section, we propose a new theoretical framework of consciousness called \{\tnamefull\}  % The Neural Corase-Graining Theory of Consciousness
+			\todo{We need a good name}. 
+		The Theory makes two propositions.
+Firstly, a NTIC process sufficiently provides content of consciousness \sout{, endowing such content with an information-theortic account}.
+Secondly, a necessary condition to achieve NTIC is for information processing to satisfy coarse-graining.
 
-\rlstart{5}
+		%
+		In what follows, we will first establish two presumptions on which our Theory depends. Then, we will develop our propositions.
+			\todo{
+				In what specific ways are these presumptions help develop the Theory?
+			}
 
-        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\}\todo{We need a good name}.
-This framework proposes that NTIC is the fundamental property for information processing to be conscious.
-Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.
-
-        We starts our argument from the first presumptive fact that every human conscious precept is highly informative.
-Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities.
-The notion of information referred to in this article is considered as resolved uncertainty.
-Being a certain conscious state rules out other enormous possible conscious experience in the state space of conscious experience.
-Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.
-
-        This notion is in agreement with one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
+		%
+		% Presumtion I: Informativeness of conscious percepts
+		The first presumption is that (human) conscious percepts are highly informative.
+Such informativeness holds true if conscious percepts serve to resolve sensory uncertainty.
+Resolved uncertainty, therefore, represents the sort of information that stands out amongst those giving rise to alternative forms of perceptual experience.
+This notion is in agreement with one of the axioms of the Integrated Information Theory (IIT 3.0), i.e., the \textit{information} axiom, which claims that \myQuote{\ldots an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences\ldots} \citep[p.
 2]{oizumi2014phenomenology}.
 
-        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality.
-Strictly speaking, we recognise information is a common language between conscious experience and the physical reality.
-We further take a radical standpoint and postulate that consciousness is fundamentally associated with information, i.e.
-information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).
+		%
+		Based on this presumption, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality.
+			\todo[inline]{
+				This statement seems somewhat unclear. Suggestion: information processed of a conscious percept has a physical underpinning(?)
+			}\noindent
+		Strictly speaking, we recognise information as a common language between conscious experience and the physical reality.
+We further take the standpoint and postulate that consciousness is fundamentally associated with information.
+Namely, we will entertain information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) in place of a more restrictive notion of neural correlates of consciousness (NCC).
 
-        Next, we next consider the second presumptive fact that the information in consciousness is bound.
-Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe.
-This leads to the boundary problems of consciousness \cite{goff2006experiences}.
-There should exist information boundaries for every conscious entity.
-Presuming consciousness is information-based phenomenon, we can identify the boundaries with measures from information theory.
-Particularly, in this case, boundaries can be defined by information closure.
-Therefore, information closure should be observed in conscious entities in the physical reality.
+		%
+		% Presumption II: Boundedness of conscious percepts
+		Next, we consider a second presumption that the amount of
+			\todo[inline]{
+				What the term `boundary' refers to could be made clearer. 
+				It is quite ambiguous as to whether it means limits in quantity or physical extent where 
+				information is available to our sensorium as well as consciousness.
+			}\noindent
+		information held in consciousness is bounded.
+Even though information involved in every conscious percept is extremely rich, it is nevertheless limited as we are only consciously aware of a subset of events physics can plausibly realise.
+This speaks to the boundary problems of consciousness \cite{goff2006experiences}.
+The problem states that there should exist information boundaries for every conscious entity.
+Assuming consciousness is an information-theoretic phenomenon, we can identify a formal account \sout{and metric} on such boundary.
+As will be outlined later in our Theory, a boundary can be characterised by information closure.
+By prediction, physical entities that follow information closure are conscious.
+			\todo[inline]{
+				The original sentence is hard to follow: Therefore, information closure should be observed in conscious entities in the physical reality.
+			}\noindent
 
-        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level.
-Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}.
+		%
+		\rewording{
+			informational closure also suggests that there is no information flow from the lower to the higher level. 
+			Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}
+		}. 
 		Information closure also implies that the system is ignorant of information outside of the system. 
@@
 
-        Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e.
-non-trivial information.
+		Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e. non-trivial information. 
 		To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.
@@
 		\begin{WritingMaterials}
-        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between.
-Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.
+		For example, consider two physical systems (Alice and Bob) that have no interaction (or information passing) in between.
+Assuming that Alice is conscious, Alice's conscious experience should not involve any information about Bob.
 
 		\todo{Considering putting this para}
-        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
-        Imagining that in the future, one poor subject attend this experiment.
-We remove the subject's visual cortex from other brain areas.
-However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables.
-Because these cables are very long, we can move the visual cortex to the surface of Mars.
-Now the experimenters give visual cortex a input signal.
-If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth.
-We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds?
-We presume that in this three seconds subject's conscious experience should not contain any information about the visual input.
-Otherwise, the subject may be able to use the information to perform subsequent actions.
-This violates physics.
-This may look like a trivial questions.
-
+		Similarly, we can conduct a thought experiment by drawing an analogy between this example and information-passing involving two brain regions.
+Suppose we have a participant who is to have their visual cortex surgically separated from the rest of the brain, yet keeping all the connectivity perfectly intact by means of artifical wiring.
+Without altering the normative functioning of the separated visual cortex, it is then sent to the surface of Mars under sufficiently long wires.
+We know for a fact that signals travel at the speed of light on these special wires.
+Still, it takes three seconds to travel end-to-end.
+We ask: what would our participant experience visually during the interval between the experimenter administering stimulation and that stimulation reaching earth?
+We conjecture that the participant's conscious experience should not contain any information about the visual stimulation.
+Otherwise, the participant may be able to use the information to perform subsequent actions, thus violating laws of physics.
+This is a seemingly trivial conclusion.
+			\todo[inline]{
+				Transitioning into NTIC seems abrupt.
+			}\noindent
 		However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity.
@@
 In the following, we explained this framework and provide mathematical definitions and implications of ICC.
+			\todo[inline]{
+				Thought experiment does not appear to have an obvious connection with NTIC and coarse-graining?
+			}\noindent
 		\end{WritingMaterials}
 
-		\begin{WritingMaterials}
-
-        @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.
-
-        @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
-
-		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
-
-		@ This drives the neural system to create a non-trivial informational closure.
-
-        @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.
-
-        @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.
-
-		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})
-
-        @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.
-
-		@ Through coarse-graining, we can define a new set of variables.
-
-        @ information is scale-dependent
-
-		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.        
-		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.
-
-        @
-
-        @ Relationship between coarse-graining, scale and interaction with environment
-
-		@ \rewrite{
-			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
-
-			@@ conscious perception are very stable and time invariant.
-			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
-
-        @ To summaries, in our framework, consciousness is 
-			    @@ Intrinsic
-
-			    @@ Informative
-
-				@@ scale-dependent
-
-        % our claim   
-			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
-
-			@ We further postulate that level of consciousness corresponds to informational closureness of processes.
-
-			@ The contents of consciousness correspond to the states of the non-trivial informational closure.
-
-		% Following
-			@ In the following part, we....\todo{todo}
-
-			@ This is the same as "if a tree falls in a forest" thought experiment.
-
-			@ Therefore, to understand this system, you don't need more information from external environment.
-
-			@ It also means everything in this system is self-defined.
-
-			@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
-				@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}
-
-				@@ pennartz levels are defined by functional elements call "functional ensembles".
+		% \begin{WritingMaterials}
+		% @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale. 
+		% @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
+		% @ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
+		% @ This drives the neural system to create a non-trivial informational closure.
+		% @ Therefore, NTIC emerges from evolutionary processes is functionally plausible. 
+		% @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.
+		% @ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})
+		% @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.
+		% @ Through coarse-graining, we can define a new set of variables.
+		% @ information is scale-dependent
+		% @ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.
+		% @ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary. 
+		% @ Relationship between coarse-graining, scale and interaction with environment
+		% @ \rewrite{
+		% 	This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
+		% 	@@ conscious perception are very stable and time invariant.
+		% 	@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.        
+		% @ To summaries, in our framework, consciousness is 
+		% 		@@ Intrinsic 
+		% 		@@ Informative  
+		% 		@@ scale-dependent 
+		% % our claim   
+		% 	@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
+		% 	@ We further postulate that level of consciousness corresponds to informational closureness of processes.
+		% 	@ The contents of consciousness correspond to the states of the non-trivial informational closure.
+		% % Following
+		% 	@ In the following part, we....\todo{todo}
+		% 	@ This is the same as "if a tree falls in a forest" thought experiment.
+		% 	@ Therefore, to understand this system, you don't need more information from external environment.
+		% 	@ It also means everything in this system is self-defined.
+		% 	@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
+		% 		@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}
+		% 		@@ pennartz levels are defined by functional elements call "functional ensembles".
 \cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}
-
-			@ \rewrite{
-				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}
-
-				@@ Oppenheim , P.
+		% 	@ \rewrite{
+		% 		Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}
+		% 		@@ Oppenheim , P.
 , \& Putnam , H.
@@
 Minneapolis : University of Minnesota Press .
-				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
-				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
-				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
-				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
-				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
-			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
-
-		\end{WritingMaterials}
-
+		% 		@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
+		% 		@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
+		% 		@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
+		% 		@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
+		% 		@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
+		% 	@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
+		% \end{WritingMaterials}
 \rlend
-
+% 
+% 
+% 
 \rlstart{3}
 		\subsection{Measure of consciousness/information correlate of consciousness}	
-		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computes the properties of a NTIC process.
-\newline
+		Based on our core assumption that NTIC provides content of conscious experience, we express formally that the content and level of consciousness can be derived by computing the properties of a NTIC process.
+			\todo[inline]{
+				What does level mean here? Level as in degree or intensity?
+			}
 
-		\noindent
 		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of $NTIC_{t}$ at a coarse-grained level.
@@
 			\end{equation}
-		\newline
-		\noindent 
+		%
 		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
@@
 		We discuss the implications of the two hypotheses in the following.
+
 		\subsection{Level of Consciousness correlates degrees of NTIC of a process}
